---
title: "cluster-analysis"
author: "William Medwid"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

This analysis excludes bottle rejectors.

<!-- # Setup -->

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```

## Actions per minute between clusters

Clusters are based on actions per minute of mother and baby, as well as feeding duration. The clusters' order is randomly determined.

```{r}
n_clusters <- 4

data_total_simple <- data_dyad_total_zeros %>% 
  group_by(id, dyad_set, dyad_unit) %>% 
  summarise(actions_per_minute = sum(num_per_length), video_mins = first(video_mins)) %>% 
  pivot_wider(id_cols = c(id, dyad_set), 
              names_from = dyad_unit, 
              values_from = c(actions_per_minute, video_mins)) %>% 
  mutate(video_mins = video_mins_Mom) %>% 
  select(-video_mins_Mom, -video_mins_Baby)

kmeans <- data_total_simple %>% 
  ungroup() %>% 
  select(-id, -dyad_set) %>% 
  kmeans(centers = n_clusters)


data_total_clustered <- data_total_simple %>% 
  cbind(cluster = as.factor(kmeans$cluster))

data_total_clustered %>% 
  ggplot(aes(x = actions_per_minute_Baby, y = actions_per_minute_Mom, colour = cluster, size = video_mins)) +
  geom_point(alpha = 0.5) +
  facet_grid(~dyad_set)

kmeans$centers %>% cbind(cluster = 1:n_clusters) %>% kable(digits = 2, caption = "Cluster centroids")
```

## Behavior prevailence differences between clusters

```{r}
dyad_cluster_by_set <- data_total_clustered %>% 
  distinct(dyad_set, id, .keep_all = TRUE) %>% 
  select(dyad_set, id, cluster)

data_dyad_total_zeros_clusters <- data_dyad_total_zeros %>% 
  mutate(id = as.factor(id)) %>% 
  left_join(dyad_cluster_by_set, x_names = c(dyad_set, id), y_names = c(dyad_set, id))

p <- data_dyad_total_zeros_clusters %>% 
    filter(Wide_group != "Baseline") %>% 
    group_by(Narrow_group, cluster) %>% # , dyad_set) %>% 
    summarise(n_occurrences = sum(if_else(num_occurrences > 0, 1, 0)),
              n = n()) %>% 
    mutate(prop = n_occurrences / n) %>% 
      ggplot(aes(color=Narrow_group, 
                 group=Narrow_group,
                 linetype=Narrow_group,
                 y=prop, 
                 x = cluster
                 )) +
    #facet_grid(~dyad_set) + 
      geom_point() +
      geom_line() +
      ylim(0,1)

p %>% ggplotly()

line_plot <- function(data_dyad_total_zeros_clusters, group){
  behaviors <- behavior_codebook %>% filter(Narrow_group == group) %>% pull(Behavior)
  
  data_dyad_total_zeros_clusters %>% 
    filter(Behavior %in% behaviors) %>% 
    group_by(Behavior, cluster) %>% # , dyad_set) %>% 
    summarise(n_occurrences = sum(if_else(num_occurrences > 0, 1, 0)),
              n = n()) %>% 
    mutate(prop = n_occurrences / n) %>% 
      ggplot(aes(color=Behavior, 
                 group=Behavior,
                 linetype=Behavior,
                 y=prop, 
                 x = cluster
                 )) +
    #facet_grid(~dyad_set) + 
      geom_point() +
      geom_line() +
      ylim(0,1)
}

data_dyad_total_zeros_clusters %>% line_plot("Potent")
data_dyad_total_zeros_clusters %>% line_plot("Subtle")
data_dyad_total_zeros_clusters %>% line_plot("Responsive")
data_dyad_total_zeros_clusters %>% line_plot("Controlling-Limiting")
data_dyad_total_zeros_clusters %>% line_plot("Controlling-Encouragment")
data_dyad_total_zeros_clusters %>% line_plot("Uninvolved")
```

Behavior groups appear nearly the same across all four of the clusters, with the more active dyads being more active in all categories at a nearly uniform level, other than controlling-limiting behaviors, which were similarly low across all clusters. Some individual behaviors do vary out of line with the overall activity levels, such as eyes closed, bites or chews nipple, and burping.

## Behavior frequencies across clusters

The plots below show behavior frequencies among dyads who displayed a behavior at least once during the feeding.

```{r}
p <- data_dyad_total_zeros_clusters %>% 
  filter(num_occurrences > 0) %>% 
  group_by(Narrow_group, cluster) %>% # , dyad_set) %>% 
  summarise(avg_per_minute = mean(num_per_min)) %>% 
  ggplot(aes(color=Narrow_group, 
             group=Narrow_group,
             linetype=Narrow_group,
             y=avg_per_minute, 
             x = cluster
             )) +
  ggtitle("Grouped behaviors") +
  geom_point() +
  geom_line() +
  ylim(0,1)

p %>% ggplotly()

line_plot <- function(data_dyad_total_zeros_clusters, group){
  behaviors <- behavior_codebook %>% filter(Narrow_group == group) %>% pull(Behavior)
  
  data_dyad_total_zeros_clusters %>% 
    filter(num_occurrences > 0) %>% 
    filter(Behavior %in% behaviors) %>% 
    group_by(Behavior, cluster) %>% # , dyad_set) %>% 
    summarise(avg_per_minute = mean(num_per_min)) %>% 
    ggplot(aes(color=Behavior, 
               group=Behavior,
               linetype=Behavior,
               y=avg_per_minute, 
               x = cluster
               )) +
    ggtitle(group) +
    geom_point() +
    geom_line() +
    ylim(0,1)
}

data_dyad_total_zeros_clusters %>% line_plot("Potent")
data_dyad_total_zeros_clusters %>% line_plot("Subtle")
data_dyad_total_zeros_clusters %>% line_plot("Responsive")
data_dyad_total_zeros_clusters %>% line_plot("Controlling-Limiting")
data_dyad_total_zeros_clusters %>% line_plot("Controlling-Encouragment")
data_dyad_total_zeros_clusters %>% line_plot("Uninvolved")
```

