---
title: 'All Dyads'
author: ""
date: "`r Sys.Date()`"
output: html_document
---

# Data Reshaping

This file refines all_data and behavior_codebook into many readily usable formats. These original dataset comes from creating-all-data in the data processing section.


```{r, include = FALSE}
library(readr)
library(dplyr)
library(tidyr) # need devtools version ?
library(tibble)
library(ggplot2)
library(stringr)
library(purrr)
library(forcats)
library(knitr)
library(purrr)
library(ggpubr)
library(cowplot)
library(gridExtra)

library(gganimate)
#devtools::install_github('haleyjeppson/ggmosaic')
library(ggmosaic)


knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Vectorized sequence function
# seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...)
seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to"))

dyad_set_levels_short <- c("2wkB", "2moB", "4moB", "6moB")
dyad_set_levels <- c("2 weeks", "2 months", "4 months", "6 months", "9 months", "12 months")

n_time_points = length(dyad_set_levels)

# state_point_duration <- 0.000000001 # for easier coding, treat state points as start/stop


```


```{r, include = FALSE}
#New behavior codebook has narrow and wide groupings.
behavior_codebook <- read_csv("behavior_codebook.csv")  %>% 
  rename(Grouped_behavior = Behavior_group)

behaviors <- as.character(behavior_codebook$Behavior)
names(behaviors) <- behavior_codebook$Grouped_behavior

# behaviors_wide <- as.character(behavior_codebook$Behavior)
# names(behaviors_wide) <- behavior_codebook$Wide_group
# 
# behaviors_narrow <- as.character(behavior_codebook$Behavior)
# names(behaviors_narrow) <- behavior_codebook$Narrow_group

state_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State start") %>%
  select(Behavior) %>%
  pull()

point_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State point") %>%
  select(Behavior) %>%
  pull()

cues <- behavior_codebook %>%
  filter(Grouped_behavior == "Infant Satiation Cues") %>%
  select(Behavior) %>%
  pull()
```

Read raw data.
Excel files have already been cleaned and combined into one file.

6moB Bottle rejector not available yet; make all non-rejectors for now.

```{r, read-data, include = FALSE}
# data is the simplest form, reading in the raw complete data.

all_data <- read_csv("all_data.csv") %>% #Groups are added by left_join in code chunk below.
  # # mutate(Grouped_behavior = fct_recode(Behavior, !!!behaviors),
  # #        Wide_grouped_behavior = fct_recode(Behavior, !!!behaviors_wide),
  # #        Narrow_grouped_behavior = fct_recode(Behavior, !!!behaviors_narrow)
  # #        ) %>%
  mutate(
    id = factor(id),
    dyad_set = factor(dyad_set)) %>% 
  mutate(
    Time_Relative_sf = as.double(Time_Relative_sf),
    Duration_sf = as.double(Duration_sf),
    Comment = as.logical(Comment),
    
    Position_of_Infant = as.integer(Position_of_Infant),
    time = as.double(time),
    duration = as.double(duration),
    dyad_set = str_replace(dyad_set, "wkB", " weeks"), # Creates full age labels
    dyad_set = str_replace(dyad_set, "moB", " months"),
    dyad_set = factor(dyad_set, levels = dyad_set_levels),
    Bottle_Rejector = replace_na(Bottle_Rejector, 0),
    Bottle_Rejector = factor(Bottle_Rejector)
  )
```


```{r behaviors}
# Creates behaviors, a dataframe of each unique behavior, its groups, and which dyad unit performs it.

behaviors <- all_data %>%
  select(Behavior) %>%
  unique() %>%
  mutate(Behavior = replace(Behavior, Behavior == "Blocks mouth", "Blocks mouth with hands or feet"))

behaviors <- left_join(behaviors,
                       behavior_codebook %>%
                         select(-Event_Type, -Event_Type)
)
```

Add columns for end time of each behavior, video length, and start/end/duration as fraction of video length.


# data-duration

data_duration is the most complete reshaped data for most purposes. It contains the starting time and duration of each behavior, as well as information about what behavior will come next from the other party.

next_behavior = the other party's next behavior (even if it's after multiple of the original party's actions.)
bottle_state = current bottle state at time of behavior.

```{r duration-data}

data_duration <- all_data %>%
  mutate(end_time = time + duration) %>%
  group_by(dyad_set, id) %>%
  mutate(duration_fraction = duration / max(end_time),
         start_fraction = time / max(end_time),
         end_fraction = end_time / max(end_time),
         video_length = max(end_time)) %>%
  filter(Event_Type %in% c("State start", "State point"))

# now including interaction variables

bottle_states <- all_data %>%
  filter(str_detect(Behavior, "^Bottle")) %>%
  pull(Behavior) %>%
  unique()


# The following code adds bottle_state, next_behavior (and next_behavior_group variables), and next_time.
# For this purpose, next_behavior is the next thing the other person does, even if there are more of the same person's behaviors beforehand.
# This definition may change, and we are considering moving the next_behavior analysis code to interaction-analysis where we can choose what definition of next behavior to use on a plot by plot basis.

data_duration <- data_duration %>% 
  group_by(dyad_set, id) %>% #Create bottle_state variable
  mutate(new_bottle_state = if_else(Behavior %in% bottle_states, 1, 0),
         bout_code = cumsum(new_bottle_state)) %>% 
  ungroup() %>% 
  group_by(dyad_set, id, bout_code) %>% 
  mutate(bottle_state = if_else(time > 0, first(Behavior), "Bottle not in mouth")) %>% #Code start time:bottle not in mouth
  ungroup() %>% 
  select(-bout_code, -new_bottle_state) %>%  
  group_by(id, dyad_set) %>% # The rest of the code is to create next_behavior and next_time
  mutate(next_dyad_unit = lead(dyad_unit),
         switch = if_else(next_dyad_unit == dyad_unit, 0, 1),
         chain_group = cumsum(switch) - switch) %>% #Switch = 1 at end of group, chain group changes at start of new group
  ungroup() %>% 
  mutate(next_behavior = if_else(switch == 1, lead(Behavior), NULL),
         next_group_narrow = if_else(switch == 1, lead(Narrow_group), NULL),
         next_group_wide = if_else(switch == 1, lead(Wide_group), NULL),
         next_time = if_else(switch == 1, lead(Time_Relative_sf), NULL)) %>% 
  group_by(id, dyad_set, chain_group) %>% 
  mutate(next_behavior = if_else(is.na(next_behavior), last(next_behavior), next_behavior),
         next_group_narrow = if_else(is.na(next_group_narrow), last(next_group_narrow), next_group_narrow),
         next_group_wide = if_else(is.na(next_group_wide), last(next_group_wide), next_group_wide),
         next_time = if_else(is.na(next_time), last(next_time), next_time),
         time_until_next = next_time - Time_Relative_sf) %>% 
  mutate(one = 1,
         remaining_cues = cumsum(one),
         remaining_cues = max(remaining_cues) - remaining_cues) %>% 
  ungroup() %>% 
  select(-switch, -chain_group, -one)

write.csv(data_duration,
  "data_duration.csv",
  row.names=FALSE)
```

Total number of dyads at each age


```{r}

n_dyads <- all_data %>%
  group_by(dyad_set, Bottle_Rejector) %>%
  summarize(n = n_distinct(id))

n_dyads# %>% kable()

# two-way table?

```


List of dyads observed, with their ages and bottle rejector status. Used to create other datasets.

```{r}

data_ids <- all_data %>%
  group_by(dyad_set, id) %>%
  summarize(id = first(id),
            Bottle_Rejector = first(Bottle_Rejector))

```


data_map summarizes which dyads are observed at which ages

- 0.0 = not observed
- 0.5 = observed, Bottle rejector
- 1.0 = observed, not bottle rejector


```{r}
# Create data map - which dyads are in which set

count_ones <- function(x){
  length(x[x == 1])
}

count_positives <- function(x){
  length(x[x > 0])
}

data_map <- all_data %>%
  group_by(id, dyad_set) %>%
  filter(row_number() == 1) %>% 
  mutate(indicator = 1 - 0.5 * as.numeric(as.character(Bottle_Rejector))) %>%
  select(id, dyad_set, indicator) %>% 
  pivot_wider(names_from = dyad_set, values_from = indicator, values_fill = 0) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(Time_points_with_rejectors = count_positives(c_across(!id))) %>%
  mutate(Time_points = count_ones(c_across(!c(id, Time_points_with_rejectors))))

write.csv(data_map,
          "data-map.csv",
          row.names = FALSE)

```

Summarize total number of dyads observed at each combination of ages


```{r}
# data_age_summary <- data_map %>%
#   ungroup() %>%
#   mutate(across(where(is.numeric), ~round(.x + 0.1))) %>%
#   filter(!(id == "Total")) %>%
#   group_by(`2 weeks`, `2 months`, `4 months`, `6 months`) %>%
#   summarize(count = n_distinct(id)) %>%
#   arrange(desc(`2 weeks` + `2 months` + `4 months` + `6 months`),
#           desc(`2 weeks`),
#           desc(`2 months`),
#           desc(`4 months`),
#           desc(`6 months`))

```

```{r}

# data_age_summary_acceptors <- data_map %>%
#   ungroup() %>%
#   mutate(across(where(is.numeric), ~trunc(.x + 0.1))) %>%
#   filter(!(id == "Total")) %>%
#   group_by(`2wkB`, `2moB`, `4moB`, `6moB`) %>%
#   summarize(count = n_distinct(id)) %>%
#   arrange(desc(`2wkB` + `2moB` + `4moB` + `6moB`),
#           desc(`2wkB`),
#           desc(`2moB`),
#           desc(`4moB`),
#           desc(`6moB`))

```

For each dyad, count number of instances and total time of each behavior, both absolute and relative to length of video.

```{r dyad-totals}
# Total count and time of each Behavior per dyad

data_dyad_total <- data_duration %>%
  group_by(dyad_set, id, Behavior) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction),
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(video_mins = video_length / 60,
         num_per_length = num_occurrences / video_length,
         num_per_min = num_occurrences / video_mins)


```

Add zeros for unobserved behaviors.
One row for each possible behavior for each dyad at each age.


```{r}
# unselecte the Bottle_Rejector from data_dyad_total because it was making 2 bottle_rejector columns
data_dyad_total_zeros <-
  left_join(expand_grid(data_ids, behaviors),
            data_dyad_total %>%
              select_if(names(.) %in% c("dyad_set", "id", "Behavior") |
                          sapply(., is.numeric)), 
            by = c("dyad_set", "id", "Behavior")) %>%
  mutate(
    across(where(is.numeric), ~replace_na(.x, 0))
  ) %>%
  group_by(dyad_set, id) %>%
  mutate(video_length = max(video_length))

write.csv(data_dyad_total_zeros,
          "data-dyad-total-zeros.csv",
          row.names = FALSE)

```


# reshape-data-time-event

```{r reshape-data-time-event}
behaviors <- all_data %>%
  select(Behavior) %>%
  unique()

# Vectorized sequence function
# seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...)
seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to"))

create_state_path <- function(x) {
  
  y <- rep(0, length(x))
  start_rows <- which(x == "State start")
  stop_rows <- which(x == "State stop") - 1
  if(length(start_rows) != length(stop_rows)){
    stop(paste("Unequal lengths of start and stop vectors:", length(start_rows), "vs.", length(stop_rows)))
  }
  state_rows <- unlist(seq_vec(from = start_rows, to = stop_rows))
  y[state_rows] <- 1
  as.numeric(y)
  
}

all_data <- all_data %>%
  arrange(dyad_set, id, time, desc(Event_Type))

for (l in bottle_states) {
  
  x = ifelse(all_data$Behavior == l, all_data$Event_Type, NA)
  y = create_state_path(x)
  all_data <- all_data %>%
    add_column(!!l := y)
  
}

bottle_state_code = max.col(all_data %>%
                              select(starts_with("Bottle "))) *
  (all_data %>% mutate(bottle_sum = rowSums(across(starts_with("Bottle ")))) %>% pull(bottle_sum) > 0)
bottle_state_code[bottle_state_code == 0] <- NA

all_data <- all_data %>%
  mutate(Bottle_state = names(all_data %>% select(starts_with("Bottle ")))[bottle_state_code]) %>%
  select(-starts_with("Bottle "))

# Function translates start/stop column to 0/1 at each time point

create_state_path <- function(x){
  y <- rep(0, length(x))
  start_rows <- which(x == "State start")
  stop_rows <- which(x == "State stop") - 1
  state_rows <- unlist(seq_vec(from = start_rows, to = stop_rows))
  y[state_rows] <- 1
  as.numeric(y)
}

# spread to create binary column for each behavior
# convert Crying and Eyes Closed to point behaviors first

convert_to_point <- c("Crying", "Eyes Closed")

data_time_event <- all_data %>%
  filter(!(Behavior %in% convert_to_point & #Remove "State stop" lines for crying and eyes closed
             Event_Type == "State stop")) %>%
  mutate(Event_Type =
           if_else(Behavior %in% convert_to_point, "State point", #Convert crying and eyes closed to points
                   Event_Type)) %>%
  mutate(duration =
           if_else(Behavior %in% convert_to_point, 0, # Should 0 be replaced with state_point_duration?
                   duration)) %>%
  arrange(dyad_set, id, time, desc(Event_Type)) %>%
  pivot_wider(names_from = Behavior,
              values_from = Event_Type)

# Change start/stop to 1/0 and point behaviors to 1/0
# Should be able to do the following with mutate?
# mutate(across(any_of(state_behaviors)), create_state_path)

for (l in setdiff(state_behaviors, convert_to_point)) {
  
  y = create_state_path(data_time_event[, l] %>% pull())
  data_time_event <- data_time_event %>%
    select(-l) %>% 
    add_column(!!l := y)
  
}

for (l in c(point_behaviors, convert_to_point)) { #This repeats eyes closed and is crying twice, though it doesn't make a difference
  if(l %in% colnames(data_time_event)){
    y = data_time_event[, l] %>% pull() %>% 
      replace_na(0) %>% 
      str_replace("State point", "1") %>% 
      #is.na() %>% 
      as.numeric()
    
    data_time_event <- data_time_event %>%
      select(-l) %>% 
      add_column(!!l := y)
    #add_column(!!l := 1 - y)
  }

  
}

# Some times have multiple rows for start/stops for multiple behaviors
# Need to collapse so only one row for each time
# **Only keep last row for each time**
# after all start/stops at a single time have been accounted

# Adjusting times with multiple rows probably needs to be checked more thoroughly

data_time_event <- data_time_event %>%
  group_by(dyad_set, id, time) %>%
  mutate(duration = ifelse(time == 0 & coder_id == "KJR",
                           duration,
                           max(duration))) %>%
  filter(row_number() == n()) %>%
  arrange(dyad_set, id, time) %>%
  mutate(infant_cue = rowSums(across(any_of(cues)))) %>%
  mutate(infant_cue = ifelse(infant_cue > 0, 1, 0)) %>%
  group_by(dyad_set, id) %>%
  select(dyad_set, id, dyad_unit, time, duration,
         starts_with("Bottle"), any_of(c(state_behaviors, point_behaviors)),
         infant_cue) 

# Add counter for each bottle state in a feeding

data_time_event <- data_time_event %>%
  rename_with(~ gsub(" ", "_", .x), starts_with("Bottle ")) %>%
  mutate(Bottle_state_code =
           1 * Bottle_not_in_mouth +
           2 * Bottle_in_mouth +
           3 * Bottle_offered) %>%
  mutate(prev_Bottle_state_code =
           dplyr::lag(Bottle_state_code, n = 1, default = NA)) %>%
  mutate(Bottle_state_change = 
           ifelse(is.na(prev_Bottle_state_code),
                  1,
                  as.numeric(!(Bottle_state_code == prev_Bottle_state_code)))) %>%
  mutate(Bottle_state_counter = cumsum(Bottle_state_change)) %>%
  mutate(next_time =
           dplyr::lead(time, n = 1, default = NA)) %>%
  mutate(time_until_next = 
           ifelse(is.na(next_time), 0, next_time - time)) %>%
  ungroup() %>%
  group_by(dyad_set, id, Bottle_state_counter, Bottle_state) %>%
  mutate(time_in_bottle_state =
           time - min(time)) %>%
  mutate(time_remaining_in_bottle_state =
           max(next_time) - time) %>%
  mutate(time_fraction_bottle_state =
           (time - min(time)) / (max(next_time) - min(time)))


# create a column for the cue that happens at the time
# For now just record multiple cues as "multiple"

cue_columns_only <- data_time_event %>% ungroup() %>% select(any_of(cues))

data_time_event <- data_time_event %>%
  mutate(num_cues_at_time = rowSums(across(any_of(cues)))) %>%
  add_column(cue_at_time = colnames(cue_columns_only)[
    apply(cue_columns_only, 1, which.max)]) %>%
  mutate(cue_at_time = ifelse(num_cues_at_time == 0, NA, cue_at_time)) %>%
  mutate(cue_at_time = ifelse(num_cues_at_time > 1, "multiple", cue_at_time))

write.csv(data_time_event,
          "data_time_event.csv",
          row.names = FALSE)
```

# duration-data-time-split

```{r duration-data-time-split}
# individual instances of each behavior
# For each behavior, compute start time, end time, and duration
# as fraction of feeding length

get_time_split <- function(x, q) {
  ifelse(x == 1, q, 1 + trunc((x * q) %% q))
}

n_time_splits <- 4 # 4 for quarters; 3 for thirds; etc

data_duration_time_split <- all_data %>%
  mutate(end_time = time + duration) %>%
  group_by(dyad_set, id) %>%
  mutate(duration_fraction = duration / max(end_time),
         start_fraction = time / max(end_time),
         end_fraction = end_time / max(end_time),
         video_length = max(end_time)) %>%
  filter(Event_Type %in% c("State start", "State point")) %>%
  mutate(time_split = get_time_split(start_fraction, n_time_splits),
         split_length = video_length / n_time_splits)


```


For each dyad, count number of instances and total time of each behavior, both absolute and relative to length of video.

```{r dyad-totals}
# Total count and time of each Behavior per dyad

data_dyad_total <- data_duration %>%
  group_by(dyad_set, id, Behavior) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length)


```

```{r dyad-totals-time-split}
# Total count and time of each Behavior per dyad

data_dyad_total_time_split <- data_duration_time_split %>%
  group_by(dyad_set, id, Behavior, time_split) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            time_split = first(time_split),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length),
            video_mins = video_length / 60,
            split_length = max(split_length)) %>%
  mutate(num_per_length = num_occurrences / video_length,
         num_per_split = num_occurrences / split_length,
         num_per_length = num_occurrences / video_length,
         num_per_min = num_occurrences / video_mins)


```



Add zeros for unobserved behaviors.
One row for each possible behavior for each dyad at each age.

<!-- Old data_dyad_total_zeros -->
<!-- ```{r} -->

<!-- data_dyad_total_zeros <- -->
<!--   left_join(expand_grid(data_ids, Behavior = behaviors), -->
<!--             data_dyad_total %>% -->
<!--               select_if(names(.) %in% c("dyad_set", "id", "Behavior") | -->
<!--                           sapply(., is.numeric)) %>%  -->
<!--               mutate(id = as.factor(id)), -->
<!--             by = c("dyad_set", "id", "Behavior")) %>% -->
<!--   mutate( -->
<!--     across(where(is.numeric), ~replace_na(.x, 0)) -->
<!--   ) %>% -->
<!--   group_by(dyad_set, id) %>% -->
<!--   mutate(video_length = max(video_length)) -->

<!-- write.csv(data_dyad_total_zeros, -->
<!--           "data-dyad-total-zeros.csv", -->
<!--           row.names = FALSE) -->

<!-- ``` -->


```{r}
behaviors <- all_data %>%
  select(Behavior) %>%
  unique() %>% 
  mutate(Behavior = replace(Behavior, Behavior == "Blocks mouth", "Blocks mouth with hands or feet")) %>% 
  pull()

data_dyad_total_time_split_zeros <-
  left_join(expand_grid(data_ids, Behavior = behaviors, time_split = 1:n_time_splits),
            data_dyad_total_time_split %>%
              select_if(names(.) %in% c("dyad_set", "id", "Behavior", "time_split", "dyad_unit") |
                          sapply(., is.numeric)),
              # mutate(id = as.factor(id)),
            by = c("dyad_set", "id", "Behavior", "time_split")) %>%
  mutate(
    across(where(is.numeric), ~replace_na(.x, 0))
  ) %>%
  group_by(dyad_set, id) %>%
  mutate(video_length = max(video_length),
         split_length = max(split_length))

write.csv(data_dyad_total_time_split_zeros,
          "data-dyad-total-time-split-zeros.csv",
          row.names = FALSE)

```



```{r quarterly-data}
# Total count and time of each Behavior per dyad

quarterly_data <- data_duration %>%
  group_by(dyad_set, id) %>%
  mutate(quarter = case_when(time < (video_length / 4) ~ 1,
                             time < 2*(video_length / 4) & time >= (video_length / 4) ~ 2,
                             time < 3*(video_length / 4) & time >= 2*(video_length / 4) ~ 3,
                             time >= 3*(video_length / 4) ~ 4)) %>%
  mutate(half = case_when(time < (video_length / 2) ~ 1,
                          time >= 2*(video_length / 4) ~ 2
                          )) %>%
  ungroup() %>%
  group_by(dyad_set, id, Behavior, quarter) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            quarter = as.factor(quarter),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length) %>%
  distinct() # because there are duplicate rows

# example// if there are 3 occurences of Burping in quarter 2 for a dyad_set / id combo, it will display that row 3 times to indicate the 3 occurences
# using disitinct gets rid of the duplicate rows.


# Add zeros for unobserved behaviors.
# One row for each possible behavior for each dyad at each age.

# quarterly_data_dyad_total_zeros <-
#   left_join(expand_grid(data_ids, behavior_codebook) %>%
#               # rename(Grouped_behavior = Behavior_group),
#             quarterly_data %>%
#               select_if(names(.) %in% c("dyad_set", "id", "Behavior") |
#                           sapply(., is.numeric)),
#             by = c("dyad_set", "id", "Behavior")) %>%
#   mutate(
#     across(where(is.numeric), ~replace_na(.x, 0))
#   ) %>%
#   group_by(dyad_set, id) %>%
#   mutate(video_length = max(video_length))

write.csv(quarterly_data,
          "quarterly-data.csv",
          row.names = FALSE)
```

```{r halved_data}
halved_data <- data_duration %>%
  group_by(dyad_set, id) %>%
  mutate(quarter = case_when(time < (video_length / 4) ~ 1,
                             time < 2*(video_length / 4) & time >= (video_length / 4) ~ 2,
                             time < 3*(video_length / 4) & time >= 2*(video_length / 4) ~ 3,
                             time >= 3*(video_length / 4) ~ 4)) %>%
  mutate(half = case_when(time < (video_length / 2) ~ 1,
                          time >= 2*(video_length / 4) ~ 2
                          )) %>%
  ungroup() %>%
  group_by(dyad_set, id, Behavior, half) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            quarter = as.factor(quarter),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length) %>%
  distinct() # because there are duplicate rows

write.csv(halved_data,
          "halved-data.csv",
          row.names = FALSE)
```

# data_onehot

EXCLUDING "State stop" lines currently, but including when states are active. They made redundant columns, but may be useful later.

```{r}
#data_onehot makes every behavior's start and ending into a numeric variable. This should help with our modeling efforts.

#Currently using data_duration, which already has a bottle_state column and no state_stop lines.
positive_state_behaviors <- c("Crying", "Eyes Closed", "Looks at phone or device", "Bottle in mouth", "Bottle Offered")

#Step 1: Add a column for each positive state
all_data_states <- all_data

for(state_name in positive_state_behaviors){
  #state_name = "Crying"
  
  all_data_states <- all_data_states %>% 
    group_by(dyad_set, id) %>% #Creating temporary variables to make state variables
    mutate(new_state = if_else(Behavior == state_name, 1, 0),
           on_or_off = if_else(Behavior == state_name, if_else(Event_Type == "State start", 1, 0), 0), #1 = start, 0 = end, 0 = neither
           # All states (listed above) are considered not happening if they have not been mentioned in the feeding yet.
           bout_code = cumsum(new_state)) %>% 
    ungroup() %>% 
    group_by(dyad_set, id, bout_code) %>% 
    mutate(state = if_else(time > 0, first(on_or_off), 0)) %>% #Code start time:bottle not in mouth
    ungroup() %>% 
    select(-new_state, -on_or_off, -bout_code)#remove temporary variables
    # Rename new state column
    names(all_data_states)[names(all_data_states) == "state"] <- str_c("state_", state_name)
}

# Step 2: Remove state_stop lines and add bottle_state variable.
#Now that we have our states, we can remove the state_stop lines, as they aren't considered to be an action.
all_data_states <- all_data_states %>% 
  filter(Event_Type != "State stop") %>% 
  group_by(dyad_set, id) %>% #Create bottle_state variable
  mutate(new_bottle_state = if_else(Behavior %in% bottle_states, 1, 0),
         bout_code = cumsum(new_bottle_state)) %>% 
  ungroup() %>% 
  group_by(dyad_set, id, bout_code) %>% 
  mutate(bottle_state = if_else(time > 0, first(Behavior), "Bottle not in mouth")) %>% #Code start time:bottle not in mouth
  ungroup() %>% 
  select(-bout_code, -new_bottle_state)
  
  

# Step 3: Pivot wider to have one column per behavior label
data_onehot <- all_data_states %>% 
  mutate(previous_bottle_state = lag(bottle_state, default = "Bottle not in mouth")) %>% 
  #select(id, dyad_set, Time_Relative_sf, Behavior, Event_Type, bottle_state, previous_bottle_state) %>%
  filter(Event_Type != "State stop") %>%
  # New columns receive the following name: Behavior name, or if state stop then "Stops " + Behavior name
  #mutate(
  #  behavior_name = str_c(if_else(Event_Type == "State point", "", "Starts "),
  #                             Behavior)) %>% 
  #mutate(behavior_name = as.factor(behavior_name)) %>% 
  mutate(temp_1 = 1.0) %>%  # To fill all true columns with 1, else 0.
  pivot_wider(names_from = Behavior, values_from = temp_1, values_fill = 0)

# Step 4: Identify the behavior columns and state columns for later use. 
# They must be to the right of all other columns for this method to work, and start with "Starts Eyes Open".
onehot_columns = colnames(data_onehot)
# The behavior colunms are all the columns to the right of "Eyes Open" at this stage.
onehot_behavior_columns = onehot_columns[match("Eyes Open", onehot_columns):length(onehot_columns)]
# The state columns start with "state_Crying" and end with "Eyes Open"
onehot_state_columns = onehot_columns[match("state_Crying", onehot_columns):(match("bottle_state", onehot_columns)-1)]

# Step 5: Then we group all cues that happen at the same time into one line.
data_onehot <- data_onehot %>% 
  group_by(id, dyad_set, Time_Relative_sf) %>% 
  summarise(starting_bottle_state = first(previous_bottle_state),
            ending_bottle_state = last(bottle_state),
            across(where(is.numeric), ~ sum(.x)),
            # If there are multiple lines, Behavior is "Multiple Behaviors". Otherwise, it's the one behavior at that time.
            current_behavior = if_else(n()>1, "Multiple Behaviors", first(Software_Behavior))) %>% 
  # If the bottle changed during this time point, this variable notes it.
  # Uses NA_character_ to make null rows if no change happened.
  mutate(changed_bottle_state = if_else(starting_bottle_state == ending_bottle_state, NA_character_, ending_bottle_state))

head(data_onehot)

write.csv(data_onehot, "data_onehot.csv")
```
# Improved clusters

- When a cue occurs, compile many parts of what happens in the next 10 seconds into a single line.

To edit the time window, change the value below (window_seconds)

```{r}
window_seconds = 10
```

```{r}
# Direct method (each behavior is only part of one group, each group lasting up to 10 seconds.)

# Step 1: Add variable for how much time has passed since last cue

df_clusters <- data_onehot %>% 
  mutate(
    time_elapsed = Time_Relative_sf - lag(Time_Relative_sf, default = 0), # Time from the previous behavior
    )

# Step 2: Group each time where cues occur into a cluster

group_vec = numeric(nrow(df_clusters))
for(row in 1:nrow(df_clusters)){ #Loop through each row in the dataframe
  if (df_clusters[row, "Time_Relative_sf"] == 0){ # Reset the group counter at the start of each video. This makes group 0 onlyinclude time=0 cues
    current_group = 0
    current_remaining = -1
  } else {
    elapsed = df_clusters[row, "time_elapsed"]
    current_remaining = current_remaining = current_remaining - elapsed # Subtract time elaped from time remaining in this group
    if (current_remaining < 0){ # When the time remaining in the cluster falls below 0, we start a new cluster with 10 seconds remaining.
      current_group = current_group + 1
      current_remaining = window_seconds
    }
  }
  group_vec[row] = current_group # On each row, record what group it falls into
}
df_clusters["cluster_group"] <- group_vec # Add our clusters column to the dataframe

df_temp <- df_clusters
#df_clusters <- df_temp

# Steps 4-5 each each manipulate df_clusters in different ways to make columns that are later joined.

# Step 4:  Group behaviors by cluster. add up all behaviors within clusters, and create time variables
df_cluster_times <- df_clusters %>% 
  group_by(id, dyad_set, cluster_group) %>% 
  summarize(start_time = min(Time_Relative_sf),
            end_time = max(Time_Relative_sf),
            cluster_time = end_time - start_time,
            first_behavior = first(current_behavior),
            bottle_state_start = first(starting_bottle_state),
            bottle_state_changed = first(na.omit(changed_bottle_state)), # this will be NA unless the bottle state changed
            across(onehot_behavior_columns, sum), # For each of the behavior columns, its new value is the sum over the group.
            across(onehot_state_columns, max) # For each state column, if it was active at any point in the cluster, it is considered active
            )
  
# Step 5: Create grouped behavior columns
# To make these, we will pivot the table into a wider form where each behavior is a row, find additional information, then re-group.
df_cluster_group_cols <- df_clusters %>% 
  pivot_longer(cols = all_of(onehot_behavior_columns), names_to = "Behavior", values_to = "count") %>% 
  left_join(behavior_codebook, by="Behavior") %>%
  group_by(id, dyad_set, cluster_group, Narrow_group, dyad_unit) %>% 
  summarize(count = sum(count)) %>% 
  pivot_wider(id_cols = c(id, dyad_set, cluster_group), names_from = Narrow_group, values_from = count)

# Could copy step 5 to sum behaviors by wide group or infant/mother
# Step 5.5
df_cluster_dyad_cols <- df_clusters %>% 
  pivot_longer(cols = all_of(onehot_behavior_columns), names_to = "Behavior", values_to = "count") %>% 
  left_join(behavior_codebook, by="Behavior") %>%
  group_by(id, dyad_set, cluster_group, dyad_unit) %>% 
  summarize(count = sum(count)) %>% 
  pivot_wider(id_cols = c(id, dyad_set, cluster_group), names_from = dyad_unit, values_from = count)

# Step 6: Join these 2 together.
df_behavior_clusters <- df_cluster_times %>% 
  left_join(df_cluster_group_cols, by = c("id", "dyad_set", "cluster_group")) %>% 
  left_join(df_cluster_dyad_cols, by = c("id", "dyad_set", "cluster_group"))

# Step 7: Remove standard cluster 0 (which just starts states off)
df_behavior_clusters <- df_behavior_clusters %>% 
  filter(cluster_group > 0)

write.csv(df_behavior_clusters, "df_behavior_clusters.csv")
```
