---
title: 'All Dyads'
author: ""
date: "`r Sys.Date()`"
output: html_document
---




```{r, include = FALSE}

library(readr)
library(dplyr)
library(tidyr) # need devtools version ?
library(tibble)
library(ggplot2)
library(stringr)
library(purrr)
library(forcats)
library(knitr)
library(purrr)
library(ggpubr)
library(cowplot)
library(gridExtra)

library(gganimate)
#devtools::install_github('haleyjeppson/ggmosaic')
library(ggmosaic)


knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Vectorized sequence function
# seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...)
seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to"))

dyad_set_levels <- c("2wkB", "2moB", "4moB", "6moB")

n_time_points = length(dyad_set_levels)

# state_point_duration <- 0.000000001 # for easier coding, treat state points as start/stop


```


```{r, include = FALSE}

behavior_codebook <- read_csv("behavior_codebook.csv")  %>% #New behavior codebook has narrow and wide groupings.
  rename(Grouped_behavior = Behavior_group)

behaviors <- as.character(behavior_codebook$Behavior)
names(behaviors) <- behavior_codebook$Grouped_behavior
# 
# behaviors_wide <- as.character(behavior_codebook$Behavior)
# names(behaviors_wide) <- behavior_codebook$Wide_group
# 
# behaviors_narrow <- as.character(behavior_codebook$Behavior)
# names(behaviors_narrow) <- behavior_codebook$Narrow_group

state_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State start") %>%
  select(Behavior) %>%
  pull()

point_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State point") %>%
  select(Behavior) %>%
  pull()

cues <- behavior_codebook %>%
  filter(Grouped_behavior == "Infant Satiation Cues") %>%
  select(Behavior) %>%
  pull()
```

Read raw data.
Excel files have already been cleaned and combined into one file.

6moB Bottle rejector not available yet; make all non-rejectors for now.

```{r, read-data, include = FALSE}
data <- read_csv("all_data.csv") %>% #Groups are added by left_join in code chunk below.
  # mutate(Grouped_behavior = fct_recode(Behavior, !!!behaviors),
  #        Wide_grouped_behavior = fct_recode(Behavior, !!!behaviors_wide),
  #        Narrow_grouped_behavior = fct_recode(Behavior, !!!behaviors_narrow)
  #        ) %>%
  rename("id" = "ID_Number",
         "coder_id" = "Coder") %>%
  mutate(
    Time_Relative_sf = as.double(Time_Relative_sf),
    Duration_sf = as.double(Duration_sf),
    Comment = as.logical(Comment),
    id = factor(id),
    Position_of_Infant = as.integer(Position_of_Infant),
    time = as.double(time),
    duration = as.double(duration),
    dyad_set = factor(dyad_set, levels = dyad_set_levels),
    Bottle_Rejector = replace_na(Bottle_Rejector, 0),
    Bottle_Rejector = factor(Bottle_Rejector)
  )
```


```{r data_update}
behaviors <- data %>%
  select(Behavior) %>%
  unique() %>% 
  mutate(Behavior = replace(Behavior, Behavior == "Blocks mouth", "Blocks mouth with hands or feet"))

behaviors <- left_join(behaviors,
                       behavior_codebook %>% 
                         select(-Event_Type, -Event_Type)
)

data <- data %>%
  mutate(Behavior = replace(Behavior,
                            Behavior == "Blocks mouth",
                            "Blocks mouth with hands or feet")) %>%
  left_join(behavior_codebook%>% 
                         select(-Event_Type, -dyad_unit)
            , by=c("Behavior"))

write.csv(data,
  "data.csv",
  row.names=FALSE)
```

Add columns for end time of each behavior, video length, and start/end/duration as fraction of video length.


```{r duration-data}
# individual instances of each behavior
# For each behavior, compute start time, end time, and duration
# as fraction of feeding length

data_duration <- data %>%
  mutate(end_time = time + duration) %>%
  group_by(dyad_set, id) %>%
  mutate(duration_fraction = duration / max(end_time),
         start_fraction = time / max(end_time),
         end_fraction = end_time / max(end_time),
         video_length = max(end_time)) %>%
  filter(Event_Type %in% c("State start", "State point"))

write.csv(data_duration,
  "data_duration.csv",
  row.names=FALSE)

data_duration %>% filter(is.na(Narrow_group))
```

Total number of dyads at each age


```{r}

n_dyads <- data %>%
  group_by(dyad_set, Bottle_Rejector) %>%
  summarize(n = n_distinct(id))

n_dyads# %>% kable()

# two-way table?

```


List of dyads observed

```{r}

data_ids <- data %>%
  group_by(dyad_set, id) %>%
  summarize(id = first(id),
            Bottle_Rejector = first(Bottle_Rejector))

```


Summarize which dyads are observed at which ages

- 0.0 = not observed
- 0.5 = observed, Bottle rejector
- 1.0 = observed, not bottle rejector


```{r}
# Create data map - which dyads are in which set

count_ones <- function(x){
  length(x[x == 1])
}

count_positives <- function(x){
  length(x[x > 0])
}

data_map <- data %>%
  group_by(id, dyad_set) %>%
  filter(row_number() == 1) %>% 
  mutate(indicator = 1 - 0.5 * as.numeric(as.character(Bottle_Rejector))) %>%
  select(id, dyad_set, indicator) %>% 
  pivot_wider(names_from = dyad_set, values_from = indicator, values_fill = 0) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(Time_points_with_rejectors = count_positives(c_across(!id))) %>%
  mutate(Time_points = count_ones(c_across(!c(id, Time_points_with_rejectors))))

write.csv(data_map,
          "data-map.csv",
          row.names = FALSE)

```

Summarize total number of dyads observed at each combination of ages


```{r}
data_age_summary <- data_map %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~round(.x + 0.1))) %>%
  filter(!(id == "Total")) %>%
  group_by(`2wkB`, `2moB`, `4moB`, `6moB`) %>%
  summarize(count = n_distinct(id)) %>%
  arrange(desc(`2wkB` + `2moB` + `4moB` +`6moB`),
          desc(`2wkB`),
          desc(`2moB`),
          desc(`4moB`),
          desc(`6moB`))

```

```{r}

data_age_summary_acceptors <- data_map %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~trunc(.x + 0.1))) %>%
  filter(!(id == "Total")) %>%
  group_by(`2wkB`, `2moB`, `4moB`, `6moB`) %>%
  summarize(count = n_distinct(id)) %>%
  arrange(desc(`2wkB` + `2moB` + `4moB` + `6moB`),
          desc(`2wkB`),
          desc(`2moB`),
          desc(`4moB`),
          desc(`6moB`))

```

For each dyad, count number of instances and total time of each behavior, both absolute and relative to length of video.

```{r dyad-totals}
# Total count and time of each Behavior per dyad

data_dyad_total <- data_duration %>%
  group_by(dyad_set, id, Behavior) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(video_mins = video_length / 60,
         num_per_length = num_occurrences / video_length,
         num_per_min = num_occurrences / video_mins)


```

Add zeros for unobserved behaviors.
One row for each possible behavior for each dyad at each age.


```{r}

data_dyad_total_zeros <-
  left_join(expand_grid(data_ids, behaviors),
            data_dyad_total %>%
              select_if(names(.) %in% c("dyad_set", "id", "Behavior") |
                          sapply(., is.numeric)),
            by = c("dyad_set", "id", "Behavior")) %>%
  mutate(
    across(where(is.numeric), ~replace_na(.x, 0))
  ) %>%
  group_by(dyad_set, id) %>%
  mutate(video_length = max(video_length))

write.csv(data_dyad_total_zeros,
          "data-dyad-total-zeros.csv",
          row.names = FALSE)

```

```{r reshape-data-time-event}
source("reshape_data_time_event.R")
```

