---
title: 'Mom Response: All Dyads'
author: ""
date: "`r Sys.Date()`"
output: html_document
---

This analysis excludes bottle rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```

# Total number of bottle states in feeding

```{r}

data_dyad_total_bottle_state <- data_dyad_total_zeros %>%
  filter(Behavior %in% bottle_states)

plot_bottle_in_mouth_pdf <- ggplot(data_dyad_total_bottle_state,
       aes(x = num_occurrences,
           y = after_stat(density),
           colour = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  ggtitle("Bottle states") +
  facet_wrap(~Behavior)


plot_bottle_in_mouth_cdf <- ggplot(data_dyad_total_bottle_state,
       aes(num_occurrences,
           colour = dyad_set)) +
  stat_ecdf() +
  ylab("Cumulative proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  facet_wrap(~Behavior)

plot_grid(plot_bottle_in_mouth_pdf,
          plot_bottle_in_mouth_cdf,
          rel_heights = c(1, 1),
          ncol = 1, nrow = 2,
          align = "h")

```

```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_occurrences, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of bouts in feeding") +
  facet_wrap(~Behavior)
                 
```


```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_occurrences),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Number of bottle states per feeding length



```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = num_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of bouts per length of feeding") +
  facet_wrap(~Behavior)
  
ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Number of bouts per length of feeding") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


# Total duration in bottle state by dyad





```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = total_duration, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total duration of dyad bouts (sec)") +
  facet_wrap(~Behavior)
  
ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = total_duration, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total duation of dyad bouts (sec)") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_duration),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```




## Total fraction of feeding time spent in bottle state by dyad





```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = total_fraction, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total fraction of feeding time spent in state") +
  facet_wrap(~Behavior)
  
ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = total_fraction, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total fraction of feeding time spent in state") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_fraction),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

# All maternal behaviors: dyad totals

## Number of occurrences of each point behavior per dyad, including 0s


```{r}



for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior) %>%
    filter()
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each behavior per dyad, including 0s

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



## Proportion of dyads that express the behavior at least once during feeding, by age

```{r}

data_proportion_behavior_occurs <-
  data_dyad_total_zeros %>%
  filter(Behavior %in% mom_behaviors) %>%
  mutate(behavior_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, Behavior, behavior_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = behavior_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_behavior = `TRUE` / (`TRUE` + `FALSE`))

ggplot(data_proportion_behavior_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_behavior, mean),
           x = proportion_dyads_with_behavior,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of mothers that express the behavior") +
  ylab("Maternal behavior") +
  ggtitle("Proportion of mothers that express behavior\n at least once during feeding")

```




## Number of occurrences of each behavior per dyad, only mothers that express behavior

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior) %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each behavior per dyad, only mothers that express behavior

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```


# State behaviors, total duration of feeding time in state (only for mothers that exhibit the behavior)

```{r}

for (selected_behavior in intersect(state_behaviors, mom_behaviors)) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Total duration (sec)") +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


# State behaviors, total proportion of feeding time in state (only for mothers that exhibit the behavior)


```{r}

for (selected_behavior in intersect(state_behaviors, mom_behaviors)) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```





# END

```{r}
knitr::knit_exit()
```

# READ THIS FOR INTERACTIONS

To find the first mom response after infant cue

- filter the infant cues, only need cue and time
- join the filtered infant cues back with the full data: left_join(full data, cues)
- fill the NAs with the time of the most recent cue and the cue
- group_by(dyad_set, id, recent_cue, recent_time)
- filter the first mom response for each cue

## Individual dyads across age (for dyads observed at multiple ages)


```{r, include = FALSE}

video_lengths_individual <-
  inner_join(video_lengths, data_map, by = "id") %>%
  filter(time_points > 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_video_length = max(video_length),
         min_video_length = min(video_length),
         ratio = max_video_length / min_video_length,
         range = max_video_length - min_video_length) %>%
    filter(row_number() == 1)
```




```{r,  fig.show="hold", out.width="50%"}

ggplot(video_lengths_individual, 
         aes(x = ratio)) +
  geom_histogram(aes(y=..density..), binwidth = 0.25) +
  geom_rug() + 
  xlab("ratio of length of longest video to shortest video")

ggplot(video_lengths_individual,
       aes(x = min_video_length,
           y = max_video_length,
           color = ratio,
           shape = Bottle_Rejector)) +
  geom_point() +
  scale_color_gradient(low="blue", high="orange") +
  xlim(0, NA) +
  ylim(0, NA) +
  xlab("shortest video length") +
  ylab("longest video length") +
  ggtitle("Infants observed at multiple ages") +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines) +
  scale_shape_manual(values = c(1, 4))

```

```{r}

video_lengths_individual %>%
  ungroup() %>%
  summarize_at(vars(ratio),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```



```{r, include = TRUE}

video_lengths_individual <-
  inner_join(video_lengths, data_map, by = "id") %>%
  filter(time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_video_length = max(video_length),
         min_video_length = min(video_length),
         range_video_length = max_video_length - min_video_length) %>%
  ungroup()

ggplot(video_lengths_individual %>%
         mutate(id = fct_reorder(id, range_video_length)),
       aes(x = id, y = video_length, col = dyad_set)) +
  coord_flip() +
  ggtitle("Infants observed at all time points") +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))

```






# Total number of cues

```{r}
# total number of cues and types of cues

data_dyad_total_cues <- data_dyad_total_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length)

```

## Number of infant cues in feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding")
                 
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Number of cues per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding")
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```



## Number of infant cues in feeding, excluding Crying and Eyes Closed

```{r}

data_dyad_total_cues_point <- data_dyad_total_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  filter(Behavior %in% intersect(cues, point_behaviors)) %>%
  group_by(dyad_set, id) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length))

ggplot(data_dyad_total_cues_point,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
                 
```

```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Number of cues per length of feeding, excluding Crying and Eyes Closed

```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
                 
```



```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


# Number of different types of cues

## Number of types

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues")

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```

## Number of types per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_types_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of different types divided by length of feeding")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))  +
  ylab("Number of different types divided by length of feeding")
                 
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_types_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```

# Individual cues



## Number of occurrences of each cue per dyad, including 0s





```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, including 0s

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



## Proportion of dyads that express the cue at least once during feeding, by age

```{r}

data_proportion_cue_occurs <-
  data_dyad_total_zeros %>%
  filter(Behavior %in% cues) %>%
  mutate(cue_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, Behavior, cue_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = cue_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_cue = `TRUE` / (`TRUE` + `FALSE`))

ggplot(data_proportion_cue_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_cue, mean),
           x = proportion_dyads_with_cue,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of infants that express the cue") +
  ylab("Infant cue") +
  ggtitle("Proportion of infants that express cue\n at least once during feeding")

```




## Number of occurrences of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue) %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```
# Crying and Eyes Closed

## Crying and Eyes Closed, total time (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


## Crying and Eyes Closed, total proportion of feeding time in state (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```





# Individual infants across ages (only for infants observed at more than 1 age)


## Total number of cues per length


```{r, include = FALSE}

cues_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(time_points > 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues_per_length),
         min_value = min(num_cues_per_length),
         range = max_value - min_value,
         ratio = max_value / min_value) %>%
  filter(row_number() == 1)

```




```{r,  fig.show="hold", out.width="50%"}

ggplot(cues_individual, 
         aes(x = ratio)) +
  geom_histogram(aes(y=..density..), binwidth = 0.25) +
  geom_rug() + 
  xlab("Ratio of largest to smallest cue rate")

ggplot(cues_individual,
       aes(x = min_value,
           y = max_value,
           color = ratio,
           shape = Bottle_Rejector)) +
  geom_point() +
  scale_color_gradient(low="blue", high="orange") +
  xlim(0, NA) +
  ylim(0, NA) +
  xlab("Smallest cue rate") +
  ylab("Largest cue rate") +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines)  +
  scale_shape_manual(values = c(1, 4))

```

```{r, include = TRUE}

cues_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues_per_length),
         min_value = min(num_cues_per_length),
         range = max_value - min_value,
         ratio = max_value / min_value) %>%
  ungroup()


ggplot(cues_individual %>%
         mutate(id = fct_reorder(id, range)),
       aes(x = id, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  ggtitle("Infants observed at all time points") +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))

```

## Individual cues, only for infants that express the cue at least once at multiple ages


```{r}

for (selected_cue in cues) {
  
  selected_cue_individual <-
    inner_join(data_dyad_total_zeros %>%
                 filter(Behavior == selected_cue),
               data_map, by = "id") %>%
    filter(time_points > 1) %>%
    ungroup() %>%
    group_by(id) %>%
    mutate(max_value = max(num_per_length),
           min_value = min(num_per_length)) %>%
    filter(min_value > 0) %>%
    mutate(range = max_value - min_value,
           ratio = max_value / min_value) %>%
    filter(row_number() == 1)
  
  
  p1 <- ggplot(selected_cue_individual, 
               aes(x = ratio)) +
    geom_histogram(aes(y=..density..), binwidth = 0.25, na.rm = TRUE) +
    geom_rug() + 
    xlab("Ratio of largest to smallest cue rate")  +
    ggtitle(selected_cue)
  
  p2 <- ggplot(selected_cue_individual,
               aes(x = min_value,
                   y = max_value,
                   color = ratio,
                   shape = Bottle_Rejector)) +
    geom_point() +
    scale_color_gradient(low="blue", high="orange") +
    xlim(0, NA) +
    ylim(0, NA) +
    xlab("Smallest cue rate") +
    ylab("Largest cue rate") +
    geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines)  +
    scale_shape_manual(values = c(1, 4))  +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- selected_cue_individual %>% 
    ungroup() %>%
    summarize_at(vars(ratio),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 2))
  cat('\n')
  
}

```






## Total number of different types of cues


```{r, include = FALSE}

types_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(time_points > 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(num_types),
         min_value = min(num_types),
         range = max_value - min_value,
         ratio = max_value / min_value) %>%
  filter(row_number() == 1)

```

```{r}
ggplot(types_individual) +
   geom_mosaic(aes(x = product(min_value, max_value), fill=factor(min_value))) +    theme(axis.text.x=element_text(angle=-25, hjust= .1)) +
  labs(x="Min ", title='xxx', y = "max") +
  guides(fill=guide_legend(title = "min", reverse = TRUE))

```
































































```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue) %>%
    mutate(cue_occurs = (num_occurrences > 0)) %>%
    group_by(dyad_set, cue_occurs) %>%
    summarize(count = n())
  
  ggplot(data_dyad_total_zeros_selected_cue,
         aes(x = dyad_set, y = count, fill = cue_occurs)) +
  geom_bar(position="fill", stat="identity") +
  ylab("Proportion of dyads")

  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```

```{r}

data_crying_total <- data_dyad_total %>% 
  filter(Behavior %in% c("Crying", "Not Crying")) %>%
  group_by(dyad_set, Behavior) %>%
  summarize(num_dyads = n()) %>%
  pivot_wider(names_from = Behavior, values_from = num_dyads) %>%
  rename(Total = `Not Crying`) %>% 
  mutate(No_Crying = Total - Crying) %>%
  select(-Total)

data_crying_total %>%
  kable()

```









































```{r}
cues_point <- intersect(cues, point_behaviors)
```





## Individual dyads





```{r}
cues_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(Time_points > 1)  %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_num_cues = max(num_cues),
         min_num_cues = min(num_cues),
         range_num_cues = max_num_cues - min_num_cues,
         max_num_types = max(num_types),
         min_num_types = min(num_types),
         range_num_types = max_num_types - min_num_types,
         max_cues_per_length = max(num_cues_per_length),
         min_cues_per_length = min(num_cues_per_length),
         range_cues_per_length = max_cues_per_length - min_cues_per_length,
         max_types_per_length = max(num_types_per_length),
         min_types_per_length = min(num_types_per_length),
         range_types_per_length = max_types_per_length - min_types_per_length) %>%
    filter(row_number() == 1) %>%
  select(-c(dyad_set, num_cues, num_types, cues_per_length, num_types_per_length))
```


```{r}
ggplot(cues_individual %>%
         mutate(ratio = max_num_cues / min_num_cues),
       aes(x = ratio, y = ..density..)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.25, alpha=0.3, position = "identity") +
  geom_rug(sides = "b", aes(y = 0)) +
  labs(x = "Ratio of largest to smallest total number of cues")

ratio_lines = seq(1.0, 5.0, 0.5)


ggplot(cues_individual,
       aes(x = min_num_cues, y = max_num_cues, shape = Bottle_Rejector)) +
  geom_point() +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines) + 
      labs(x = "Smallest total number of cues",
         y = "Largest total number of cues")

```


```{r}
cues_individual_all_times <-
  inner_join(data_cues_dyad_total, data_map, by = "id") %>%
  filter(Time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_num_cues = max(num_cues),
         min_num_cues = min(num_cues),
         range_num_cues = max_num_cues - min_num_cues) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, range_num_cues))

ggplot(cues_individual_all_times,
       aes(x = id, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))


```



# Crying

## Crying (time)

```{r}

data_crying_total <- data_dyad_total %>% 
  filter(Behavior %in% c("Crying", "Not Crying")) %>%
  group_by(dyad_set, Behavior) %>%
  summarize(num_dyads = n()) %>%
  pivot_wider(names_from = Behavior, values_from = num_dyads) %>%
  rename(Total = `Not Crying`) %>% 
  mutate(No_Crying = Total - Crying) %>%
  select(-Total)

data_crying_total %>%
  kable()

```



```{r}

data_crying_total <- data_dyad_total %>% 
  filter(Behavior %in% c("Crying", "Not Crying")) %>%
  group_by(dyad_set, Behavior) %>%
  summarize(num_dyads = n()) %>%
  pivot_wider(names_from = Behavior, values_from = num_dyads) %>%
  rename(Total = `Not Crying`) %>% 
  mutate(No_Crying = Total - Crying) %>%
  select(-Total)

data_crying_total %>%
  kable()

data_crying_total <- data_crying_total %>%
  pivot_longer(!dyad_set, names_to = "Some_Crying", values_to = "num_dyads")

ggplot(data_crying_total,
       aes(fill=Some_Crying, y=num_dyads, x=dyad_set)) + 
  geom_bar(position="fill", stat="identity") +
  ylab("Proportion of dyads")



```




```{r}
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Crying")) ,
       aes(x = total_duration, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Crying")),
       aes(x = dyad_set, y = total_duration, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_dyad_total %>% 
  filter(Behavior %in% c("Crying")) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(total_duration),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Crying (fraction)




```{r}
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Crying")) ,
       aes(x = total_fraction, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Crying")),
       aes(x = dyad_set, y = total_fraction, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_dyad_total %>% 
  filter(Behavior %in% c("Crying")) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(total_fraction),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```


## Here are the babies that spend over 50% of the feeding Crying.

```{r}
data_dyad_total %>% 
  filter(Behavior %in% c("Crying")) %>%
  filter(total_fraction > 0.5) %>%
  select(dyad_set, id, Behavior, total_fraction) %>%
  arrange(desc(total_fraction)) %>%
  kable(digits = 3)
```


## Individual dyads across age (for dyads observed at multiple ages)



```{r}
crying_individual <-
  left_join(data_ids,
            data_dyad_total %>% filter(Behavior == "Crying"),
            by = c("dyad_set", "id")) %>% 
  mutate(Behavior = "Crying") %>% 
  mutate(
    across(where(is.numeric), ~replace_na(.x, 0))
  )%>%
  filter(Time_points > 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_fraction = max(total_fraction),
         min_fraction = min(total_fraction),
         range_fraction = max_fraction - min_fraction) %>%
  filter(row_number() == 1)

```


```{r,  fig.show="hold", out.width="50%"}

ggplot(crying_individual %>%
         mutate(ratio = max_fraction / min_fraction),
       aes(x = ratio, y = ..density..)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.25, alpha=0.3, position = "identity") +
  geom_rug(sides = "b", aes(y = 0)) +
  labs(x = "Ratio of longest to shortest fraction of time Crying")

ratio_lines = seq(1.0, 5.0, 0.5)

ggplot(crying_individual,
       aes(x = min_fraction, y = max_fraction, shape = Bottle_Rejector)) +
  geom_point() +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines) +
      labs(x = "Shortest fraction Crying",
         y = "Longest fraction Crying",
         color = "Legend") +
    scale_color_manual(values = ratio_lines)

```


## Eyes Closed (time)



```{r}

data_eyes_total <- data_dyad_total %>% 
  filter(Behavior %in% c("Eyes Closed", "Eyes Open")) %>%
  group_by(dyad_set, Behavior) %>%
  summarize(num_dyads = n()) %>%
  pivot_wider(names_from = Behavior, values_from = num_dyads) %>%
  rename(Total = `Eyes Open`) %>% 
  mutate(No_Eyes_Closed = Total - `Eyes Closed`) %>%
  select(-Total)

data_eyes_total %>%
  kable()

data_eyes_total <- data_eyes_total %>%
  pivot_longer(!dyad_set, names_to = "Eyes", values_to = "num_dyads")

ggplot(data_eyes_total,
       aes(fill = Eyes, y = num_dyads, x = dyad_set)) + 
  geom_bar(position = "fill", stat = "identity") +
  ylab("Proportion of dyads")



```




```{r}
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Eyes Closed")) ,
       aes(x = total_duration, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Eyes Closed")),
       aes(x = dyad_set, y = total_duration, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_dyad_total %>% 
  filter(Behavior %in% c("Eyes Closed")) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(total_duration),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Eyes Closed (fraction)




```{r}
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Eyes Closed")) ,
       aes(x = total_fraction, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total %>% 
         filter(Behavior %in% c("Eyes Closed")),
       aes(x = dyad_set, y = total_fraction, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_dyad_total %>% 
  filter(Behavior %in% c("Eyes Closed")) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(total_fraction),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```

# On average, how many cues do babies display at each age? Does this change over time?



```{r}
# Totals for cues of each type per dyad

data_cues <- data_duration %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id, Behavior) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length)

# Dyad totals; total number of cues and number of different types of cues

data_cues_dyad_total <- data_cues %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior),
            cues_per_length = sum(num_per_length),
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length)

```




## Total number of cues




```{r}
ggplot(data_cues_dyad_total,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_cues_dyad_total,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_cues_dyad_total %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Dyads with the most infant cues.

```{r}
data_cues_dyad_total %>%
  arrange(desc(num_cues)) %>%
  select(dyad_set, id, num_cues) %>%
  head(10) %>%
  kable()
```



```{r}
cues_individual <-
  inner_join(data_cues_dyad_total, data_map, by = "id") %>%
  filter(Time_points > 1)  %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_num_cues = max(num_cues),
         min_num_cues = min(num_cues),
         range_num_cues = max_num_cues - min_num_cues,
         max_num_types = max(num_types),
         min_num_types = min(num_types),
         range_num_types = max_num_types - min_num_types,
         max_cues_per_length = max(cues_per_length),
         min_cues_per_length = min(cues_per_length),
         range_cues_per_length = max_cues_per_length - min_cues_per_length,
         max_types_per_length = max(num_types_per_length),
         min_types_per_length = min(num_types_per_length),
         range_types_per_length = max_types_per_length - min_types_per_length) %>%
    filter(row_number() == 1) %>%
  select(-c(dyad_set, num_cues, num_types, cues_per_length, num_types_per_length))
```


```{r}
ggplot(cues_individual %>%
         mutate(ratio = max_num_cues / min_num_cues),
       aes(x = ratio, y = ..density..)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.25, alpha=0.3, position = "identity") +
  geom_rug(sides = "b", aes(y = 0)) +
  labs(x = "Ratio of largest to smallest total number of cues")

ratio_lines = seq(1.0, 5.0, 0.5)


ggplot(cues_individual,
       aes(x = min_num_cues, y = max_num_cues, shape = Bottle_Rejector)) +
  geom_point() +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines) + 
      labs(x = "Smallest total number of cues",
         y = "Largest total number of cues")

```


```{r}
cues_individual_all_times <-
  inner_join(data_cues_dyad_total, data_map, by = "id") %>%
  filter(Time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_num_cues = max(num_cues),
         min_num_cues = min(num_cues),
         range_num_cues = max_num_cues - min_num_cues) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, range_num_cues))

ggplot(cues_individual_all_times,
       aes(x = id, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))


```



## Total number of cues per video length (cue rate)




```{r}
ggplot(data_cues_dyad_total,
       aes(x = cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_cues_dyad_total,
       aes(x = dyad_set, y = cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_cues_dyad_total %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```


```{r}
ggplot(cues_individual,
       aes(x = min_cues_per_length, y = max_cues_per_length, shape = Bottle_Rejector)) +
  geom_point() +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "orange")

```



```{r}
ggplot(cues_individual_all_times,
       aes(x = id, y = cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))
```



## By Cue

```{r}

cues_point <- intersect(cues, point_behaviors)

for (selected_cue in cues_point) {
  
  data_selected_cue_total <- left_join(data_ids, data_dyad_total %>% filter(Behavior == selected_cue), by = c("dyad_set", "id")) %>% 
    mutate(Behavior = selected_cue) %>% 
    mutate(
      across(where(is.numeric), ~replace_na(.x, 0))
    )
  
  p1 <- ggplot(data_selected_cue_total,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences in feeding") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_selected_cue_total,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences in feeding") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_selected_cue_total %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```






# On average, how many different *types* of cues do babies display at each age? Does this change over time?

## Total number of types


```{r}

ggplot(data_cues_dyad_total,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues")

```






```{r}
ggplot(cues_individual,
       aes(x = min_num_types, y = max_num_types, shape = Bottle_Rejector)) +
  geom_jitter(width = 0.1, height = 0.1) +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "orange")

```



```{r}
ggplot(cues_individual_all_times,
       aes(x = id, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_jitter(aes(shape = Bottle_Rejector), width = 0, height = 0.1) +
  scale_shape_manual(values = c(1, 4))
```

## Total number of *types* per video length



```{r}
ggplot(data_cues_dyad_total,
       aes(x = num_types_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_cues_dyad_total,
       aes(x = dyad_set, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```



```{r}

data_cues_dyad_total %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_types_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```





```{r}
ggplot(cues_individual,
       aes(x = min_types_per_length, y = max_types_per_length, shape = Bottle_Rejector)) +
  geom_point() +
  scale_shape_manual(values = c(1, 4)) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "orange")

```



```{r}
ggplot(cues_individual_all_times,
       aes(x = id, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))
```






