---
title: 'Bottle Feeding: Descriptive Statistics'
author: "Kevin Ross"
date: "`r Sys.Date()`"
output: html_document
---

NEED TO REDO THE DYAD TOTALS TO INCLUDE 0 COUNTS FOR BEHAVIORS

```{r setup}
source("shared_setup.R")
```


<!-- # Dyad totals -->

<!-- - Number of occurrences of each behavior for each dyad in each set, and -->
<!-- - Number of occurrences divided by video length -->

```{r dyad-totals}

data_dyad_total <- data_duration %>%
  group_by(dyad_set, id, Behavior, dyad_unit) %>%
  summarize(Event_Type = first(Event_Type),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length)

# State behaviors only

data_dyad_total_states <- data_dyad_total %>%
  filter(Event_Type == "State start")

data_dyad_total_points <- data_dyad_total %>%
  filter(Event_Type == "State point")

```

THE NEXT CHUNK NEEDS TO BE FIXED (OR DELETED IF NOT NEEDED)

```{r dyad-totals-by-bottle-state, eval = FALSE, include = FALSE}

data_duration_by_bottle_state <- data %>%
  mutate(end_time = time + duration) %>%
  group_by(dyad_set, id, Bottle_state) %>%
  mutate(duration_fraction = duration / max(end_time),
         start_fraction = time / max(end_time),
         end_fraction = end_time / max(end_time),
         bottle_state_length = max(end_time)) %>%
  filter(Event_Type %in% c("State start", "State point"))

data_dyad_total_by_bottle_state <- data_duration_by_bottle_state %>%
  group_by(dyad_set, id, Bottle_state, Behavior) %>%
  summarize(Event_Type = first(Event_Type),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length)

# State behaviors only

data_dyad_total_states <- data_dyad_total %>%
  filter(Event_Type == "State start")

data_dyad_total_points <- data_dyad_total %>%
  filter(Event_Type == "State point")

```



<!-- ## Grouped behaviors -->

```{r dyad-grouped}

data_dyad_grouped <- data_duration %>%
  group_by(dyad_set, id, Grouped_behavior, dyad_unit) %>%
  summarize(Event_Type = first(Event_Type),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length)) %>%
  mutate(num_per_length = num_occurrences / video_length)

# State behaviors only

data_dyad_grouped_states <- data_dyad_grouped %>%
  filter(Event_Type == "State start")

data_dyad_grouped_points <- data_dyad_grouped %>%
  filter(Event_Type == "State point")

```


# Timeline plot for all dyads


```{r timeline-plot-data, fig.width = 10}

data_duration_plot <- data_duration %>%
  select(dyad_set, id, dyad_unit, Behavior, Event_Type, time, end_time) %>%#,
#         start_fraction, end_fraction, end_time) %>%
  mutate(Behavior = fct_relevel(Behavior, sort)) %>%
  mutate(row_id = row_number()) %>%
  gather("state", "time", c(time, end_time)) %>%
  arrange(dyad_set, id, Behavior, time)

```


animation.hook="ffmpeg"

fig.show='animate'

```{r, timeline-gif, animation.hook="gifski", interval=2.5, fig.width=10, cache = TRUE}

ids = sort(unique(data_duration$id))

for (id_to_view in ids) {
  p <- ggplot(data_duration_plot %>%
                filter(id == id_to_view) %>%
                filter(Event_Type == "State start"),
              aes(x = time,
                  y = Behavior,
                  group = row_id,
                  color = dyad_unit)) + 
    geom_line(size = 3) +
    ggtitle(paste("dyad", id_to_view)) +
    geom_point(data = data_duration_plot %>%
                 filter(id == id_to_view) %>%
                 filter(Event_Type == "State point"),
               aes(x = time, color = dyad_unit)) +
    xlab("Time (sec)") +
    ylab("Behavior") +
    facet_wrap(vars(dyad_set))
  
  plot(p)
}
```



# State behaviors

## Time as fraction


```{r plot-fraction-states}

ggplot(data_dyad_total_states,
       aes(x = fct_reorder(Behavior, total_fraction, median, .desc = TRUE),
           y = total_fraction)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State behavior") +
  ylab("Total duration of occurrence in [0, 1]") +
  facet_wrap(~dyad_set)
# +
#  geom_jitter(aes(color = dyad_unit))

```

```{r plot-fraction-bottle}

Bottle_positions <- c("Bottle in mouth",
                      "Bottle not in mouth",
                      "Bottle offered")

ggplot(data_dyad_total_states %>%
         filter(Behavior %in% Bottle_positions),
       aes(total_fraction, fill = Behavior)) +
  geom_histogram(aes(y = ..density..)) +
  xlab("Total duration ([0, 1])") +
  facet_grid(dyad_set ~ .)
# +
#  geom_jitter(aes(color = dyad_unit))

```

```{r summary-fraction, message = FALSE}

data_dyad_total_states %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_fraction),
               list(~length(.), ~mean(.), ~sd(.), ~min(.),
                    ~median(.), ~max(.))) %>%
  kable(digits = 3)

```


```{r, eval = FALSE, include = FALSE}

ggplot(data_dyad_total_states,
       aes(total_fraction, fill = Behavior)) +
  geom_histogram(aes(y = ..density..)) +
  xlab("Total duration ([0, 1])") +
  facet_grid(dyad_set ~ .)

```

## Time as seconds

```{r plot-duration}

ggplot(data_dyad_total_states,
       aes(x = fct_reorder(Behavior, total_duration, median, .desc = TRUE),
           y = total_duration)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State behavior") +
  ylab("Total duration of occurrence (sec)") +
  facet_wrap(~dyad_set)
# +
#  geom_jitter(aes(color = dyad_unit))


```

```{r}

ggplot(data_dyad_total_states %>%
         filter(Behavior %in% Bottle_positions),
       aes(total_duration, fill = Behavior)) +
  geom_histogram(aes(y = ..density..)) +
  xlab("Total duration of occurrence (sec)") +
  facet_grid(dyad_set ~ .)
# +
#  geom_jitter(aes(color = dyad_unit))
```


```{r summary-duration, message = FALSE}

data_dyad_total_states %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_duration),
               list(~length(.), ~mean(.), ~sd(.),
                    ~min(.), ~median(.), ~max(.))) %>%
  kable(digits = 1)

```



```{r, eval = FALSE, include = FALSE}

ggplot(data_dyad_total_states,
       aes(total_duration, fill = Behavior)) +
  geom_histogram(aes(y = ..density..)) +
  xlab("Total duration (sec)") +
  facet_grid(dyad_set ~ .)

```



# Point behaviors: counts



```{r}

ggplot(data_dyad_total_points,
       aes(x = fct_reorder(Behavior, num_occurrences),
           y = num_occurrences)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State point") +
  ylab("Number of occurrences (per dyad)") +
  facet_grid(~ dyad_set)
# +
#  geom_jitter()

```





```{r}

data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_occurrences),
               list(~sum(.), ~mean(.), ~sd(.),
                    ~min(.), ~median(.), ~max(.))) %>%
  arrange(dyad_set, desc(sum)) %>%
  kable(digits = 1)
  

```


## Grouped behaviors



```{r}

ggplot(data_dyad_grouped_points %>%
         filter(dyad_unit == "Mom"),
       aes(x = fct_reorder(Grouped_behavior, num_occurrences),
           y = num_occurrences)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State point") +
  ylab("Number of occurrences (per dyad)") +
  facet_wrap(~ dyad_set)
# +
#  geom_jitter()

```





```{r}

data_dyad_grouped_points %>%
  ungroup() %>%
  group_by(dyad_set, Grouped_behavior) %>%
  summarize_at(vars(num_occurrences),
               list(~sum(.), ~mean(.), ~sd(.),
                    ~min(.), ~median(.), ~max(.))) %>%
  arrange(dyad_set, desc(sum)) %>%
  kable(digits = 1)
  

```




# Point behaviors: count per video length



```{r}

ggplot(data_dyad_total_points,
       aes(x = fct_reorder(Behavior, num_per_length),
           y = num_per_length*60)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State point") +
  ylab("Number of occurrences per minute (per dyad)") +
  facet_grid(cols = vars(dyad_set))
# +
#  geom_jitter()

```





```{r}

data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_per_length),
               list(~sum(.), ~mean(.), ~sd(.),
                    ~min(.), ~median(.), ~max(.))) %>%
  arrange(dyad_set, desc(sum)) %>%
  kable(digits = 4)
  

```

## Grouped behaviors


```{r}

ggplot(data_dyad_grouped_points %>%
         filter(dyad_unit == "Mom"),
       aes(x = fct_reorder(Grouped_behavior, num_per_length),
           y = num_per_length)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("State point") +
  ylab("Number of occurrences / video length (per dyad)") +
  facet_wrap(~ dyad_set)
# +
#  geom_jitter()

```


```{r}

data_dyad_grouped_points %>%
  ungroup() %>%
  group_by(dyad_set, Grouped_behavior) %>%
  summarize_at(vars(num_per_length),
               list(~sum(.), ~mean(.), ~sd(.),
                    ~min(.), ~median(.), ~max(.))) %>%
  arrange(dyad_set, desc(sum)) %>%
  kable(digits = 4)
  

```

# Point behaviors: time of occurrence

```{r}

point_times <- data_duration %>%
  filter(Event_Type == "State point") %>%
  group_by(id, dyad_set, dyad_unit, Behavior)

ggplot(point_times,
       aes(x = fct_reorder(Behavior, start_fraction, median, .desc = TRUE),
                       y = start_fraction)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("Point behavior") +
  ylab("Time of occurrence in [0, 1]") +
  facet_wrap(~ dyad_set)

```

## Grouped behaviors

```{r}

point_times <- data_duration %>%
  filter(Event_Type == "State point") %>%
  group_by(id, dyad_set, dyad_unit, Grouped_behavior)

ggplot(point_times,
       aes(x = fct_reorder(Grouped_behavior, start_fraction, median, .desc = TRUE),
                       y = start_fraction)) +
  geom_boxplot(aes(color = dyad_unit)) +
  coord_flip() +
  xlab("Point behavior group") +
  ylab("Time of occurrence in [0, 1]") +
  facet_wrap(~ dyad_set)

```

# Point behaviors: Mom vs Baby total counts

```{r}

dyad_unit_total_points <- data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, id, dyad_unit) %>%
  summarize(total_point_count = sum(num_occurrences)) %>%
  pivot_wider(names_from = dyad_unit,
              values_from = total_point_count)


ggplot(dyad_unit_total_points,
       aes(x = Baby, y = Mom, label = id)) +
  geom_point() +
  geom_text(size = 3, hjust = 0, nudge_x = 0.05) +
  xlab("Total number of point behaviors for Baby") +
  ylab("Total number of point behaviors for Mom") +
  facet_wrap(~ dyad_set)


```



```{r}

dyad_unit_total_points_per_length <- data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, id, dyad_unit) %>%
  summarize(total_point_count_per_length = sum(num_occurrences) / max(video_length)) %>%
  pivot_wider(names_from = dyad_unit,
              values_from = total_point_count_per_length)


ggplot(dyad_unit_total_points_per_length,
       aes(x = Baby, y = Mom, label = id)) +
  geom_point() +
  geom_text(size = 3, hjust = 0, nudge_x = 0) +
  xlab("Total number of point behaviors per video length for Baby") +
  ylab("Total number of point behaviors per video length for Mom") +
  facet_wrap(~ dyad_set)



```



## Log scale


```{r}

dyad_unit_total_points <- data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, id, dyad_unit) %>%
  summarize(total_point_count = sum(num_occurrences)) %>%
  pivot_wider(names_from = dyad_unit,
              values_from = total_point_count)


ggplot(dyad_unit_total_points,
       aes(x = Baby, y = Mom, label = id)) +
  geom_point() +
  geom_text(size = 3, hjust = 0, nudge_x = 0.05) +
  scale_y_continuous(trans = "log10") +
  scale_x_continuous(trans = "log10") +
  xlab("Total number of point behaviors for Baby (log10)") +
  ylab("Total number of point behaviors for Mom (log10)") +
  facet_wrap(~ dyad_set)


```



```{r}

dyad_unit_total_points_per_length <- data_dyad_total_points %>%
  ungroup() %>%
  group_by(dyad_set, id, dyad_unit) %>%
  summarize(total_point_count_per_length = sum(num_occurrences) / max(video_length)) %>%
  pivot_wider(names_from = dyad_unit,
              values_from = total_point_count_per_length)


ggplot(dyad_unit_total_points_per_length,
       aes(x = Baby, y = Mom, label = id)) +
  geom_point() +
  geom_text(size = 3, hjust = 0, nudge_x = 0) +
  scale_y_continuous(trans = "log10") +
  scale_x_continuous(trans = "log10") +
  xlab("Total number of point behaviors per video length for Baby (log10)") +
  ylab("Total number of point behaviors per video length for Mom (log10)") +
  facet_wrap(~ dyad_set)


```


# Mom responses to infant cues


```{r}

data_mom_response <- data_duration %>%
  ungroup() %>%
  group_by(dyad_set, id) %>%
  mutate(next_behavior = dplyr::lead(Grouped_behavior, n = 1, default = NA),
         next_time = dplyr::lead(time, n = 1, default = NA),
         next_unit = dplyr::lead(dyad_unit, n = 1, default = NA)) %>%
  filter(!Behavior %in% c("Eyes Open", "Not Crying")) %>%
  filter(!Grouped_behavior %in% c("Propped bottle", "Looks at phone or device")) %>%
  filter(dyad_unit == "Baby") %>%
  mutate(mom_response = as_factor(if_else(next_unit == "Baby", "No response", as.character(next_behavior)))) %>%
  mutate(response_time = next_time - time) %>%
  mutate(Behavior = fct_infreq(Behavior)) %>%
  ungroup() %>%
  mutate(mom_response2 = fct_lump_n(mom_response, 5)) %>%
  group_by(dyad_set, id)



ggplot(data_mom_response) +
  geom_mosaic(aes(x = product(mom_response2, Behavior),
                  fill=mom_response2), na.rm = TRUE) +
  facet_grid(rows = vars(dyad_set)) + 
  scale_y_productlist() + 
  scale_x_productlist() +
  labs(x = "Infant cue", y = "Mom response", 
       title='')

# write.csv(data_mom_response, "data-mom-response.csv")

```


## Mom response time for each infant cue


```{r, response-plot, animation.hook="gifski", interval=2.5, fig.width=10, cache = TRUE}

cues = sort(unique(data_mom_response$Behavior))

for (cue in cues) {
  p <- ggplot(data_mom_response %>%
                filter(Behavior == cue) %>%
                filter(!is.na(response_time)),
              aes(x = fct_reorder(mom_response2, response_time, median, .desc = TRUE),
                  y = response_time)) +
    geom_boxplot() +
    coord_flip() +
    xlab("Mom response") +
    ylab("Response time (sec)") +
    ggtitle(paste("Infant cue:", cue)) +
    facet_wrap(~dyad_set)
  
  plot(p)
}
```

## Mom response time for each infant cue: constant time axis

```{r, response-plot-fixed, animation.hook="gifski", interval=2.5, fig.width=10, cache = TRUE}

cues = sort(unique(data_mom_response$Behavior))
max_time = max(data_mom_response$response_time, na.rm = TRUE)

for (cue in cues) {
  p <- ggplot(data_mom_response %>%
                filter(Behavior == cue) %>%
                filter(!is.na(response_time)),
              aes(x = fct_reorder(mom_response2, response_time, median, .desc = TRUE),
                  y = response_time)) +
    geom_boxplot() +
    ylim(0, max_time) +
    coord_flip() +
    xlab("Mom response") +
    ylab("Response time (sec)") +
    ggtitle(paste("Infant cue:", cue)) +
    facet_wrap(~dyad_set)
  
  plot(p)
}
```

