---
title: 'Infant Cues - Across Ages - Feeding Split into Quarters - Non-Rejectors Only'
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    
---

This analysis excludes bottle rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```


<!-- ```{r, include = FALSE} -->

<!-- library(readr) -->
<!-- library(dplyr) -->
<!-- library(tidyr) # need devtools version ? -->
<!-- library(tibble) -->
<!-- library(ggplot2) -->

<!-- library(stringr) -->
<!-- library(purrr) -->
<!-- library(forcats) -->
<!-- library(knitr) -->
<!-- library(purrr) -->
<!-- library(ggpubr) -->
<!-- library(cowplot) -->
<!-- library(gridExtra) -->


<!-- library(gganimate) -->
<!-- # devtools::install_github('haleyjeppson/ggmosaic') -->
<!-- library(ggmosaic) -->


<!-- knitr::opts_chunk$set(echo = FALSE, -->
<!--                       message = FALSE, -->
<!--                       warning = FALSE) -->

<!-- # Vectorized sequence function -->
<!-- # seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...) -->
<!-- seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to")) -->

<!-- ratio_lines = seq(1, 4, 0.5) -->

<!-- ``` -->


<!-- ```{r, include = FALSE} -->

<!-- # Reorder dyad_set: 2wk, 2mo, 4mo, 6mo -->
<!-- dyad_set_levels <- c("2wkB", "2moB", "4moB", "6moB") -->

<!-- n_time_points = length(dyad_set_levels) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- theme_set(theme_minimal()) -->



<!-- cbPalette  <- c("#88CCEE", "#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499",  -->
<!--                              "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888") -->

<!-- color_theme <- scale_color_manual(values = cbPalette, -->
<!--                                   aesthetics = c("color", "fill")) -->

<!-- ``` -->


```{r, include = FALSE}

# Load data and select non-rejectors c(0), rejectors c(1), or all c(0, 1)

include_rejectors <- c(0)

data_dyad_total_time_split_zeros <- read_csv("data-dyad-total-time-split-zeros.csv") %>%
  mutate(dyad_set = factor(dyad_set, levels = dyad_set_levels),
         id = factor(id),
         time_split = factor(time_split),
         Bottle_Rejector = factor(Bottle_Rejector),
         num_per_min = num_per_length * 60) %>%
  filter(Bottle_Rejector %in% include_rejectors)
# %>% filter(time_split == 4)

data_map <- read_csv("data-map.csv") %>%
  mutate(id = factor(id))

if(1 %in% include_rejectors) {
  data_map <- data_map %>%
    mutate(time_points = Time_points_with_rejectors)
} else {
  data_map <- data_map %>%
    mutate(time_points = Time_points)
}

```


<!-- ```{r, include = FALSE} -->

<!-- behaviors <- data_dyad_total_zeros %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- state_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(Event_Type == "State start") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- point_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(Event_Type == "State point") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- cues <- data_dyad_total_zeros %>% -->
<!--   filter(Grouped_behavior == "Infant Satiation Cues") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- mom_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(dyad_unit == "Mom") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- bottle_states <- state_behaviors[grep("Bottle", state_behaviors)] -->

<!-- ``` -->

# Total number of cues

```{r}
# total number of cues and types of cues

data_dyad_total_cues <- data_dyad_total_time_split_zeros %>%
  filter(dyad_unit == "Baby") %>%
  # filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id, time_split) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            num_cues_per_min = num_cues_per_length * 60,
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length,
         num_types_per_min = num_types_per_length * 60)

```

## Split by quarter

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant cues in quarter") +
  labs(fill = "age", color = "age") +
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))
                 
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Comparison of quarters at each age

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant cues in quarter") +
  labs(fill = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_cues, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


# Cues per minute in each quarter

## Split by quarter

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_min, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant cues per minute in quarter") +
  labs(fill = "age", color = "age") +
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues_per_min, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues per minute in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

## Comparison of Quarters at each age

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_min, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant cues per minute in quarter") +
  labs(fill = "quarter", color = "quarter") +

  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_cues_per_min, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues per minute in quarter") +
  labs(x = "quarter", color = "quarter") +

  facet_wrap(vars(dyad_set))
                 
```




```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

# Number of point cues: excluding Crying and Eyes Closed


```{r}

data_dyad_total_cues_point <- data_dyad_total_time_split_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  filter(Behavior %in% intersect(cues, point_behaviors)) %>%
  group_by(dyad_set, id, time_split) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            num_cues_per_min = sum(num_per_min),
            video_length = max(video_length),
            time_split = first(time_split))
```



## Split by quarter


```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant point cues in quarter") +
  labs(fill = "age", color = "age") +
 
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant point cues in quarter") +
  labs(x = "age", color = "age") +

  facet_wrap(vars(time_split))
                 
```


```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```

## Comparison of Quarters at each age

```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant point cues in quarter") +
  labs(fill = "quarter", color = "quarter") +
 
  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues_point,
       aes(x = time_split, y = num_cues, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of point infant cues in quarter") +
  labs(x = "quarter", color = "quarter") +

  facet_wrap(vars(dyad_set))
                 
```



```{r}

data_dyad_total_cues_point %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


# Point cues per minute: excluding Crying and Eyes Closed

## Split by quarter


```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues_per_min, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant point cues per minute in quarter") +
  labs(fill = "age", color = "age") +
 
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues_per_min, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant point cues per minute in quarter") +
  labs(x = "age", color = "age") +

  facet_wrap(vars(time_split))
                 
```


```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

## Comparison of Quarters at each age

```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues_per_min, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of infant point cues per minute in quarter") +
  labs(fill = "quarter", color = "quarter") +
 
  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues_point,
       aes(x = time_split, y = num_cues_per_min, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of point infant cues per minute in quarter") +
  labs(x = "quarter", color = "quarter") +

  facet_wrap(vars(dyad_set))
                 
```




```{r}

data_dyad_total_cues_point %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```





# Total number of different types of cues



## Split by quarter

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues in quarter") +
  labs(color = "age") +
  facet_wrap(vars(time_split))

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of cues in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Comparison of quarters at each age

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = time_split)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues in quarter") +
  labs(color = "quarter") +

  facet_wrap(vars(dyad_set))

ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_types, col = time_split)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of cues in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))


```



```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```






# Types of cues per minute



## Split by quarter

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types_per_min,
           color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues per minute in quarter") +
  labs(color = "age", fill = "age") +
  facet_wrap(vars(time_split))

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types_per_min, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Number of different types of cues per minute in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_types_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```


## Comparison of quarters at each age

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types_per_min,
           color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues per minute in quarter") +
  labs(color = "quarter", fill = "quarter") +

  facet_wrap(vars(dyad_set))

ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_types_per_min, col = time_split)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of cues per minute in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))


```



```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_types_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```



# Proportion of dyads that express the cue at least once during quarter



```{r}
data_proportion_cue_occurs <-
  data_dyad_total_time_split_zeros %>%
  filter(Behavior %in% cues) %>%
  mutate(cue_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, time_split, Behavior, cue_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = cue_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_cue = `TRUE` / (`TRUE` + `FALSE`))
```

## Split by quarter

```{r}

ggplot(data_proportion_cue_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_cue, mean),
           x = proportion_dyads_with_cue,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of infants that express the cue") +
  ylab("Infant cue") +
  labs(col = "age") +
  ggtitle("Proportion of infants that express cue\n at least once during feeding") +

  facet_wrap(vars(time_split))

```


## Comparison of quarters at each age


```{r}

ggplot(data_proportion_cue_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_cue, mean),
           x = proportion_dyads_with_cue,
           col = time_split)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of infants that express the cue") +
  ylab("Infant cue") +
  labs(col = "quarter") +
  ggtitle("Proportion of infants that express cue\n at least once during feeding") +

  facet_wrap(vars(dyad_set))

```



# Individual cues: number of occurrences per minute in quarter

Only includes dyads who express the behavior at least once in quarter

## Split by quarter

```{r}

for (selected_cue in sort(cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of cue per minute in quarter") +
    labs(color = "age", fill = "age") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of cue per minute in quarter") +
    labs(color = "age") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_min, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of cue per minute in quarter") +
    labs(x = "age", col = "age") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)

  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set, time_split) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```




## Comparison of Quarters at each age


```{r}

for (selected_cue in sort(cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = time_split,
                   fill = time_split)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of cue per minute in quarter") +
    labs(color = "quarter", fill = "quarter") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = time_split)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of cue per minute in quarter") +
    labs(color = "quarter") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = time_split, y = num_per_min, col = time_split)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of cue per minute in quarter") +
    labs(x = "quarter", col = "quarter") +
    ggtitle(selected_cue) +
  
    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(time_split, dyad_set) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



```{r}
knitr::knit_exit()
```

# END

# Crying and Eyes Closed

Fraction of quarter spent in state?

## Crying and Eyes Closed, total time (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_cue) +
    color_theme
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue) +
    color_theme
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue) +
    color_theme
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


## Crying and Eyes Closed, total proportion of feeding time in state (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue) +
    color_theme
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue) +
    color_theme
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue) +
    color_theme
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



