---
title: 'Infant Cues - Across Ages - Whole Feeding - Non-Rejectors Only'
author: ""
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
source("shared_setup.R")
```


# Feeding length

```{r}
video_lengths <- data_dyad_total_zeros %>%
  group_by(dyad_set, id) %>%
  filter(video_length == max(video_length)) %>%
  filter(row_number() == 1) %>%
  select(id, dyad_set, video_length, Bottle_Rejector)

ggplot(video_lengths,
       aes(x = video_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(video_lengths,
       aes(x = dyad_set, y = video_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
```

```{r}

video_lengths %>%
  group_by(dyad_set) %>%
  summarize_at(vars(video_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```




# Total number of cues

```{r}
# total number of cues and types of cues

data_dyad_total_cues <- data_dyad_total_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length)

```

## Number of infant cues in feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding")
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Number of cues per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding")
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```



## Number of infant cues in feeding, excluding Crying and Eyes Closed

```{r}

data_dyad_total_cues_point <- data_dyad_total_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  filter(Behavior %in% intersect(cues, point_behaviors)) %>%
  group_by(dyad_set, id) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length))

ggplot(data_dyad_total_cues_point,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
                 
```

```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Number of cues per length of feeding, excluding Crying and Eyes Closed

```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed)")
                 
```



```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


# Number of different types of cues

## Number of types

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Number of dyads") +
  xlab("Number of different types of cues")

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```

## Number of types per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_types_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of different types divided by length of feeding")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))  +
  ylab("Number of different types divided by length of feeding")
                 
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_types_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```

# Individual cues



## Number of occurrences of each cue per dyad, including 0s





```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, including 0s

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)

  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



## Proportion of dyads that express the cue at least once during feeding, by age

```{r}
data_proportion_cue_occurs <-
  data_dyad_total_zeros %>%
  filter(Behavior %in% cues) %>%
  mutate(cue_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, Behavior, cue_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = cue_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_cue = `TRUE` / (`TRUE` + `FALSE`)) 

ggplot(data_proportion_cue_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_cue, mean),
           x = proportion_dyads_with_cue,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of infants that express the cue") +
  ylab("Infant cue") +
  ggtitle("Proportion of infants that express cue\n at least once during feeding")
```




## Number of occurrences of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue) %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)

  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```
# Crying and Eyes Closed

## Crying and Eyes Closed, total time (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


## Crying and Eyes Closed, total proportion of feeding time in state (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```

# END

```{r}
knitr::knit_exit()
```
