---
title: "infant_descriptive_statistics"
author: "William Medwid"
date: "7/9/2021"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

This analysis excludes bottle rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```

# Cues over the whole duration

```{r bar-grid}
# Many bar plots -----------


grid_plot <- function(used_behaviors, num_splits, behavior_group = ""){
  
  
  # Finds what proportion of dyads expressed each behavior at least once during each quarter
  n_dyads_cue <- data_duration %>% #Cue representation in dyads before the requested time period
    filter(Behavior %in% used_behaviors) %>% 
    mutate(split = get_time_split(start_fraction, num_splits)) %>% 
    distinct(Behavior, dyad_set, id, split) %>% #Removes repeated cues from the same infant within the same feeding
    group_by(dyad_set, split) %>% 
    count(Behavior) %>% 
    mutate(n_dyads = n) %>% 
    select(!n) %>% 
    left_join(dyad_set_counts) %>% 
    mutate(prop_dyads = n_dyads / count)
  

  n_dyads_cue %>% 
    ggplot(aes(y=prop_dyads, x = split)) +
    geom_bar(position="dodge", stat="identity") +
    facet_grid(reorder(Behavior, desc(prop_dyads))~dyad_set) +
    ggtitle(paste("Percent of infants expressing ", behavior_group, "behaviors in each 1/", num_splits, " of feeding", sep = ""))+
    xlab(str_c("1/", num_splits, " Split")) +
    ylab("Proportion expressing cue within period") +
    theme(strip.text.y.right = element_text(angle = 0)) +
    ylim(0, 0.6) %>% 
    return()
}

potent_behaviors <- behavior_codebook %>% 
    filter(Narrow_group == "Potent") %>% 
    pull(Behavior)
subtle_behaviors <- behavior_codebook %>% 
    filter(Narrow_group == "Subtle") %>% 
    pull(Behavior)
infant_behaviors = behavior_codebook %>% 
    filter(dyad_unit == "Baby") %>% 
    pull(Behavior)

grid_plot(potent_behaviors, 4, "potent ")
grid_plot(subtle_behaviors, 4, "subtle ")
grid_plot(potent_behaviors, 5, "potent ")
grid_plot(subtle_behaviors, 5, "subtle ")


```

Plot with only cues most skewed towards the end:

```{r}
best_predictors = c("Lip compression/does not open mouth", 
                    "Drools, spits out milk, spits up", 
                    "Pushes bottle away", "Leans away or arches back", 
                    "Shakes head or turns head/body away", 
                    "Gags, coughs, chokes",
                    "Crying")

grid_plot(best_predictors, 4)
```

### Swapped barplot grid

To compare dyad ages within each split.

```{r flipped-bar-grid}
# Many bar plots -----------

grid_plot <- function(group, num_splits){
  used_behaviors <- behavior_codebook %>% 
    filter(Narrow_group == group) %>% 
    pull(Behavior)
  
  n_dyads_cue <- data_duration %>% #Cue representation in dyads before the requested time period
    filter(Behavior %in% used_behaviors) %>% 
    mutate(split = get_time_split(start_fraction, num_splits)) %>% 
    distinct(Behavior, dyad_set, id, split) %>% #Removes repeated cues from the same infant within the same feeding
    group_by(dyad_set, split) %>% 
    count(Behavior) %>% 
    mutate(n_dyads = n) %>% 
    select(!n) %>% 
    left_join(dyad_set_counts) %>% 
    mutate(prop_dyads = n_dyads / count)
  

  n_dyads_cue %>% 
    ggplot(aes(y=prop_dyads, x = dyad_set)) +
    geom_bar(position="dodge", stat="identity") +
    facet_grid(reorder(Behavior, desc(prop_dyads))~split) +
    ggtitle(paste("Percent of infants expressing ", group, " behaviors in each 1/", num_splits, " of feeding", sep = ""))+
    xlab("Dyad set (column = split)") +
    ylab("Proportion expressing cue within period") +
    theme(strip.text.y.right = element_text(angle = 0)) +
    theme(axis.text.x = element_text(angle=90)) +
    ylim(0, 0.6) %>% 
    return()
}

grid_plot("Potent", 4)
grid_plot("Subtle", 4)
grid_plot("Potent", 5)
grid_plot("Subtle", 5)
```

These plots provide a more intutive comparison between behaviors in different quarters, fifths, or any other split desired. The same trends are visible in the previous "Relative cue pervailence in the final 25% of feeding" plot, but with even more detail. (Split by behavior group is just to keep the plots a readable size.)

## Comparing when different cues tend to be expressed by infants

```{r}
df_points <- data_duration %>% 
  filter(dyad_unit == "Baby" & Event_Type == "State point")

med_times <- df_points %>% 
  group_by(Behavior) %>% 
  summarise(med_time = median(start_fraction)) %>%
  arrange(med_time) %>% 
  pull(Behavior)

df_points %>% 
  ggplot(aes(y=factor(Behavior, levels=med_times), x=start_fraction*100)) +
  geom_violin()+
  geom_boxplot(width=0.2, outlier.shape = NA, coef = 0) +
  facet_grid(cols = vars(dyad_set)) +
  ylab("Behavior") +
  xlab("Percent of feeding completed") +
  ggtitle("Shape and center 50 percentile of cue Times")
```

Like the previous plot, this one finds the strongest indicator of satiation to be lip compression. This may be the best expression of where within the feeding session infants tend to express each cue, and allows us to see that many cues at different ages are expressed almost uniformly regardless of feeding progress. Those cues may still be important, but cannot be used on their own as indicators that an infant is satiated. Pushing nipple out with tongue or biting it appear to be more common at the start of feeding.


## Proportion of time in which behaviors are visible

```{r}
time_plot <- function(states){
  total_fractions <- data_duration %>%
    filter(Behavior %in% states) %>% 
    filter(Event_Type == "State start") %>%
    group_by(id, dyad_set, Behavior) %>% 
    summarise(total_fraction = sum(duration_fraction))
  
  total_fractions <- total_fractions %>% 
    expand(nesting(id, dyad_set), Behavior = states) %>%
    left_join(total_fractions, on=c(id, dyad_set, Behavior)) %>%
    replace_na(list(total_fraction = 0)) %>% 
    group_by(Behavior, dyad_set) %>% 
    summarise(mean_fraction = mean(total_fraction))
    
  #total_fractions %>% group_by(dyad_set) %>% summarise(s = sum(mean_fraction))
  
  total_fractions %>% 
    ggplot(aes(x=dyad_set, y=mean_fraction, group=Behavior, color=Behavior,
               linetype=Behavior)) +
    geom_path() + 
    geom_point() +
    ylab("Mean Fraction of Time in State") +
    xlab("Infant Age") +
    ylim(0, 1) + 
    ggtitle("Proportion of time exhibiting certain behaviors") %>% 
    return()
}

related <- list(
  c("Bottle in mouth", "Bottle offered", "Crying", "Eyes Closed"),
  c("Bottle not in mouth", "Bottle in mouth", "Bottle offered"),
  c("Crying", "Not Crying"),
  c("Eyes Closed", "Eyes Open"))

for (states in related){
  print(time_plot(states))
}
```

```{r}
total_fractions <- data_duration %>%
  filter(Behavior %in% c("Crying", "Eyes Closed", "Bottle in mouth")) %>% 
  filter(Event_Type == "State start") %>%
  group_by(id, dyad_set, Behavior) %>% 
  summarise(total_fraction = sum(duration_fraction))

total_fractions %>% 
  ggplot(aes(x = total_fraction, y = Behavior, col = dyad_set)) +
  geom_boxplot() +
  ggtitle("Time in states distribution (all non-rejector dyads)") +
  xlab("Total fraction of time in state")
```


## Group analysis

```{r}
df_points <- data_duration %>% 
  filter(dyad_unit == "Baby" & Event_Type == "State point")

med_times <- df_points %>% 
  group_by(Narrow_group) %>% 
  summarise(med_time = median(start_fraction)) %>%
  arrange(med_time) %>% 
  pull(Narrow_group)

df_points %>% 
  ggplot(aes(y=factor(Narrow_group, levels=med_times), x=start_fraction*100)) +
  geom_violin()+
  geom_boxplot(width=0.2, outlier.shape = NA, coef = 0) +
  facet_grid(cols = vars(dyad_set)) +
  ylab("Cue Type") +
  xlab("Percent of feeding completed") +
  ggtitle("Shape and center 50 percentile of cue Times")

df_points %>% 
  group_by(Narrow_group, dyad_set) %>% 
  summarise(mean=mean(start_fraction),
            sd = sd(start_fraction)) %>% 
  mutate(readout = paste("Mean: ", round(mean, 2), "SD: ", round(sd, 2))) %>% 
  pivot_wider(names_from = Narrow_group, values_from=readout, id_cols=dyad_set) %>% 
  kable(caption = "Mean and standard deviation of average cues for potent and subtle cues")
```

## Distributions of cues per minute

```{r}
line_plot <- function(group){
  p <- data_dyad_total_zeros %>% 
    filter(dyad_unit=="Baby") %>% 
    filter(Narrow_group==group) %>% 
    group_by(Behavior, dyad_set, Narrow_group) %>% 
    summarise(mean_per_min = round(mean(num_per_min), 2)) %>% 
    ggplot(aes(x=dyad_set, 
               y=mean_per_min, 
               color=Behavior,
               group=Behavior,
               linetype=Behavior)) +
    geom_point()+
    geom_line() +
    ylim(0,1)+
    ggtitle(paste("Overall", group, "cue frequencies")) +
    ylab("Average expressions per minute") +
    xlab("Baby age")
  
  p %>% ggplotly()
}
line_plot("Potent")
line_plot("Subtle")
```

## Proportional analysis

```{r}
line_plot <- function(group){
  p <- data_dyad_total_zeros %>% 
    mutate(any_occurances = if_else(num_occurrences>0, 1, 0)) %>% 
    filter(dyad_unit=="Baby") %>% 
    filter(Narrow_group==group) %>% 
    group_by(Behavior, dyad_set, Narrow_group) %>% 
    summarise(prop_occurances = round(mean(any_occurances), 2)) %>% 
    ggplot(aes(x=dyad_set, 
               y=prop_occurances, 
               color=Behavior,
               group=Behavior,
               linetype=Behavior)) +
    geom_point()+
    geom_line() +
    ylim(0, 1) +
    ggtitle(paste("Proportion of infants expressing", group, "cues")) +
    ylab("Proportion expressing cue at least once") +
    xlab("Baby age")
  
  p %>% ggplotly()
}

line_plot("Potent")
line_plot("Subtle")
```


## Cues/min analysis

Among infants expressing the cue, how often did they express the cue?

```{r cues_min_analysis}
#Commented out code separates outliers into a third plot, allowing easier comparisons.

give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

freq_boxplot <- function(data_dyad_total_zeros, Narrow_group_used, scaling){
  if(scaling == "(log base 2 scale)"){
    x_vals = log(data_dyad_total_zeros$num_per_min)
  } else{
    x_vals = data_dyad_total_zeros$num_per_min
  }
  
  data_dyad_total_zeros %>%
    mutate(x_vals = x_vals) %>% 
    filter(dyad_unit == "Baby") %>% 
    filter(Narrow_group == Narrow_group_used) %>%
    filter(num_per_min>0) %>% 
    group_by(Behavior, dyad_set) %>% 
    mutate(n_verbose = if_else(x_vals == max(x_vals),
                                                  paste("n = ", n()),
                                                  "")) %>%
    mutate(Behavior = reorder(Behavior, num_per_min)) %>% 
    ggplot(aes(y=Behavior, x=x_vals, col=dyad_set)) +
    geom_boxplot(outlier.alpha = 0.75, outlier.size = 1) +
    geom_text(aes(label = n_verbose), position = position_dodge(width = 1), hjust="inward") +
    ggtitle(paste(Narrow_group_used, "behhavior frequencies (excluding 0's)")) +
    xlab(paste("Cues per minute", scaling))
}

data_dyad_total_zeros %>% 
  freq_boxplot("Potent", "")

data_dyad_total_zeros %>% 
  freq_boxplot("Subtle", "")

data_dyad_total_zeros %>% 
  freq_boxplot("Potent", "(log base 2 scale)")

data_dyad_total_zeros %>% 
  freq_boxplot("Subtle", "(log base 2 scale)")
```




