---
title: 'Infant Cues - Within Dyad - Non-rejectors only'
author: ""
date: "`r Sys.Date()`"
output: html_document
---

This analysis excludes bottle rejectors.

FIX TO DO TOTAL NUMBER OF CUES BOTH WITH AND WITHOUT CRYING/EYES-CLOSED


```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```


```{r}

data_dyad_total_cues <- data_dyad_total_zeros %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            num_cues_per_min = sum(num_per_min),
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length,
         num_types_per_min = num_types_per_length * 60)

```



# Feeding length


```{r}

data_dyad_total_cues_selected <- data_dyad_total_zeros %>%
  group_by(dyad_set, id) %>%
  filter(video_length == max(video_length)) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(video_length),
         min_value = min(video_length),
         range_value = max_value - min_value) %>%
  mutate(num_ages = n()) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))


for (age in 1:n_time_points) {
  p <- ggplot(data_dyad_total_cues_selected %>%
                filter(num_ages == age),
              aes(x = id, y = video_length, color = dyad_set, shape = dyad_set)) +
    geom_point() +
    ggtitle(paste("Dyads observed at", age, "ages")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(y = "Feeding length (sec)") +
    ylim(0, max(data_dyad_total_cues_selected$video_length))
  print(p)
}

```


```{r}

pd <- position_dodge(0.4)

ggplot(data_dyad_total_cues_selected,
       aes(x = dyad_set, y = video_length, group = id, color = as_factor(num_ages))) +
  geom_line(alpha = 0.2, position = pd) +
  geom_point(position = pd) +
  labs(y = "Feeding length (sec)",
       x = "age", 
       color = "Number of ages")
```

# Total number of cues, excluding Crying and Eyes Closed


```{r}

data_dyad_total_cues_selected <- data_dyad_total_cues %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues),
         min_value = min(num_cues),
         range_value = max_value - min_value) %>%
  mutate(num_ages = n()) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))


for (age in 1:n_time_points) {
  p <- ggplot(data_dyad_total_cues_selected %>%
             filter(num_ages == age),
           aes(x = id, y = num_cues, color = dyad_set, shape = dyad_set)) +
      geom_point() +
      ggtitle(paste("Dyads observed at", age, "ages")) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(y = "Total number of cues")  +
    ylim(0, max(data_dyad_total_cues_selected$num_cues))
  print(p)
}

```



```{r}

pd <- position_dodge(0.4)

ggplot(data_dyad_total_cues_selected,
       aes(x = dyad_set, y = num_cues, group = id, color = as_factor(num_ages))) +
  geom_line(alpha = 0.2, position = pd) +
  geom_point(position = pd) +
  labs(y = "Total number of cues",
       x = "age", 
       color = "Number of ages")
```


# Total number of cues per length (min) of feeding


```{r}

data_dyad_total_cues_selected <- data_dyad_total_cues %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues_per_min),
         min_value = min(num_cues_per_min),
         range_value = max_value - min_value) %>%
  mutate(num_ages = n()) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))


for (age in 1:n_time_points) {
  p <- ggplot(data_dyad_total_cues_selected %>%
             filter(num_ages == age),
           aes(x = id, y = num_cues_per_min, color = dyad_set, shape = dyad_set)) +
      geom_point() +
      ggtitle(paste("Dyads observed at", age, "ages")) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(y = "Total number of cues, per minute") +
    ylim(0, max(data_dyad_total_cues_selected$num_cues_per_min))
  print(p)
}

```



```{r}

pd <- position_dodge(0.4)

ggplot(data_dyad_total_cues_selected,
       aes(x = dyad_set, y = num_cues_per_min, group = id, color = as_factor(num_ages))) +
  geom_line(alpha = 0.2, position = pd) +
  geom_point(position = pd) +
  labs(y = "Total number of cues, per minute",
       x = "age", 
       color = "Number of ages")
```



# Number of different types of cues



```{r}

data_dyad_total_cues_selected <- data_dyad_total_cues %>%
  group_by(id) %>%
  mutate(max_value = max(num_types),
         min_value = min(num_types),
         range_value = max_value - min_value) %>%
  mutate(num_ages = n()) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))


for (age in 1:n_time_points) {
  p <- ggplot(data_dyad_total_cues_selected %>%
             filter(num_ages == age),
           aes(x = id, y = num_types, color = dyad_set, shape = dyad_set)) +
      geom_point() +
      ggtitle(paste("Dyads observed at", age, "ages")) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(y = "Number of different types of cues") +
    ylim(0, max(data_dyad_total_cues_selected$num_types))
  print(p)
}

```



```{r}

pd <- position_dodge(0.4)

ggplot(data_dyad_total_cues_selected,
       aes(x = dyad_set, y = num_types, group = id, color = as_factor(num_ages))) +
  geom_line(alpha = 0.2, position = pd) +
  geom_point(position = pd) +
  labs(y = "Number of different types of cues",
       x = "age", 
       color = "Number of ages")
```



# Number of different types of cues, per length (min) of feeding



```{r}

data_dyad_total_cues_selected <- data_dyad_total_cues %>%
  group_by(id) %>%
  mutate(max_value = max(num_types_per_min),
         min_value = min(num_types_per_min),
         range_value = max_value - min_value) %>%
  mutate(num_ages = n()) %>%
  ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))


for (age in 2:n_time_points) {
  p <- ggplot(data_dyad_total_cues_selected %>%
             filter(num_ages == age),
           aes(x = id, y = num_types_per_min, color = dyad_set, shape = dyad_set)) +
      geom_point() +
      ggtitle(paste("Dyads observed at", age, "ages")) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(y = "Number of different types of cues, per minute") +
    ylim(0, max(data_dyad_total_cues_selected$num_types_per_min))
  print(p)
}

```



```{r}

pd <- position_dodge(0.4)

ggplot(data_dyad_total_cues_selected,
       aes(x = dyad_set, y = num_types_per_min, group = id, color = as_factor(num_ages))) +
  geom_line(alpha = 0.2, position = pd) +
  geom_point(position = pd) +
  labs(y = "Number of different types of cues, per minute",
       x = "age", 
       color = "Number of ages")
```




# Individual cues, per length of feeding

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_cues_selected <- data_dyad_total_zeros %>%
    filter(Behavior == selected_cue) %>%
    group_by(id) %>%
    mutate(max_value = max(num_per_min),
           min_value = min(num_per_min),
           range_value = max_value - min_value) %>%
    mutate(num_ages = n()) %>%
    ungroup() %>%
  mutate(id = fct_reorder(id, min_value)) %>%
  mutate(id = fct_reorder(id, range_value))
  
  
  for (age in 1:n_time_points) {
    p <- ggplot(data_dyad_total_cues_selected %>%
                  filter(num_ages == age),
                aes(x = id, y = num_per_min, color = dyad_set, shape = dyad_set)) +
      geom_point() +
      ggtitle(paste(selected_cue, "Dyads observed at", age, "ages")) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
      labs(y = "Number of cues, per minute") +
    ylim(0, max(data_dyad_total_cues_selected$num_per_min))
    print(p)
  }
  
  p2 <- ggplot(data_dyad_total_cues_selected,
               aes(x = dyad_set, y = num_per_min, group = id, color = as_factor(num_ages))) +
    geom_line(alpha = 0.2, position = pd) +
    geom_point(position = pd) +
    labs(y = "Number of cues, per minute",
         x = "age", 
         color = "Number of ages")  +
          ggtitle(selected_cue) 
  
  print(p2)
  
}

```



# END

```{r}
knitr::knit_exit()
```
