---
title: "interaction-analysis"
author: "William Medwid"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

### This analysis temporarily excludes bottle rejectors (for consistency)

```{r setup, include=FALSE}
#This analysis includes bottle rejectors and non-rejectors.

include_rejectors <- c(0) #, 1
source("shared_setup.R")
```

```{r}
df_behavior_clusters <- read_csv("df_behavior_clusters.csv")
```


## 1. Plot number of cues versus number of mom behaviors (per length of feeding) for dyads across ages, in total and for some of the specific cue-behavior comparisons in Dr. Ventura’s notes.

```{r}
p <- data_dyad_total_zeros %>% 
  group_by(id, dyad_set, dyad_unit) %>% 
  summarise(total_apm = sum(num_per_min), feeding_minutes = max(video_mins)) %>% 
  pivot_wider(id_cols = c(id, dyad_set), names_from = dyad_unit, values_from = c(total_apm, feeding_minutes)) %>% 
  ggplot(aes(x = total_apm_Baby, 
             y = total_apm_Mom, 
             col = dyad_set,
             text = paste("Mother:", total_apm_Mom,
                          "\nBaby:", total_apm_Baby,
                          "\nFeeding mins:", feeding_minutes_Baby,
                          "\nid:", id,
                          "\nDyad set:", dyad_set)
             )) +
  geom_point(alpha = 0.35) +
  geom_smooth(aes(x = total_apm_Baby, y = total_apm_Mom), method = "lm", inherit.aes = FALSE) + #the text aes broke geom_smooth, so it's removed.
  facet_grid(cols = vars(dyad_set)) +
  xlab("Baby cues per minute") +
  ylab("Mom behaviors per minute")

p %>%  ggplotly(tooltip = "text")
p
```



## 2. For each infant cue, what happens “next”?  How long?

<!-- interaction_data is now included in data_duration -->

```{r heat_plot_function}
process_interactions <- function(data_duration, 
                                 dyad_unit_response, # Mom or baby, whose behaviors are we looking for?
                                 facet # Another variable to categorize by.
                                 ){
  # Example
  #dyad_unit_response = "Mom"
  #facet = "bottle_state"
  
  # data_processed tallies the number of A -> B interactions. 
  # Note that next_behavior is not the behavior on the next line, but the next behavior of the other party.
  # For example, if the baby gives 5 cues, then the mother inserts the bottle, next_behavior will be Bottle In Mouth for all 5 cues.
  # It only contains a row for each combination observed at least once.
  data_processed <- data_duration %>% 
    filter(dyad_unit == dyad_unit_response) %>%
    filter(!is.na(next_behavior)) %>% 
    filter(Time_Relative_sf > 0) %>% #Starting conditions don't really count
    group_by(Behavior, next_behavior, !!as.name(facet)) %>%
    summarise(num_count = n(),
            q1_time = quantile(time_until_next, 0.25),
            med_time = median(time_until_next),
            q3_time = quantile(time_until_next, 0.75)) %>% 
    ungroup()
  
  # The rest of the code just creates "0" rows for A -> B interactions that were never observed.
  # To ensure a row for every combination of A -> B interactions, we create a data frame all_combos of every combination. 
  all_combos <- expand.grid(Behavior = data_processed %>% distinct(Behavior) %>% pull(),
                            next_behavior = data_processed %>% distinct(next_behavior) %>% pull(),
                            facet_place = data_processed %>% distinct(!!as.name(facet)) %>% pull()) #Grabs the desired facet but it's named "facet_place"
  # Resets facet's name from facet_place to its original variable name.
  names(all_combos)[names(all_combos) == "facet_place"] <- facet
  
  # Final grouped data columns:
  # num_count: observed combinations of exact A -> B interaction (grouped by facet)
  # n_total: number of behavior A observed (grouped by facet)
  # following_prop: what proportion of behavior A was followed by response B (grouped by facet)
  data_processed %>%
    right_join(all_combos, on = c(Behavior, next_behavior, !!as.name(facet))) %>% 
    group_by(Behavior, !!as.name(facet)) %>% 
    mutate(across(c(num_count, q1_time, med_time, q3_time), .fns = ~replace_na(.,0))) %>%  #Fill stats columns with 0 where no interactions were observed.
    mutate(following_prop = num_count / sum(num_count),
           n_total = sum(num_count)) %>%
    mutate(following_prop = replace_na(following_prop, 0)) %>% 
    return()
}

#Faceted on dyad_set and bottle_state
#Same function as above, but doesn't require an additional variable to split by.
process_interactions_full_facet <- function(data_duration, dyad_unit_response){
  
  data_processed <- data_duration %>% 
    filter(dyad_unit == dyad_unit_response) %>%
    filter(!is.na(next_behavior)) %>% 
    filter(Time_Relative_sf > 0) %>% #Starting conditions don't really count
    group_by(Behavior, next_behavior, dyad_set, bottle_state) %>% 
    summarise(num_count = n(),
            q1_time = quantile(time_until_next, 0.25),
            med_time = median(time_until_next),
            q3_time = quantile(time_until_next, 0.75)) %>% 
    ungroup()
  
  all_combos <- expand.grid(Behavior = data_processed %>% distinct(Behavior) %>% pull(),
                            next_behavior = data_processed %>% distinct(next_behavior) %>% pull(),
                            dyad_set = data_processed %>% distinct(dyad_set) %>% pull(),
                            bottle_state = data_processed %>% distinct(bottle_state) %>% pull())
  
  data_processed %>%
    right_join(all_combos, on = c(Behavior, next_behavior, dyad_set, bottle_state)) %>% 
    group_by(Behavior, dyad_set, bottle_state) %>% 
    mutate(across(c(num_count, q1_time, med_time, q3_time), .fns = ~replace_na(.,0))) %>% 
    mutate(following_prop = num_count / sum(num_count),
           n_total = sum(num_count)) %>%
    mutate(following_prop = replace_na(following_prop, 0)) %>% 
    return()
}

heat_plot <- function(interactions, used_next, title){
  interactions %>%
    filter(next_behavior %in% used_next) %>%
    ggplot(aes(y = Behavior,
               x = next_behavior,
               col = following_prop,
               text = paste("Behavior: ", Behavior,
                            "\nResponse: ", next_behavior,
                            "\nProp. following: ", round(following_prop, 2), " (", num_count, "/", n_total, ")",
                            "\nTime between behavior and response ---",
                            "\nq1 time: ", round(q1_time, 2),
                            "\nMedian Time: ", round(med_time, 2),
                            "\nq3 time: ", round(q3_time, 2),
                            sep=""))) +
    geom_point(shape = "square", size = 2) + #bootleg heatmap
    coord_equal() +
    scale_color_continuous(type = "viridis") +
    theme(axis.text.x = element_text(angle = 90, hjust= 1)) +
    ylab("Original behavior") +
    xlab("Response to behavior") +
    ggtitle(title)
}

heat_table <- function(interactions, used_next, facet){
  interactions %>%
    mutate(prop_verbose = paste(round(following_prop, 2), " (", num_count, "/", n_total, ")", sep = "")) %>%
    filter(next_behavior %in% used_next) %>%
    pivot_wider(id_cols = c("Behavior", facet), names_from = next_behavior, values_from = prop_verbose) %>% 
    arrange(across(all_of(c(facet)))) %>% 
    return()
}
```


```{r first-set-infant}
infant_interactions <- data_duration %>% process_interactions("Baby", "bottle_state")

responses = behavior_codebook %>% filter(dyad_unit == "Mom") %>% pull(Behavior)

infant_interactions %>% 
  filter(bottle_state == "Bottle in mouth") %>% 
  heat_plot(responses, "First responses to infant behaviors - Bottle in mouth") %>% 
  ggplotly(tooltip = "text")

infant_interactions %>% 
  filter(bottle_state == "Bottle not in mouth") %>% 
  heat_plot(responses, "First responses to infant behaviors - Bottle not in mouth") %>% 
  ggplotly(tooltip = "text")

infant_interactions %>% 
  filter(bottle_state == "Bottle offered") %>% 
  heat_plot(responses, "First responses to infant behaviors - Bottle offered") %>% 
  ggplotly(tooltip = "text")


infant_interactions %>% 
  heat_table(responses, "bottle_state") %>% 
  kable()
```

```{r}
infant_interactions <- data_duration %>% 
  mutate(next_behavior = get_group(next_behavior, "narrow")) %>% 
  process_interactions("Baby", "dyad_set") %>% 
  filter(next_behavior != "Uninvolved")
  

responses <- behavior_codebook %>% filter(dyad_unit == "Mom") %>% pull(Narrow_group)

p <- infant_interactions %>% 
  heat_plot(responses, "First responses to infant behaviors (by category)") + facet_grid(cols = vars(dyad_set))
p

infant_interactions %>% 
  heat_table(responses, "dyad_set") %>% 
  kable()
```

The following plots show the behavior following a group of behaviors.


## 3. For each mom behavior, what happened “before”? How long?

```{r}
mother_interactions <- data_duration %>% process_interactions("Mom", "bottle_state")
  # filter(dyad_unit == "Mom") %>% 
  # group_by(Behavior, next_behavior, bottle_state) %>% 
  # summarise(num_count = n()) %>% 
  # group_by(Behavior, bottle_state) %>% 
  # mutate(following_prop = num_count / sum(num_count),
  #        n_total = sum(num_count)) %>% 
  # mutate(Behavior = reorder(Behavior, num_count, max), #These reorderings don't work as intended yet
  #        next_behavior = reorder(next_behavior, num_count, max))

responses <- behavior_codebook %>% filter(dyad_unit == "Baby") %>% pull(Behavior)

mother_interactions %>% 
  filter(bottle_state == "Bottle in mouth") %>% 
  heat_plot(responses, "First responses to mother behaviors - Bottle in mouth") %>% 
  ggplotly(tooltip = "text")

mother_interactions %>% 
  filter(bottle_state == "Bottle not in mouth") %>% 
  heat_plot(responses, "First responses to mother behaviors - Bottle not in mouth") %>% 
  ggplotly(tooltip = "text")

mother_interactions %>% 
  filter(bottle_state == "Bottle offered") %>% 
  heat_plot(responses, "First responses to mother behaviors - Bottle offered") %>% 
  ggplotly(tooltip = "text")

mother_interactions %>% 
  heat_table(responses, "bottle_state") %>% 
  kable()
```

```{r}
infant_interactions <- data_duration %>% 
  mutate(next_behavior = get_group(next_behavior, "narrow")) %>% 
  process_interactions("Mom", "dyad_set")


responses <- behavior_codebook %>% filter(dyad_unit == "Baby") %>% pull(Narrow_group)

p <- infant_interactions %>% 
  heat_plot(responses, "First responses to mother behaviors (Subtle Cues)") + facet_grid(cols = vars(dyad_set))
p # %>% ggplotly(tooltip = "text")

infant_interactions %>% 
  heat_table(responses, "dyad_set") %>% 
  kable()
```

### How long after each behavior is the response?

```{r}
data_duration$time_until_next %>% 
  summary()

time_interactions <- data_duration %>% 
  filter(!is.na(next_behavior)) %>% 
  mutate(Behavior = Narrow_group,
       #next_behavior = get_group(next_behavior, "Narrow")
       ) %>% 
  group_by(Narrow_group, next_group_narrow, dyad_unit, dyad_set) %>% 
  summarise(num_count = n(),
            q1_time = quantile(time_until_next, 0.25),
            med_time = median(time_until_next),
            q3_time = quantile(time_until_next, 0.75))

p <- time_interactions %>% 
  filter(dyad_unit == "Baby") %>% 
  filter(num_count > 5) %>% 
  ggplot(aes(y = Narrow_group,
             x = next_group_narrow,
             col = med_time,
             text = paste("Behavior: ", Narrow_group,
                          "\nResponse: ", next_group_narrow,
                          "\nn :", num_count,
                          "\nTime between cue and response ---",
                          "\nq1 time: ", q1_time,
                          "\nMedian Time: ", as.character(med_time),
                          "\nq3 time: ", q3_time,
                          sep=""))) +
  geom_point(shape = "square", size = 3) + #bootleg heatmap
  scale_color_continuous(type = "viridis") +
  theme(axis.text.x = element_text(angle = 90, hjust= 1)) +
  coord_equal() +
  facet_grid(cols = vars(dyad_set)) +
  ylab("Original behavior") +
  xlab("Response to behavior") +
  ggtitle("Baby cue response times (for n > 5 occurences)")

p %>% ggplotly(tooltip = "text")

#For this plot, display colors as inverted time? Scale would be better but less easy to interpret.
p <- time_interactions %>% 
  filter(dyad_unit == "Mom") %>% 
  filter(num_count > 5) %>% 
  ggplot(aes(y = Narrow_group,
             x = next_group_narrow,
             col = med_time,
             text = paste("Behavior: ", Narrow_group,
                          "\nResponse: ", next_group_narrow,
                          "\nn :", num_count,
                          "\nTime between cue and response ---",
                          "\nq1 time: ", q1_time,
                          "\nMedian Time: ", as.character(med_time),
                          "\nq3 time: ", q3_time,
                          sep=""))) +
  geom_point(shape = "square", size = 3) + #bootleg heatmap
  scale_color_continuous(type = "viridis") +
  theme(axis.text.x = element_text(angle = 90, hjust= 1)) +
  coord_equal() +
  facet_grid(cols = vars(dyad_set)) +
  ylab("Original behavior") +
  xlab("Response to behavior") +
  ggtitle("Mom behavior response times (for n > 5 occurences)")

p# %>% ggplotly(tooltip = "text")
```

Other than a few outliers, this mainly shows that most behaviors have similarly quick response times. Further analysis could reveal more significant differences.

# Faceted by dyad_set and bottle state

## Baby cues

```{r}
interaction_data <- data_duration %>% 
  mutate(Behavior = Narrow_group, next_behavior = next_group_narrow) %>% 
  process_interactions_full_facet("Baby")

responses = behavior_codebook %>% filter(dyad_unit == "Mom") %>% pull(Narrow_group)

p <- interaction_data %>% 
  filter(bottle_state == "Bottle in mouth") %>% 
  heat_plot(responses, "First responses to baby behaviors - Bottle in mouth") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")

p <- interaction_data %>% 
  filter(bottle_state == "Bottle not in mouth") %>% 
  heat_plot(responses, "First responses to baby behaviors - Bottle not in mouth") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")

p <- interaction_data %>% 
  filter(bottle_state == "Bottle offered") %>% 
  heat_plot(responses, "First responses to baby behaviors - Bottle offered") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")
```

## Mom behaviors

```{r}
interaction_data <- data_duration %>% 
  mutate(Behavior = Narrow_group, next_behavior = next_group_narrow) %>% 
  process_interactions_full_facet("Mom")

responses = behavior_codebook %>% filter(dyad_unit == "Baby") %>% pull(Narrow_group)

p <- interaction_data %>% 
  filter(bottle_state == "Bottle in mouth") %>% 
  heat_plot(responses, "First responses to mom behaviors - Bottle in mouth") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")

p <- interaction_data %>% 
  filter(bottle_state == "Bottle not in mouth") %>% 
  heat_plot(responses, "First responses to mom behaviors - Bottle not in mouth") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")

p <- interaction_data %>% 
  filter(bottle_state == "Bottle offered") %>% 
  heat_plot(responses, "First responses to mom behaviors - Bottle offered") +
  facet_grid(cols = vars(dyad_set))
p  %>% ggplotly(tooltip = "text")
```

## Behaviors until a response

### Baby cues

```{r}
data_duration %>% 
  filter(dyad_unit == "Baby" & Narrow_group == "Subtle") %>% 
  ggplot(aes(x = remaining_cues, y = Behavior, col = dyad_set)) +
  geom_boxplot() +
  ggtitle("Baby cues before a response")

data_duration %>% 
  filter(dyad_unit == "Baby" & Narrow_group == "Potent") %>% 
  ggplot(aes(x = remaining_cues, y = Behavior, col = dyad_set)) +
  geom_boxplot() +
  ggtitle("Baby cues before a response")

data_duration %>% 
  filter(dyad_unit == "Baby") %>% 
  group_by(Behavior, dyad_set) %>% 
  summary_5_num("remaining_cues") %>% 
  arrange(Behavior, dyad_set) %>% 
  kable()
```

### Mom behaviors

```{r}
mom_narrow_groups <- behavior_codebook %>% filter(dyad_unit == "Mom") %>% distinct(Wide_group) %>% pull()

for(t in mom_narrow_groups){
  p <- data_duration %>% 
    filter(Wide_group == t) %>% 
    ggplot(aes(x = remaining_cues, y = Behavior, col = dyad_set)) +
    geom_boxplot() +
    ggtitle("Mom behaviors remaining before a response")
  p %>% print()
}

data_duration %>% 
  filter(dyad_unit == "Mom") %>% 
  group_by(Behavior, dyad_set) %>% 
  summary_5_num(to_summarise = "remaining_cues") %>% 
  arrange(Behavior, dyad_set) %>% 
  kable()
```

## New plots (starting April 2020)

Plot 1

- For each infant cue (at narrow group level) what is the next mom response (at narrow group level), excluding changes in bottle state

- If an infant cue is followed by another infant cue before a mom response, treat that as "no response". For example, if the sequence is Cries, Shakes head, Burps, then Cries would result in No response and Shakes head would result in Burps

- Tile/mosaic plot of distribution of mom response for each infant cue

- (I don't know if it makes more sense to do this at the individual cue/response level and then regroup, or just do it at the group level)

- Do two versions of this: one with uninvolved response as its own group, and one with uninvolved grouped together with no response

```{r}
#Controlling-Encouragment is a typo, fix later.
response_level_order = c("No response", "Uninvolved", "Other mother behavior", "Controlling-Limiting","Controlling-Encouragment", "Responsive")

infant_immediate_next = data_duration %>% 
  filter(Time_Relative_sf > 0) %>% 
  mutate(immediate_next_narrow = if_else(dyad_unit != lead(dyad_unit, 1), lead(Narrow_group), "No response")) %>% 
  select(dyad_unit, Behavior, Narrow_group, immediate_next_narrow, dyad_set) %>% 
  filter(dyad_unit == "Baby", Narrow_group %in% c("Potent", "Subtle")) %>% 
  mutate(immediate_next_narrow = factor(immediate_next_narrow, levels = response_level_order))

# By group, with uninvolved as a category
infant_immediate_next %>% 
  ggplot(aes(x = Narrow_group, fill = immediate_next_narrow)) +
  geom_bar(position = "fill") +
  xlab("Infant Behavior") +
  ylab("Proportion") +
  ggtitle("Immediate responses to infant behavior") +
  labs(fill = "Mother's Response") +
  facet_grid(rows = ~dyad_set)

# By group, with uninvolved as a category
infant_immediate_next %>% 
  mutate(immediate_next_narrow = fct_recode(immediate_next_narrow, "No response" = "Uninvolved")) %>% 
  ggplot(aes(x = Narrow_group, fill = immediate_next_narrow)) +
  geom_bar(position = "fill") +
  xlab("Infant Behavior") +
  ylab("Proportion") +
  ggtitle("Immediate responses to infant behavior") +
  labs(fill = "Mother's Response") +
  facet_grid(rows = ~dyad_set)
```

These two plots show the proportion of infants' behaviors immediately followed by a response. If the infant gives off two cues before the mother responds, the first one will be be categorized as "No response", while the second will have the mother's response category. Currently "Bottle in mouth" and "Bottle offered" are categorized as "Other mother behavior".

In case this is interesting, broken out by individual infant behavior:

```{r}
#By individual behavior
immediate_next_individual <- infant_immediate_next %>% 
  mutate(immediate_next_narrow = fct_recode(immediate_next_narrow, 
                                            "No response" = "Uninvolved", 
                                            "Inserts/Offers Bottle" = "Other mother behavior", 
                                            "Controlling" = "Controlling-Limiting", "Controlling" = "Controlling-Encouragment")) %>% 
  group_by(Behavior, immediate_next_narrow) %>% 
  summarize(n = n()) %>% 
  group_by(Behavior) %>% 
  mutate(prop = n/sum(n)) %>% 
  ungroup()

behavior_order = immediate_next_individual %>%
  filter(immediate_next_narrow == "Responsive") %>% 
  arrange(prop) %>% 
  pull(Behavior)

immediate_next_individual <- immediate_next_individual %>% 
  mutate(Behavior = factor(Behavior, levels = behavior_order))

immediate_next_individual %>% 
  ggplot(aes(x = prop, y = Behavior, fill = immediate_next_narrow)) +
  geom_bar(stat = "identity") +
  xlab("Proportion") +
  ylab("Infant Behavior") +
  ggtitle("Immediate responses to infant behavior") +
  labs(fill = "Mother's Response type")
```

# Responses within 10 seconds

Using the mother's next action: If that action is not within 10 seconds, it is listed as "No response". 

```{r}
window_seconds = 10

next_response_within_window <- data_duration %>% 
  filter(dyad_unit == "Baby", Time_Relative_sf > 0) %>% 
  # Change behaviors more than 10 seconds to "No response"
  mutate(mother_response = if_else(time_until_next <= window_seconds & !is.na(next_group_narrow), next_group_narrow, "No response")) %>% 
  # Further grouping and changing 
  mutate(mother_response = fct_recode(mother_response, 
                                      "No response" = "Uninvolved", 
                                      "Inserts/Offers Bottle" = "Other mother behavior", 
                                      "Controlling" = "Controlling-Limiting", "Controlling" = "Controlling-Encouragment")) %>% 
  mutate(mother_response = factor(mother_response, levels = c("No response", "Inserts/Offers Bottle", "Controlling", "Responsive"))) %>% 
  group_by(Behavior, mother_response) %>% 
  summarize(n = n()) %>% 
  group_by(Behavior) %>% 
  mutate(prop = n/sum(n)) %>% 
  ungroup()

# Next, we order the behaviors by what proportion receive a responsive response
behavior_order = next_response_within_window %>%
  filter(mother_response == "Responsive") %>% 
  arrange(prop) %>% 
  pull(Behavior)

next_response_within_window <- next_response_within_window %>% 
  mutate(Behavior = factor(Behavior, levels = behavior_order))

# Then plot by individual behavior
next_response_within_window %>% 
  ggplot(aes(x = prop, y = Behavior, fill = mother_response)) +
  geom_bar(stat = "identity") +
  scale_x_continuous(minor_breaks = seq(0.1 , 0.9, 0.2), breaks = seq(0, 1, 0.2)) + 
  theme(panel.grid.major.x = element_line("grey40", 0.25),
        panel.grid.minor.x = element_line("grey80", 0.25),
        panel.grid.major.y = element_blank()) +
  xlab("Proportion") +
  ylab("Infant cue") +
  ggtitle("Responses within 10 seconds of infant cues") +
  labs(fill = "Mother's Response type")
```

# Times until response

Plot 2
- For each infant cue measure amount of time until next mom response (whenever it happens, even if multiple infant cues in between), excluding changes in bottle state. For example, if Cries at 10, Shakes head at 12, and Burbs at 17, then time for Cries is 7 and for Shakes head is 5.

- Histograms to compare distribution of responses times for potent vs subtle cues at each age

- There will no "no responses" for this one. Do two versions: one where uninvolved is counted as a response and one where it's not.

```{r}
# Process copied from data-reshaping.Rmd, but without uninvolved mothers' behaviors
times_until_next = data_duration %>% 
  filter(Narrow_group != "Uninvolved") %>% 
  group_by(id, dyad_set) %>% #create next_behavior and next_time
  mutate(next_dyad_unit = lead(dyad_unit),
         switch = if_else(next_dyad_unit == dyad_unit, 0, 1),
         chain_group = cumsum(switch) - switch) %>% #Switch = 1 at end of group, chain group changes at start of new group
  ungroup() %>% 
  mutate(next_behavior = if_else(switch == 1, lead(Behavior), NULL),
         next_group_narrow = if_else(switch == 1, lead(Narrow_group), NULL),
         next_group_wide = if_else(switch == 1, lead(Wide_group), NULL),
         next_time = if_else(switch == 1, lead(Time_Relative_sf), NULL)) %>% 
  group_by(id, dyad_set, chain_group) %>% 
  mutate(next_behavior = if_else(is.na(next_behavior), last(next_behavior), next_behavior),
         next_group_narrow = if_else(is.na(next_group_narrow), last(next_group_narrow), next_group_narrow),
         next_group_wide = if_else(is.na(next_group_wide), last(next_group_wide), next_group_wide),
         next_time = if_else(is.na(next_time), last(next_time), next_time),
         time_until_next = next_time - Time_Relative_sf) %>% 
  mutate(one = 1,
         remaining_cues = cumsum(one),
         remaining_cues = max(remaining_cues) - remaining_cues) %>% 
  ungroup() %>% 
  select(-switch, -chain_group, -one) %>% 
  filter(dyad_unit == "Baby") %>% 
  select(dyad_set, Behavior, Narrow_group, time_until_next)
  
times_until_next %>% 
  filter(Narrow_group %in% c("Potent", "Subtle")) %>% 
  ggplot(aes(x = time_until_next, y = ..density..)) +
  geom_histogram() +
  facet_grid(facets = vars(Narrow_group)) +
  xlab("Time until next mother response (excluding uninvolved behaviors)") +
  ggtitle("Time until response by infant behavior")
```

# Showcase for df_behavior_clusters

Clusters

```{r}
df_behavior_clusters %>% 
  filter(id == 70008, dyad_set == "4 months") %>% 
  head(10)
```

To validate, the data as normally seen: 

Only state starts and state points - state stops were excluded from both, as they represent actions that are redundant or unclear in meaning such as no longer looking at phone (what category would this fall in?).

```{r}
data_duration %>% 
  filter(id == 70008, dyad_set == "4 months") %>% 
  select(-Event_Log, -Observation, -Comment, -Bottle_Emptying) %>% 
  head(10)
```


## Sample plots

Sample plot 1: Infant cues vs. mother cues in bout

```{r}
df_behavior_clusters %>% 
  ggplot(aes(x = Baby, y = Mom)) +
  geom_jitter(alpha = 0.1)
```


Sample plot 2: Infants' cues during a cluster vs. mother's behaviors. (Grouped, Jittered) Each point is one cluster.

```{r}
df_behavior_clusters %>% 
  pivot_longer(c("Potent", "Subtle"), names_to = "Infant_behavior_type", values_to = "Infant_behavior_count") %>% 
  pivot_longer(c("Controlling-Encouragment", "Controlling-Limiting", "Other mother behavior", "Responsive"), names_to = "Mother_behavior_type", values_to = "Mother_behavior_count") %>% 
  #mutate(Infant_behavior_count = as.factor(Infant_behavior_count),
  #       Mother_behavior_count = as.factor(Mother_behavior_count)) %>% 
  ggplot(aes(x = Infant_behavior_count, y = Mother_behavior_count)) +
  #geom_tile(alpha = 0.01) +
  geom_jitter(alpha = 0.1) +
  facet_grid(rows = vars(Infant_behavior_type), cols = vars(Mother_behavior_type))
```



