---
title: "interaction-analysis"
author: "William Medwid"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

This analysis includes bottle rejectors and non-rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0, 1)
source("shared_setup.R")
```


## 1. Plot number of cues versus number of mom behaviors (per length of feeding) for dyads across ages, in total and for some of the specific cue-behavior comparisons in Dr. Ventura’s notes.

```{r}
p <- data_dyad_total_zeros %>% 
  group_by(id, dyad_set, dyad_unit) %>% 
  summarise(total_apm = sum(num_per_min), feeding_minutes = max(video_mins)) %>% 
  pivot_wider(id_cols = c(id, dyad_set), names_from = dyad_unit, values_from = c(total_apm, feeding_minutes)) %>% 
  ggplot(aes(x = total_apm_Baby, 
             y = total_apm_Mom, 
             col = dyad_set,
             text = paste("Mother:", total_apm_Mom,
                          "\nBaby:", total_apm_Baby,
                          "\nFeeding mins:", feeding_minutes_Baby,
                          "\nid:", id,
                          "\nDyad set:", dyad_set)
             )) +
  geom_point(alpha = 0.35) +
  geom_smooth(aes(x = total_apm_Baby, y = total_apm_Mom), method = "lm", inherit.aes = FALSE) + #the text aes broke geom_smooth, so it's removed.
  facet_grid(cols = vars(dyad_set)) +
  xlab("Baby cues per minute") +
  ylab("Mom behaviors per minute")

p %>%  ggplotly(tooltip = "text")
```



## 2. For each infant cue, what happens “next”?  How long?

The following plots display the prevalence of each mother reaction to each infant cue. They only show mother behaviors which directly follow infant cues.

```{r}
infant_interactions <- data_duration %>%
  mutate(next_behavior = lead(Behavior), next_dyad_unit = lead(dyad_unit)) %>% 
  filter(dyad_unit == "Baby") %>% 
  filter(next_dyad_unit == "Mom") %>%
  group_by(Behavior, next_behavior) %>% 
  summarise(num_count = n()) %>% 
  group_by(Behavior) %>% 
  mutate(following_prop = num_count / sum(num_count),
         n_total = sum(num_count)) %>% 
  mutate(Behavior = reorder(Behavior, num_count, max), #These reorderings don't work as intended yet
         next_behavior = reorder(next_behavior, num_count, max))



heat_plot <- function(infant_interactions, used_next, title){
  infant_interactions %>% 
    filter(next_behavior %in% used_next) %>% 
    ggplot(aes(y = Behavior, 
               x = next_behavior, 
               col = following_prop,
               text = paste("Baby cue: ", Behavior,
                            "\nNext mom behavior: ", next_behavior,
                            "\nProp. following: ", round(following_prop, 2), " (", num_count, "/", n_total, ")",
                            sep=""))) +
    geom_point(shape = "square", size = 3) + 
    coord_equal() +
    scale_color_continuous(type = "viridis") +
    theme(axis.text.x = element_text(angle = 90, hjust= 1)) +
    ylab("Infant behavior") +
    xlab("Mom behavior immediately following") +
    ggtitle(title)

}
# Plots split by prevelance ----

# top_mom_behaviors <- infant_interactions %>% 
#   group_by(next_behavior) %>% 
#   summarise(n = max(num_count)) %>% 
#   arrange(n) %>% 
#   top_n(3) %>% 
#   pull(next_behavior)
# 
# bottom_mom_behaviors <- behavior_codebook %>% 
#   filter(dyad_unit == "Mom") %>% 
#   filter(!Behavior %in% top_mom_behaviors) %>% 
#   pull(Behavior)
# 
# infant_interactions %>% 
#   heat_plot(top_mom_behaviors, "Most common mother behaviors") %>% 
#   ggplotly(tooltip = "text")
# 
# infant_interactions %>% 
#   heat_plot(bottom_mom_behaviors, "Least common mother behaviors") %>% 
#   ggplotly()

infant_interactions %>% 
  heat_plot(behavior_codebook %>% 
  filter(dyad_unit == "Mom") %>% pull(Behavior), "All mother behaviors") %>% 
  ggplotly(tooltip = "text")
```


## 3. For each mom behavior, what happened “before”? How long?

```{r}

```

