---
title: "Jake Interaction Analysis"
author: "Jake Esprabens"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
include_rejectors <- c(0, 1)
source("shared_setup.R")
```

# 3. When the state is bottle-offer and infant cues occur (especially Blocks mouth and Lip compression, but others, too):


```{r}
interaction_data <- data_duration %>% 
  filter(!is.na(next_group_narrow)) %>% # if the narrow group of the next behavior was NA, i took it out for these summaries.
  filter(bottle_state == "Bottle offered",
         dyad_unit == "Baby")
```

## a,b) How often does this lead to a controlling maternal behavior? How often does this lead to responsive behaviors?

#### For All Dyad Sets

```{r}

interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="stack",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Number of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12))

with(interaction_data, table(Behavior, next_group_narrow)) %>%
  addmargins(margin = 2,FUN = list("Total Count" = sum)) %>%
  kable(caption = "Number of Behaviors for each \nInfant Cue when State is Bottle Offered")
  

interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12))

with(interaction_data, prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered",
        digits = 3)


interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  filter(Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle Offered")+
  theme(plot.title = element_text(size=12))

specific_behavior <- interaction_data %>%
  filter(Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet")
  
with(specific_behavior, prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle Offered",
        digits = 3)


interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_behavior, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12))

with(interaction_data, prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered",
        digits = 3)
```



#### By Dyad Set


```{r}
interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  filter(bottle_state == "Bottle offered",
         dyad_unit == "Baby") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="stack",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Number of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)

# still looking for a better solution for a table
with(interaction_data[interaction_data$dyad_set == "2wkB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "2 Week - Number of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "2moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "2 Month - Number of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "4moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "4 Month - Number of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "6moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "6 Month - Number of Behaviors for each \nInfant Cue when State is Bottle Offered")


interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  filter(bottle_state == "Bottle offered",
         dyad_unit == "Baby") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)


with(interaction_data[interaction_data$dyad_set == "2wkB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "2moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "4moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "6moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  filter(bottle_state == "Bottle offered",
         dyad_unit == "Baby",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle Offered")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)

with(interaction_data %>% filter(
        dyad_set == "2wkB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data %>% filter(
        dyad_set == "2moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data %>% filter(
        dyad_set == "4moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data %>% filter(
        dyad_set == "6moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

interaction_data %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  filter(bottle_state == "Bottle offered",
         dyad_unit == "Baby") %>%
  ggplot(aes(fill = next_behavior, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)

with(interaction_data[interaction_data$dyad_set == "2wkB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "2moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "4moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")

with(interaction_data[interaction_data$dyad_set == "6moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle Offered")
```

## c) How many subsequent bottle-offers occur until mother indicates feed is over?

```{r}
interaction_data2 <- data_duration 

interaction_data2 %>%
  filter(bottle_state == "Bottle offered" | Behavior == "Indicates feeding is over") %>%
  select(dyad_unit, dyad_set, id, bottle_state, Behavior) %>%
  mutate(bottle_state = replace_na(bottle_state, "NA")) %>%
  group_by(dyad_set, id) %>%
  summarise(count_bottle_offers = sum(bottle_state == "Bottle offered")) %>%
  ggplot(aes(x = count_bottle_offers, color = dyad_set)) +
  geom_freqpoly(stat = "count", binwidth = 1, linetype = "solid") + 
  xlab("Number of Bottle Offers") + 
  theme(panel.grid.major.y = element_blank()) +
  ggtitle("Number of Bottle Offers Until \nMom Indicates Feed is Over") + 
  labs(color='Dyad Set') 

```

```{r}
interaction_data2 %>%
  filter(bottle_state == "Bottle offered" | Behavior == "Indicates feeding is over") %>%
  select(dyad_unit, dyad_set, id, bottle_state, Behavior) %>%
  mutate(bottle_state = replace_na(bottle_state, "NA")) %>%
  group_by(dyad_set,id) %>%
  summarise(count_bottle_offers = sum(bottle_state == "Bottle offered")) %>%
  group_by(dyad_set) %>%
  summarise_at(vars(count_bottle_offers),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


```{r}
bottle_offers <- interaction_data2 %>%
  group_by(dyad_set, id) %>%
  filter(bottle_state == "Bottle offered") %>%
  slice(1) %>%
  mutate(bottle_offer_time = time) %>%
  select(dyad_set, id, bottle_state, bottle_offer_time)

feed_over <- interaction_data2 %>%
  group_by(dyad_set, id) %>%
  filter(Behavior == "Indicates feeding is over") %>%
  slice(1) %>%
  mutate(feeding_over_time = time) %>%
  select(dyad_set, id, Behavior, feeding_over_time)

bottle_offer_counts <- interaction_data2 %>%
  filter(bottle_state == "Bottle offered" | Behavior == "Indicates feeding is over") %>%
  select(dyad_unit, dyad_set, id, bottle_state, Behavior) %>%
  mutate(bottle_state = replace_na(bottle_state, "NA")) %>%
  group_by(dyad_set,id) %>%
  summarise(count_bottle_offers = sum(bottle_state == "Bottle offered"))


bottle_offers %>% 
  left_join(feed_over, by =c("dyad_set", "id")) %>%
  select(dyad_set, id, bottle_offer_time, feeding_over_time) %>%
  left_join(bottle_offer_counts, by =c("dyad_set", "id")) %>%
  filter(count_bottle_offers != 0) %>% # when the number of bottle offers is 0, then the bottle offers per min is undefined
  mutate(bot_offer_per_min = ((feeding_over_time - bottle_offer_time) / count_bottle_offers) / 60) %>%
  ggplot(aes(x = dyad_set, y = bot_offer_per_min, color = dyad_set)) +
  geom_violin() +
  geom_jitter() +
  theme(panel.grid.major.y = element_blank()) +
  ggtitle("Number of Bottle Offers Per Minute Until \nMom Indicates Feed is Over") + 
  labs(color='Dyad Set') +
  coord_flip() +
  ylab("Number of Bottle Offers Per Minute") +
  xlab("") +
  theme(legend.title = element_blank()) +
  scale_x_discrete(limits=rev)
  
  
# there is an instance where the bot_offer_per_min is < 0.  Because the first time the bottle was offered was after indicates feeding is over. is this possible?
  # for 2wk, 70346

# Indicates Feeding is over at 405.33
# Bottle Offered at 446.47
# to get the duration from first bottle offer, i subtracted the bottle offer time from the feeding is over time
# typically this could be positive because the feeding ending usually comes after the first bottle offer but this is not the case.


# interaction_data %>%
#   filter(id == 70346) %>%
#   select(Behavior,time,dyad_set,id)

interaction_data2 %>%
  filter(Behavior == "Indicates feeding is over")
```


```{r}
bottle_offers %>% 
  left_join(feed_over, by =c("dyad_set", "id")) %>%
  select(dyad_set, id, bottle_offer_time, feeding_over_time) %>%
  left_join(bottle_offer_counts, by =c("dyad_set", "id")) %>%
  filter(count_bottle_offers != 0) %>%
  mutate(bot_offer_per_min = ((feeding_over_time - bottle_offer_time) / count_bottle_offers) / 60) %>%
  group_by(dyad_set) %>%
  drop_na() %>%
  summarise_at(vars(bot_offer_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```





# 4. When the state is bottle-not-in-mouth and infant cues occur:


## a,b) How often does this lead to a controlling maternal behavior? How often does this lead to responsive behaviors?

```{r}
interaction_data4 <- data_duration %>% 
  filter(!is.na(next_group_narrow)) %>% # if the narrow group of the next behavior was NA, i took it out for these summaries.
  filter(bottle_state == "Bottle not in mouth",
         dyad_unit == "Baby")

interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="stack",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12))

with(interaction_data4, table(Behavior, next_group_narrow)) %>%
  addmargins(margin = 2,FUN = list("Total Count" = sum)) %>%
  kable(caption = "Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")
  

interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12))

with(interaction_data4, prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth",
        digits = 3)


interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  filter(Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12))

specific_behavior <- interaction_data4 %>%
  filter(Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet")
  
with(specific_behavior, prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle not in Mouth",
        digits = 3)


interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow) %>%
  ggplot(aes(fill = next_behavior, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12)) + 
  scale_fill_manual(values=c("antiquewhite", "aquamarine", "azure3", "blue", 
                             "brown", "burlywood", "cadetblue", "darkseagreen", 
                             "chocolate1", "darkgoldenrod", "darkgreen", "darkmagenta",
                             "darkolivegreen1", "hotpink1"))

with(interaction_data4, prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth",
        digits = 3)
```


```{r}
interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="stack",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)

# still looking for a better solution for a table
with(interaction_data4[interaction_data4$dyad_set == "2wkB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "2 Week - Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "2moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "2 Month - Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "4moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "4 Month - Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "6moB",], table(Behavior, next_group_narrow)) %>%
  kable(caption = "6 Month - Number of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")


interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)


with(interaction_data4[interaction_data4$dyad_set == "2wkB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "2moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "4moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "6moB",], prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  filter(Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet") %>%
  ggplot(aes(fill = next_group_narrow, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for Lip Compression \nand Blocks mouth when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12)) +
  facet_grid(~ dyad_set)

with(interaction_data4 %>% filter(
        dyad_set == "2wkB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data4 %>% filter(
        dyad_set == "2moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data4 %>% filter(
        dyad_set == "4moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

with(interaction_data4 %>% filter(
        dyad_set == "6moB",
         Behavior == "Lip compression/does not open mouth" |
         Behavior == "Blocks mouth with hands or feet"), prop.table(table(Behavior, next_group_narrow),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for \nLip compression does not open mouth and Blocks mouth")

interaction_data4 %>%
  select(dyad_unit, bottle_state, Behavior, next_behavior, next_group_narrow, dyad_set) %>%
  ggplot(aes(fill = next_behavior, x=Behavior)) +
  geom_bar(position="fill",stat ="count") + 
  labs(fill="Next Behavior") +
  theme(axis.title.x=element_blank()) +
  coord_flip() +
  ggtitle("Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")+
  theme(plot.title = element_text(size=12)) +
  scale_fill_manual(values=c("antiquewhite", "aquamarine", "azure3", "blue", 
                             "brown", "burlywood", "cadetblue", "darkseagreen", 
                             "chocolate1", "darkgoldenrod", "darkgreen", "darkmagenta",
                             "darkolivegreen1", "hotpink1")) +
  facet_grid(~ dyad_set)

with(interaction_data4[interaction_data4$dyad_set == "2wkB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "2 Week - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "2moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "2 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "4moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "4 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")

with(interaction_data4[interaction_data4$dyad_set == "6moB",], prop.table(table(Behavior, next_behavior),1)) %>%
  kable(caption = "6 Month - Proportion of Behaviors for each \nInfant Cue when State is Bottle not in Mouth")
```



