---
title: 'Mom Behaviors - Across Ages - Feeding Split into Quarters - Non-rejectors only'
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---


This analysis excludes bottle rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```


<!-- ```{r, include = FALSE} -->

<!-- library(readr) -->
<!-- library(dplyr) -->
<!-- library(tidyr) # need devtools version ? -->
<!-- library(tibble) -->
<!-- library(ggplot2) -->

<!-- library(stringr) -->
<!-- library(purrr) -->
<!-- library(forcats) -->
<!-- library(knitr) -->
<!-- library(purrr) -->
<!-- library(ggpubr) -->
<!-- library(cowplot) -->
<!-- library(gridExtra) -->


<!-- library(gganimate) -->
<!-- # devtools::install_github('haleyjeppson/ggmosaic') -->
<!-- library(ggmosaic) -->


<!-- knitr::opts_chunk$set(echo = FALSE, -->
<!--                       message = FALSE, -->
<!--                       warning = FALSE) -->

<!-- # Vectorized sequence function -->
<!-- # seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...) -->
<!-- seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to")) -->

<!-- ratio_lines = seq(1, 4, 0.5) -->

<!-- ``` -->


<!-- ```{r, include = FALSE} -->

<!-- # Reorder dyad_set: 2wk, 2mo, 4mo, 6mo -->
<!-- dyad_set_levels <- c("2wkB", "2moB", "4moB", "6moB") -->

<!-- n_time_points = length(dyad_set_levels) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- theme_set(theme_minimal()) -->
<!-- ``` -->


```{r, include = FALSE}

# Load data and select non-rejectors c(0), rejectors c(1), or all c(0, 1)

include_rejectors <- c(0)

data_dyad_total_time_split_zeros <- read_csv("data-dyad-total-time-split-zeros.csv") %>%
  mutate(dyad_set = factor(dyad_set, levels = dyad_set_levels),
         id = factor(id),
         time_split = factor(time_split),
         Bottle_Rejector = factor(Bottle_Rejector),
         num_per_min = num_per_length * 60) %>%
  filter(Bottle_Rejector %in% include_rejectors)
# %>% filter(time_split == 4)

data_map <- read_csv("data-map.csv") %>%
  mutate(id = factor(id))

if(1 %in% include_rejectors) {
  data_map <- data_map %>%
    mutate(time_points = Time_points_with_rejectors)
} else {
  data_map <- data_map %>%
    mutate(time_points = Time_points)
}

```


<!-- ```{r, include = FALSE} -->

<!-- behaviors <- data_dyad_total_zeros %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- state_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(Event_Type == "State start") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- point_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(Event_Type == "State point") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- cues <- data_dyad_total_zeros %>% -->
<!--   filter(Grouped_behavior == "Infant Satiation Cues") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- mom_behaviors <- data_dyad_total_zeros %>% -->
<!--   filter(dyad_unit == "Mom") %>% -->
<!--   select(Behavior) %>% -->
<!--   unique() %>% -->
<!--   pull() -->

<!-- bottle_states <- state_behaviors[grep("Bottle", state_behaviors)] -->

<!-- ``` -->

# Total number of cues

```{r}
# total number of cues and types of cues

data_dyad_total_cues <- data_dyad_total_time_split_zeros %>%
  filter(dyad_unit == "Baby") %>%
  # filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id, time_split) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            num_cues_per_min = num_cues_per_length * 60,
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length,
         num_types_per_min = num_types_per_length * 60)

```

## Split by quarter

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of mom behaviors in quarter") +
  labs(fill = "age", color = "age") +
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of mom behaviors in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))
                 
```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Comparison of quarters at each age

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of mom behaviors in quarter") +
  labs(fill = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_cues, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of mom behaviors in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```



# Mother behaviors per minute in each quarter

## Split by quarter

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_min, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of mom behaviors per minute in quarter") +
  labs(fill = "age", color = "age") +
  facet_wrap(vars(time_split))
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues_per_min, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of mom behaviors per minute in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

## Comparison of Quarters at each age

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_min, color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total number of mom behaviors per minute in quarter") +
  labs(fill = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
  
ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_cues_per_min, col = time_split)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  # geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of mom behaviors per minute in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))
                 
```




```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_cues_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```




# Total number of different types of mother behaviors



## Split by quarter

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of mom behaviors in quarter") +
  labs(color = "age") +
  facet_wrap(vars(time_split))

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of mom behaviors in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Comparison of quarters at each age

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = time_split)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of mom behaviors in quarter") +
  labs(color = "quarter") +
  facet_wrap(vars(dyad_set))

ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_types, col = time_split)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of mom behaviors in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))


```



```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```






# Types of mom behaviors per minute in quarter



## Split by quarter

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types_per_min,
           color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Density") +
  xlab("Number of different types of mom behaviors per minute in quarter") +
  labs(color = "age", fill = "age") +
  facet_wrap(vars(time_split))

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types_per_min, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Number of different types of mom behaviors per minute in quarter") +
  labs(x = "age", color = "age") +
  facet_wrap(vars(time_split))

```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, time_split) %>%
  summarize_at(vars(num_types_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```


## Comparison of quarters at each age

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types_per_min,
           color = time_split, fill = time_split)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of mom behaviors per minute in quarter") +
  labs(color = "quarter", fill = "quarter") +
  facet_wrap(vars(dyad_set))

ggplot(data_dyad_total_cues,
       aes(x = time_split, y = num_types_per_min, col = time_split)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(shape = 1, alpha = 0.8) +
  ylab("Number of different types of mom behaviors per minute in quarter") +
  labs(x = "quarter", color = "quarter") +
  facet_wrap(vars(dyad_set))


```



```{r}

data_dyad_total_cues %>% 
  group_by(time_split, dyad_set) %>%
  summarize_at(vars(num_types_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```



# Proportion of mothers that express the behavior at least once during quarter

```{r}

data_proportion_behavior_occurs <-
  data_dyad_total_time_split_zeros %>%
  filter(Behavior %in% mom_behaviors) %>%
  mutate(behavior_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, time_split, Behavior, behavior_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = behavior_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_behavior = `TRUE` / (`TRUE` + `FALSE`))

```

## Split by quarter

```{r}

ggplot(data_proportion_behavior_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_behavior, mean),
           x = proportion_dyads_with_behavior,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of mothers that express the behavior in quarter") +
  ylab("Maternal behavior") +
  labs(col = "age") +
  ggtitle("Proportion of mothers that express behavior\n at least once during quarter") +
  facet_wrap(vars(time_split))

```

## Comparison of quarters at each age

```{r}

ggplot(data_proportion_behavior_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_behavior, mean),
           x = proportion_dyads_with_behavior,
           col = time_split)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of mothers that express the behavior in quarter") +
  ylab("Maternal behavior") +
  labs(col = "quarter") +
  ggtitle("Proportion of mothers that express behavior\n at least once during quarter") +
  facet_wrap(vars(dyad_set))

```





# Individual mother behaviors: number of occurrences per minute in quarter

Only includes dyads who express the behavior at least once in quarter

## Split by quarter

```{r}

for (selected_cue in sort(mom_behaviors)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of behavior per minute in quarter") +
    labs(color = "age", fill = "age") +
    ggtitle(selected_cue) +
    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of behavior per minute in quarter") +
    labs(color = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_min, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of behavior per minute in quarter") +
    labs(x = "age", col = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)

  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set, time_split) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```




## Comparison of Quarters at each age


```{r}

for (selected_cue in sort(mom_behaviors)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = time_split,
                   fill = time_split)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of behavior per minute in quarter") +
    labs(color = "quarter", fill = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = time_split)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of behavior per minute in quarter") +
    labs(color = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = time_split, y = num_per_min, col = time_split)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of behavior per minute in quarter") +
    labs(x = "quarter", col = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(time_split, dyad_set) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```





# Number of bottle states by quarter


## Split by quarter

```{r}

for (selected_cue in sort(bottle_states)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of bottle state in quarter") +
    labs(color = "age", fill = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of bottle state in quarter") +
    labs(color = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_occurrences, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of bottle states in quarter") +
    labs(x = "age", col = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)

  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set, time_split) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```




## Comparison of Quarters at each age


```{r}

for (selected_cue in sort(bottle_states)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = time_split,
                   fill = time_split)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of bottle state in quarter") +
    labs(color = "quarter", fill = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = time_split)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of bottle state in quarter") +
    labs(color = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = time_split, y = num_occurrences, col = time_split)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of bottle state in quarter") +
    labs(x = "quarter", col = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(time_split, dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```




# Number of bottle states per minute in quarter


## Split by quarter

```{r}

for (selected_cue in sort(bottle_states)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of bottle state per minute in quarter") +
    labs(color = "age", fill = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of bottle state per minute in quarter") +
    labs(color = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_min, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of bottle states per minute in quarter") +
    labs(x = "age", col = "age") +
    ggtitle(selected_cue) +

    facet_wrap(vars(time_split), ncol = 2, drop = FALSE)

  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set, time_split) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```




## Comparison of Quarters at each age


```{r}

for (selected_cue in sort(bottle_states)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_dyad_total_time_split_zeros %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   y = after_stat(density),
                   color = time_split,
                   fill = time_split)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Occurrences of bottle state per minute in quarter") +
    labs(color = "quarter", fill = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_min,
                   color = time_split)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Occurrences of bottle state per minute in quarter") +
    labs(color = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = time_split, y = num_per_min, col = time_split)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(shape = 1, alpha = 0.8) +
    ylab("Occurrences of bottle state per minute in quarter") +
    labs(x = "quarter", col = "quarter") +
    ggtitle(selected_cue) +

    facet_wrap(vars(dyad_set), ncol = 2, drop = FALSE)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(time_split, dyad_set) %>%
    summarize_at(vars(num_per_min),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```


```{r}
knitr::knit_exit()
```

# END


# Total number of bottle states in feeding

```{r}

data_dyad_total_bottle_state <- data_dyad_total_time_split_zeros %>%
  filter(Behavior %in% bottle_states)

plot_bottle_in_mouth_pdf <- ggplot(data_dyad_total_bottle_state,
       aes(x = num_occurrences,
           y = after_stat(density),
           colour = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  ggtitle("Bottle states") +
  facet_wrap(~Behavior) +
  


plot_bottle_in_mouth_cdf <- ggplot(data_dyad_total_bottle_state,
       aes(num_occurrences,
           colour = dyad_set)) +
  stat_ecdf() +
  ylab("Cumulative proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  facet_wrap(~Behavior) +
  

plot_grid(plot_bottle_in_mouth_pdf,
          plot_bottle_in_mouth_cdf,
          rel_heights = c(1, 1),
          ncol = 1, nrow = 2,
          align = "h")

```

```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_occurrences, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of bouts in feeding") +
  facet_wrap(~Behavior) +
  
                 
```


```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_occurrences),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

## Number of bottle states per feeding length



```{r}
n_time_splits = 4

for (q in 1:n_time_splits) {
p1 <- ggplot(data_dyad_total_bottle_state,
       aes(x = num_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of bouts per length of feeding") +
  facet_wrap(~Behavior) +
  ggtitle(paste("Quarter = ", q))
print(p1)

p2<- ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Number of bouts per length of feeding") +
  facet_wrap(~Behavior) +
  ggtitle(paste("Quarter = ", q))
print(p2)

t1 <- data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior, time_split) %>%
  filter(time_split == q) %>%
  summarize_at(vars(num_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)
print(t1)
}

```

