---
title: 'Mom Behaviors - Across Ages - Whole Feeding - Non-rejectors only'
author: ""
date: "`r Sys.Date()`"
output: html_document
---

This analysis excludes bottle rejectors.

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```

# Total number of bottle states in feeding

```{r}

data_dyad_total_bottle_state <- data_dyad_total_zeros %>%
  filter(Behavior %in% bottle_states)

plot_bottle_in_mouth_pdf <- ggplot(data_dyad_total_bottle_state,
       aes(x = num_occurrences,
           y = after_stat(density),
           colour = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  ggtitle("Bottle states") +
  facet_wrap(~Behavior)


plot_bottle_in_mouth_cdf <- ggplot(data_dyad_total_bottle_state,
       aes(num_occurrences,
           colour = dyad_set)) +
  stat_ecdf() +
  ylab("Cumulative proportion of dyads") +
  xlab("Total number of bouts in feeding") +
  facet_wrap(~Behavior)

plot_grid(plot_bottle_in_mouth_pdf,
          plot_bottle_in_mouth_cdf,
          rel_heights = c(1, 1),
          ncol = 1, nrow = 2,
          align = "h")

```

```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_occurrences, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of bouts in feeding") +
  facet_wrap(~Behavior)
                 
```


```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_occurrences),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1,
        caption = "Number of bouts of each bottle state")

```

## Number of bottle states per feeding length



```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = num_per_min, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of bouts per minute of feeding") +
  facet_wrap(~Behavior)

ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = num_per_min, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Number of bouts per minute of feeding") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(num_per_min),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```


# Total duration in bottle state by dyad





```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = total_duration, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total duration of dyad bouts (sec)") +
  facet_wrap(~Behavior)
  
ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = total_duration, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total duation of dyad bouts (sec)") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_duration),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1,
        caption = "Bout durations (sec)")

```




## Total fraction of feeding time spent in bottle state by dyad





```{r}

ggplot(data_dyad_total_bottle_state,
       aes(x = total_fraction, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Total fraction of feeding time spent in state") +
  facet_wrap(~Behavior)

ggplot(data_dyad_total_bottle_state,
       aes(x = dyad_set, y = total_fraction, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total fraction of feeding time spent in state") +
  facet_wrap(~Behavior)
                 
```

```{r}

data_dyad_total_bottle_state %>%
  group_by(dyad_set, Behavior) %>%
  summarize_at(vars(total_fraction),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2,
        caption = "Fraction of time spent in state")

```

# All maternal behaviors: dyad totals

## Number of occurrences of each point behavior per dyad, including 0s


```{r}



for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior) %>%
    filter()
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
    
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each behavior per dyad, including 0s

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ylab("Number of occurrences of behavior per second") +
    xlab("Age") +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



## Proportion of dyads that express the behavior at least once during feeding, by age

```{r}

data_proportion_behavior_occurs <-
  data_dyad_total_zeros %>%
  filter(Behavior %in% mom_behaviors) %>%
  mutate(behavior_occurs = as.factor(num_occurrences > 0)) %>%
  group_by(dyad_set, Behavior, behavior_occurs, .drop = FALSE) %>%
  summarize(count = n()) %>%
  pivot_wider(names_from = behavior_occurs, values_from = count) %>%
  mutate(proportion_dyads_with_behavior = `TRUE` / (`TRUE` + `FALSE`))

ggplot(data_proportion_behavior_occurs,
       aes(y = reorder(Behavior, proportion_dyads_with_behavior, mean),
           x = proportion_dyads_with_behavior,
           col = dyad_set)) +
  geom_jitter(width = 0, height = 0.1) +
  xlim(0, 1) + 
  xlab("Proportion of mothers that express the behavior") +
  ylab("Maternal behavior") +
  ggtitle("Proportion of mothers that express behavior\n at least once during feeding")

```




## Number of occurrences of each behavior per dyad, only mothers that express behavior

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior) %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior in feeding") +
    ggtitle(selected_behavior)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each behavior per dyad, only mothers that express behavior

```{r}

for (selected_behavior in mom_behaviors) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ylab("Number of occurrences of behavior per second") +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```


# State behaviors, total duration of feeding time in state (only for mothers that exhibit the behavior)

```{r}

for (selected_behavior in intersect(state_behaviors, mom_behaviors)) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ylab("Total duration (sec)") +
    ggtitle(selected_behavior)

  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


# State behaviors, total proportion of feeding time in state (only for mothers that exhibit the behavior)


```{r}

for (selected_behavior in intersect(state_behaviors, mom_behaviors)) {
  
  data_dyad_total_zeros_selected_behavior <-
    data_dyad_total_zeros %>%
    filter(Behavior == selected_behavior)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_behavior,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ylab("Proportion of total feeding time spent in state") +
    ggtitle(selected_behavior)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_behavior %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```





# END

```{r}
knitr::knit_exit()
```

