---
title: "mother-descriptive-statistics"
author: "William Medwid"
date: "7/22/2021"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

This analysis excludes bottle rejectors.

# Mother descriptive statistics

```{r setup, include=FALSE}
include_rejectors <- c(0)
source("shared_setup.R")
```

## Quarterly proportions

```{r grid_plot}
# Many bar plots -----------

grid_plot <- function(group, num_splits){
  used_behaviors <- behavior_codebook %>% 
    filter(Wide_group == group) %>% 
    pull(Behavior)
  
  
  n_dyads_cue <- data_duration %>% #Cue representation in dyads before the requested time period
    filter(Behavior %in% used_behaviors) %>% 
    mutate(split = get_time_split(start_fraction, num_splits)) %>% 
    distinct(Behavior, dyad_set, id, split) %>% #Removes repeated cues from the same infant within the same feeding
    group_by(dyad_set, split) %>% 
    count(Behavior) %>% 
    mutate(n_dyads = n) %>% 
    select(!n) %>% 
    left_join(dyad_set_counts) %>% 
    mutate(prop_dyads = n_dyads / count)
  

  n_dyads_cue %>% 
    ggplot(aes(y=prop_dyads, x = split)) +
    geom_bar(position="dodge", stat="identity") +
    facet_grid(reorder(Behavior, desc(prop_dyads))~dyad_set) +
    ggtitle(paste("Percent of infants expressing ", group, " behaviors in each 1/", num_splits, " of feeding", sep = ""))+
    xlab("Split") +
    ylab("Proportion expressing cue within period") +
    theme(strip.text.y.right = element_text(angle = 0)) +
    ylim(0, 1) %>% 
    return()
}

grid_plot("Responsive", 4)
grid_plot("Controlling", 4)
grid_plot("Uninvolved", 4)
# grid_plot("Responsive", 5)
# grid_plot("Controlling", 5)
# grid_plot("Uninvolved", 5)
```

### Swapped barplot grid

To compare dyad ages within each split.

```{r flipped_grid_plot}
# Many bar plots -----------

grid_plot <- function(group, num_splits){
  used_behaviors <- behavior_codebook %>% 
    filter(Wide_group == group) %>% 
    pull(Behavior)
  
  
  n_dyads_cue <- data_duration %>% #Cue representation in dyads before the requested time period
    filter(Behavior %in% used_behaviors) %>% 
    mutate(split = get_time_split(start_fraction, num_splits)) %>% 
    distinct(Behavior, dyad_set, id, split) %>% #Removes repeated cues from the same infant within the same feeding
    group_by(dyad_set, split) %>% 
    count(Behavior) %>% 
    mutate(n_dyads = n) %>% 
    select(!n) %>% 
    left_join(dyad_set_counts) %>% 
    mutate(prop_dyads = n_dyads / count)
  

  n_dyads_cue %>% 
    ggplot(aes(y=prop_dyads, x = dyad_set)) +
    geom_bar(position="dodge", stat="identity") +
    facet_grid(reorder(Behavior, desc(prop_dyads))~split) +
    ggtitle(paste("Percent of infants expressing ", group, " behaviors in each 1/", num_splits, " of feeding", sep = ""))+
    xlab("Dyad set (Column = quarter)") +
    ylab("Proportion expressing cue within period") +
    theme(strip.text.y.right = element_text(angle = 0)) +
    theme(axis.text.x = element_text(angle=90)) +
    ylim(0, 1) %>% 
    return()
}

grid_plot("Responsive", 4)
grid_plot("Controlling", 4)
grid_plot("Uninvolved", 4)
# grid_plot("Responsive", 5)
# grid_plot("Controlling", 5)
# grid_plot("Uninvolved", 5)
```


```{r distribution_plot}
df_points <- data_duration %>% 
  filter(dyad_unit == "Mom" & Event_Type == "State point") %>% 
  filter(Behavior != "Indicates feeding is over")

med_times <- df_points %>% 
  group_by(Behavior) %>% 
  summarise(med_time = median(start_fraction)) %>%
  arrange(med_time) %>% 
  pull(Behavior)

df_points %>% 
  ggplot(aes(y=factor(Behavior, levels=med_times), x=start_fraction*100)) +
  geom_violin(aes(fill=dyad_set))+
  geom_boxplot(width=0.2, outlier.shape = NA, coef = 0) +
  facet_grid(cols = vars(dyad_set)) +
  ylab("Behavior") +
  xlab("Percent of feeding completed") +
  ggtitle("Shape and center 50 percentile of behavior times") +
  theme(legend.position = "none") #The fill colors are purely aesthetic so the legend is removed.
```



```{r}
states <- data_duration %>%
  filter(dyad_unit == "Mom") %>% 
  filter(!(Behavior %in% bottle_states)) %>% 
  filter(Narrow_group!="Other mother behavior") %>%
  filter(Event_Type == "State start") %>% 
  distinct(Behavior) %>% 
  pull()


total_fractions <- data_duration %>%
  filter(Behavior %in% states) %>% 
  filter(Event_Type == "State start") %>%
  group_by(id, dyad_set, Behavior) %>% 
  summarise(total_fraction = sum(duration_fraction))

total_fractions <- total_fractions %>% 
  expand(nesting(id, dyad_set), Behavior = states) %>%
  left_join(total_fractions, on=c(id, dyad_set, Behavior)) %>%
  replace_na(list(total_fraction = 0)) %>% 
  group_by(Behavior, dyad_set) %>% 
  summarise(mean_fraction = mean(total_fraction))

p <- total_fractions %>% 
  ggplot(aes(x=dyad_set,
             y=mean_fraction, 
             group=Behavior, 
             color=Behavior,
             linetype=Behavior)) +
  geom_path() + 
  geom_point() +
  ylab("Mean Fraction of Time in State") +
  xlab("Dyad Set") +
  ggtitle("Proportion of time exhibiting extended behaviors")

p %>% ggplotly()
```

This confirms expected trends of more mature behaviors increasing over time while burping decreases. Each of these are very small fractions of the feeding time, but still significant.

```{r}
line_plot <- function(group){
  p <- data_dyad_total_zeros %>% 
    mutate(any_occurances = if_else(num_occurrences>0, 1, 0)) %>% 
    filter(Wide_group==group) %>% 
    group_by(Behavior, dyad_set, Narrow_group) %>% 
    summarise(prop_occurances = round(mean(any_occurances), 2)) %>% 
    ggplot(aes(x=dyad_set, 
               y=prop_occurances, 
               color=Behavior,
               group=Behavior,
               linetype=Behavior)) +
    geom_point()+
    geom_line() +
    ylim(0, 1) +
    ggtitle(paste("Proportion of mothers performing", group, "actions")) +
    ylab("Proportion expressing cue at least once") +
    xlab("Baby age")
  
  p %>% ggplotly()
}

line_plot("Responsive")
line_plot("Controlling")
line_plot("Uninvolved")
```

One unusual finding here is that among four behaviors (3 controlling, one responsive), there is a sharp decrease in frequency from 2 months to 4 months, then a rebound at 6 months. Any ideas why this might be?

## Behavior frequencies

The following plots illustrate differences in behaviors per minute. Labelled numbers represent number of observations.

```{r}
mother_narrow <- data_dyad_total_zeros %>% 
  filter(dyad_unit == "Mom") %>% 
  distinct(Narrow_group) %>% 
  pull()

for(behavior_type in mother_narrow){
  p <- data_dyad_total_zeros %>%
    filter(dyad_unit == "Mom") %>% 
    filter(Narrow_group==behavior_type) %>% 
    mutate(Behavior = reorder(Behavior, num_per_min)) %>% 
    filter(num_per_min > 0) %>% 
    group_by(Behavior, dyad_set, Narrow_group) %>% 
    mutate(n_verbose = if_else(num_per_min == max(num_per_min), 
                                                  paste("", n()), 
                                                  "")) %>% 
    ungroup() %>% 
    ggplot(aes(y=Behavior, x=num_per_min, col=dyad_set)) +
    geom_boxplot(outlier.alpha = 0.75, outlier.size = 1) +
    geom_text(aes(label = n_verbose, x = num_per_min), label_padding = 10, position = position_dodge(width = 1)) +
    xlim(0,8) +
    ggtitle(paste(behavior_type)) + 
    xlab("Behaviors per minute")
  print(p)
}
```

In these plots, everything is treated as a state point behavior. Maybe it'd be more useful to separate the duration behaviors, but here we get a more direct comparison.

```{r}
data_dyad_total_zeros %>%
  filter(dyad_unit == "Mom") %>% 
  filter(!(Behavior %in% bottle_states)) %>% 
  filter(num_per_min > 0) %>% 
  group_by(dyad_set, id, Narrow_group) %>% 
  summarise(sum_num_per_min = sum(num_per_min)) %>% 
  group_by(Narrow_group, dyad_set) %>% 
  mutate(n_verbose = if_else(sum_num_per_min == max(sum_num_per_min), 
                                                    paste("", n()), 
                                                    "")) %>% 
  mutate(Narrow_group = reorder(Narrow_group, sum_num_per_min, median)) %>% 
  ggplot(aes(y=Narrow_group, x=sum_num_per_min, col=dyad_set)) +
  geom_boxplot(outlier.alpha = 0.75, outlier.size = 1) +
  geom_text(aes(label = n_verbose, x = -0.25), label_padding = 10, position = position_dodge(width = 1)) +
  ggtitle("Mothers' behavior group frequencies (0's excluded)") + 
  xlab("Behaviors per minute")
```

The main trends we can see are, encouragement is more often used on younger babies while responsive behavior is more often given to older infants.

## Distribution table

```{r distribution_table}
#Table ---------------
df_points <- data_duration %>% 
  filter(dyad_unit == "Mom" & Event_Type == "State point")

df_points %>%
  group_by(Behavior, dyad_set) %>%
  summarise(q1 = quantile(start_fraction, 0.25),
            median = median(start_fraction),
            q3 = quantile(start_fraction, 0.75), 
            total_expressions = n(), 
            dyads_expressing = n_distinct(dyad_set, id)) %>%
  kable(digits=2, caption = "When behaviors happen within the feeding, proportionally")
```