---
title: "Quarterly Data Summary"
author: "Kevin Ross and Jake Esprabens"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r, include = FALSE}

# library(readr)
# library(dplyr)
# library(tidyr) # need devtools version ?
# library(tibble)
# library(ggplot2)
# library(GGally)
# library(stringr)
# library(purrr)
# library(forcats)
# library(knitr)
# library(purrr)
# library(ggpubr)
# library(cowplot)
# library(gridExtra)
# 
# library(gifski)
# library(gganimate)
# # devtools::install_github('haleyjeppson/ggmosaic')
# library(ggmosaic)
# 
# 
# knitr::opts_chunk$set(echo = FALSE,
#                       message = FALSE,
#                       warning = FALSE)
# 
# # Vectorized sequence function
# # seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...)
# seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to"))
# 
# ratio_lines = seq(1, 4, 0.5)

```


```{r, include = FALSE}

# behavior_codebook <- read_csv("behavior_codebook.csv")
# behaviors <- as.character(behavior_codebook$Behavior)
# names(behaviors) <- behavior_codebook$Behavior_group
# 
# state_behaviors <- behavior_codebook %>%
#   filter(Event_Type == "State start") %>%
#   select(Behavior) %>%
#   pull()
# 
# point_behaviors <- behavior_codebook %>%
#   filter(Event_Type == "State point") %>%
#   select(Behavior) %>%
#   pull()
# 
# cues <- behavior_codebook %>%
#   filter(Behavior_group == "Infant Satiation Cues") %>%
#   select(Behavior) %>%
#   pull()
# 
# 
# cues <- replace(cues, cues =="Blocks mouth with hands or feet", "Blocks mouth")
# cues <- replace(cues, cues =="Blocks mouth with hands", "Blocks mouth")
# cues <- replace(cues, cues =="Displays negative facial expression when not crying","Displays negative facial expression")
# cues <- replace(cues, cues =="Leans away from bottle or arches back","Leans away or arches back")
# cues <- replace(cues, cues =="Lip compression/does not open mouth for nipple","Lip compression/does not open mouth")
# cues <- replace(cues, cues == "Shakes head or turns head/body away from nipple/bottle", "Shakes head or turns head/body away")
# cues <- replace(cues,cues =="Verbal question or acknowledgement of hunger","Verbal acknowledgement of hunger")
# cues <- replace(cues,cues =="Verbal question or acknowledgement of fullness","Verbal acknowledgement of fullness")
# 
# cues <- unique(cues)
# 
# # Reorder dyad_set: 2wk, 2mo, 4mo
# dyad_set_levels <- c("2 weeks", "2 months", "4 months", "6 months")
# 
# n_time_points = length(dyad_set_levels)

```


```{r setup, include=FALSE}
include_rejectors <- c(0, 1)
source("shared_setup.R")
```


```{r, include = FALSE}

# Load data and select non-rejectors c(0), rejectors c(1), or all c(0, 1)


data_quarterly <- read_csv("data-quarterly.csv") %>%
  # TEMPORARILY FILLING NA with 0 just so I can visualize the 6moB
  # mutate(Bottle_Rejector = replace_na(Bottle_Rejector, 0)) %>%# tempo
  mutate(dyad_set = factor(dyad_set, levels = dyad_set_levels)) %>%
  mutate(id = factor(id),
         Bottle_Rejector = factor(Bottle_Rejector),
         quarter = factor(quarter))
  # filter(Bottle_Rejector %in% include_rejectors) %>% # this filters out 6moB because we don't have the bottle rejectors yet
  # filter(quarter != 0) # is this okay? gets rid of the observations that never happen

data_map <- read_csv("data-map.csv") %>%
  mutate(id = factor(id))

if(1 %in% include_rejectors) {
  data_map <- data_map %>%
    mutate(time_points = Time_points_with_rejectors)
} else {
  data_map <- data_map %>%
    mutate(time_points = Time_points)
}
```





# Feeding length



```{r}
# don't need quarterly because feeding length
video_lengths <- data_quarterly %>%
  group_by(dyad_set, id, quarter) %>%
  filter(video_length == max(video_length)) %>%
  filter(row_number() == 1) %>%
  select(id, dyad_set, video_length, Bottle_Rejector, quarter)

ggplot(video_lengths,
       aes(x = video_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity")

ggplot(video_lengths,
       aes(x = dyad_set, y = video_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))
                 
```

```{r}

video_lengths %>%
  group_by(dyad_set) %>%
  summarize_at(vars(video_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```





## Individual dyads across age (for dyads observed at multiple ages)


```{r, include = FALSE}

video_lengths_individual <-
  inner_join(video_lengths, data_map, by = "id") %>%
  filter(time_points > 1) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_video_length = max(video_length),
         min_video_length = min(video_length),
         ratio = max_video_length / min_video_length,
         range = max_video_length - min_video_length) %>%
    filter(row_number() == 1)
```




```{r,  fig.show="hold", out.width="50%"}

ggplot(video_lengths_individual, 
         aes(x = ratio)) +
  geom_histogram(aes(y=..density..), binwidth = 0.25) +
  geom_rug() + 
  xlab("ratio of length of longest video to shortest video")

ggplot(video_lengths_individual,
       aes(x = min_video_length,
           y = max_video_length,
           color = ratio,
           shape = Bottle_Rejector)) +
  geom_point() +
  scale_color_gradient(low="blue", high="orange") +
  xlim(0, NA) +
  ylim(0, NA) +
  xlab("shortest video length") +
  ylab("longest video length") +
  ggtitle("Infants observed at multiple ages") +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines) +
  scale_shape_manual(values = c(1, 4))

```

```{r}

video_lengths_individual %>%
  ungroup() %>%
  summarize_at(vars(ratio),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```



```{r, include = TRUE}

video_lengths_individual <-
  inner_join(video_lengths, data_map, by = "id") %>%
  filter(time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_video_length = max(video_length),
         min_video_length = min(video_length),
         range_video_length = max_video_length - min_video_length) %>%
  ungroup()

ggplot(video_lengths_individual %>%
         mutate(id = fct_reorder(id, range_video_length)),
       aes(x = id, y = video_length, col = dyad_set)) +
  coord_flip() +
  ggtitle("Infants observed at all time points") +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))

```

# Total number of cues

```{r}
# total number of cues and types of cues

data_dyad_total_cues <- data_quarterly %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  group_by(dyad_set, id, quarter) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length)) %>%
  mutate(num_types_per_length = num_types / video_length)

ddtz <- read.csv("data-dyad-total-zeros.csv") %>%
  group_by(dyad_set, id) %>%
  select(dyad_set, id, Behavior, num_occurrences)
```

## Number of infant cues in feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") + 
  facet_wrap(~quarter) +
  ggtitle("Number of Infant cues by Quarter")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") + 
  facet_wrap(~quarter) +
  ggtitle("Number of Infant cues by Quarter")
                 
```

4th quarter only
```{r}

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
ggplot(aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") + 
  # facet_wrap(~quarter)
  ggtitle("Number of Infant cues in Last Quarter")
  
data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") + 
  # facet_wrap(~quarter) +
  ggtitle("Number of Infant cues in Last Quarter")
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

4ht quarter only
```{r}
# last quarter only
data_dyad_total_cues %>%
  filter(quarter == 4) %>% 
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)
```


## Number of cues per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  facet_wrap(~quarter) + 
  ggtitle("Number of Cues per Length of Feeding by Quarter")
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  facet_wrap(~quarter)  + 
  ggtitle("Number of Cues per Length of Feeding by Quarter")
                 
```

4th quarter only
```{r}

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  # facet_wrap(~quarter) 
  ggtitle("Number of Cues per Length of Feeding in Last Quarter")
  
data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  # facet_wrap(~quarter)
  ggtitle("Number of Cues per Length of Feeding in Last Quarter")
                 
```


```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

4th quarter only
```{r}

data_dyad_total_cues %>% 
  filter(quarter == 4) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


## Number of infant cues in feeding, excluding Crying and Eyes Closed

```{r}

data_dyad_total_cues_point <- data_quarterly %>%
  filter(dyad_unit == "Baby") %>%
  filter(!(Behavior %in% c("Eyes Open", "Not Crying"))) %>%
  filter(Behavior %in% intersect(cues, point_behaviors)) %>%
  group_by(dyad_set, id, quarter) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            num_cues = sum(num_occurrences),
            num_types = n_distinct(Behavior[num_occurrences > 0]),
            num_cues_per_length = sum(num_per_length),
            video_length = max(video_length))

ggplot(data_dyad_total_cues_point,
       aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  facet_wrap(~quarter) + 
  ggtitle("Excluding state cues (Crying and Eyes Closed) by Quarter")
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) by Quarter") +
  facet_wrap(~quarter)
                 
```

for 4th quarter only
```{r}

data_dyad_total_cues_point %>%
  filter(quarter == 4) %>%
ggplot(aes(x = num_cues, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  # facet_wrap(~quarter) + 
  ggtitle("Excluding state cues (Crying and Eyes Closed) in Last Quarter")

data_dyad_total_cues_point %>%
  filter(quarter == 4) %>%
ggplot(aes(x = dyad_set, y = num_cues, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infant cues in feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) in Last Quarter")
  # facet_wrap(~quarter)
                 
```



```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```

4th quarter only
```{r}
data_dyad_total_cues_point %>% 
  filter(quarter == 4) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 1)

```


## Number of cues per length of feeding, excluding Crying and Eyes Closed

```{r}
ggplot(data_dyad_total_cues_point,
       aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) by Quarter") +
  facet_wrap(~quarter)
  
ggplot(data_dyad_total_cues_point,
       aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) by Quarter") +
  facet_wrap(~quarter)
                 
```


4th quarter only
```{r}
data_dyad_total_cues_point %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = num_cues_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) in Last Quarter")
  # facet_wrap(~quarter)
  
data_dyad_total_cues_point %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = dyad_set, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  ylab("Total number of infants cues divided by length of feeding") +
  ggtitle("Excluding state cues (Crying and Eyes Closed) in Last Quarter")
  # facet_wrap(~quarter)
                 
```


```{r}

data_dyad_total_cues_point %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```

4th quarter only
```{r}

data_dyad_total_cues_point %>% 
  filter(quarter == 4) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(num_cues_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 4)

```


# Number of different types of cues

## Number of types

```{r}

ggplot(data_dyad_total_cues,
       aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues") +
  facet_wrap(~quarter) +
  ggtitle("Number of Types of Cues by Quarter")

ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  facet_wrap(~quarter) +
  ggtitle("Number of Types of Cues by Quarter")

```

4th quarter only
```{r}

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = num_types,
           y = after_stat(density),
           color = dyad_set)) +
  geom_freqpoly(binwidth = 1, linetype = "solid") +
  ylab("Proportion of dyads") +
  xlab("Number of different types of cues") +
  facet_wrap(~quarter) +
  ggtitle("Number of Types of Cues in Last Quarter")

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  ggplot(aes(x = dyad_set, y = num_types, col = dyad_set)) +
  coord_flip() +
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4)) +
  facet_wrap(~quarter) +
  ggtitle("Number of Types of Cues in Last Quarter")

```



```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```

4th quarter only
```{r}

data_dyad_total_cues %>% 
  filter(quarter == 4) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(num_types),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 2)

```

## Number of types per length of feeding

```{r}
ggplot(data_dyad_total_cues,
       aes(x = num_types_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of different types divided by length of feeding") +
  facet_wrap(~quarter)
  
ggplot(data_dyad_total_cues,
       aes(x = dyad_set, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))  +
  ylab("Number of different types divided by length of feeding") +
  facet_wrap(~quarter)
                 
```

```{r}
data_dyad_total_cues %>%
  filter(quarter == 4) %>%
ggplot(aes(x = num_types_per_length, color = dyad_set, fill = dyad_set)) +
  geom_histogram(aes(y = ..density..), alpha=0.3, position = "identity") +
  xlab("Number of different types divided by length of feeding") +
  # facet_wrap(~quarter)
  ggtitle("For Last Quarter")
  

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
ggplot(aes(x = dyad_set, y = num_types_per_length, col = dyad_set)) +
  coord_flip() +
  geom_violin() + 
  geom_boxplot(width = 0.1) + 
  geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
  scale_shape_manual(values = c(1, 4))  +
  ylab("Number of different types divided by length of feeding") +
  # facet_wrap(~quarter)
  ggtitle("For Last Quarter")
                 
```

```{r}

data_dyad_total_cues %>% 
  group_by(dyad_set, quarter) %>%
  summarize_at(vars(num_types_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```

4th quarter
```{r}

data_dyad_total_cues %>%
  filter(quarter == 4) %>%
  group_by(dyad_set) %>%
  summarize_at(vars(num_types_per_length),
               list(size = ~length(.),
                    ~mean(.),
                    ~sd(.),
                    ~min(.),
                    Q1 = ~quantile(., 0.25),
                    ~median(.), Q3 = ~quantile(., 0.75),
                    ~max(.))) %>%
  kable(digits = 3)

```


# Individual cues for Last Quarter


The rest of the plots are only focused on quarter 4.  Looking at all 4 quarters was getting a bit cluttered a difficult to do.


## Number of occurrences of each cue per dyad, including 0s for Last Quarter





```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue) 
    # facet_wrap(~quarter)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, including 0s

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```



## Proportion of dyads that express the cue at least once during feeding, by age

```{r}
# This cell is giving an error an Im not sure why


# data_proportion_cue_occurs <-
#   data_dyad_total_zeros %>%
#   filter(Behavior %in% cues) %>%
#   mutate(cue_occurs = as.factor(num_occurrences > 0)) %>%
#   group_by(dyad_set, Behavior, cue_occurs, .drop = FALSE) %>%
#   summarize(count = n()) %>%
#   pivot_wider(names_from = cue_occurs, values_from = count) %>%
#   mutate(proportion_dyads_with_cue = `TRUE` / (`TRUE` + `FALSE`))
# 
# ggplot(data_proportion_cue_occurs,
#        aes(y = reorder(Behavior, proportion_dyads_with_cue, mean),
#            x = proportion_dyads_with_cue,
#            col = dyad_set)) +
#   geom_jitter(width = 0, height = 0.1) +
#   xlim(0, 1) + 
#   xlab("Proportion of infants that express the cue") +
#   ylab("Infant cue") +
#   ggtitle("Proportion of infants that express cue\n at least once during feeding") + 
#   facet_wrap(~quarter)

```




## Number of occurrences of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue) %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   y = after_stat(density),
                   color = dyad_set)) +
    geom_freqpoly(binwidth = 1, linetype = "solid") +
    ylab("Proportion of dyads") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_occurrences,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue in feeding") +
    ggtitle(selected_cue) 
    # facet_wrap(~quarter)
  
  grid.arrange(p1, p2, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_occurrences),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
    
}

```



## Rate of occurrence of each cue per dyad, only infants that express cue

```{r}

for (selected_cue in cues) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = num_per_length,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Number of occurrences of cue per second") +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set, y = num_per_length, col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    ggtitle(selected_cue)
    # facet_wrap(~quarter)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(num_per_length),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```
# Crying and Eyes Closed

## Crying and Eyes Closed, total time (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_duration,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_duration,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Total duration (sec)") +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 1))
  cat('\n')
  
}

```


## Crying and Eyes Closed, total proportion of feeding time in state (only for infants that exhibit the cue)


```{r}

for (selected_cue in intersect(state_behaviors, cues)) {
  
  data_dyad_total_zeros_selected_cue <-
    data_quarterly %>%
    filter(quarter == 4) %>%
    filter(Behavior == selected_cue)  %>%
    filter(num_occurrences > 0)
  
  p1 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   y = after_stat(density),
                   color = dyad_set,
                   fill = dyad_set)) +
    geom_histogram(aes(y = ..density..), alpha = 0.3, position = "identity") +
    ylab("Density") +
    xlim(0, NA) + 
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p2 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = total_fraction,
                   color = dyad_set)) +
    stat_ecdf(geom = "step") +
    ylab("Cumulative proportion of dyads") +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  p3 <- ggplot(data_dyad_total_zeros_selected_cue,
               aes(x = dyad_set,
                   y = total_fraction,
                   col = dyad_set)) +
    coord_flip() +
    geom_violin() + 
    geom_boxplot(width = 0.1) + 
    geom_jitter(aes(shape = Bottle_Rejector), alpha = 0.8) +
    scale_shape_manual(values = c(1, 4)) +
    xlab("Proportion of total feeding time spent in state") +
    ggtitle(selected_cue)
  
  
  grid.arrange(p1, p3, ncol = 2)
  
  t <- data_dyad_total_zeros_selected_cue %>% 
    group_by(dyad_set) %>%
    summarize_at(vars(total_duration),
                 list(size = ~length(.),
                      ~mean(.),
                      ~sd(.),
                      ~min(.),
                      Q1 = ~quantile(., 0.25),
                      ~median(.), Q3 = ~quantile(., 0.75),
                      ~max(.)))
  print(kable(t, digits = 4))
  cat('\n')
  
}

```





# Individual infants across ages (only for infants observed at more than 1 age)


## Total number of cues per length


```{r, include = FALSE}

cues_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(time_points > 1) %>%
  filter(quarter == 4) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues_per_length),
         min_value = min(num_cues_per_length),
         range = max_value - min_value,
         ratio = max_value / min_value) %>%
  filter(row_number() == 1)

```




```{r,  fig.show="hold", out.width="50%"}

ggplot(cues_individual, 
         aes(x = ratio)) +
  geom_histogram(aes(y=..density..), binwidth = 0.25) +
  geom_rug() + 
  xlab("Ratio of largest to smallest cue rate")

ggplot(cues_individual,
       aes(x = min_value,
           y = max_value,
           color = ratio,
           shape = Bottle_Rejector)) +
  geom_point() +
  scale_color_gradient(low="blue", high="orange") +
  xlim(0, NA) +
  ylim(0, NA) +
  xlab("Smallest cue rate") +
  ylab("Largest cue rate") +
  geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines)  +
  scale_shape_manual(values = c(1, 4))

```

```{r, include = TRUE}

cues_individual <-
  inner_join(data_dyad_total_cues, data_map, by = "id") %>%
  filter(time_points == n_time_points) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(max_value = max(num_cues_per_length),
         min_value = min(num_cues_per_length),
         range = max_value - min_value,
         ratio = max_value / min_value) %>%
  ungroup()


ggplot(cues_individual %>%
         mutate(id = fct_reorder(id, range)),
       aes(x = id, y = num_cues_per_length, col = dyad_set)) +
  coord_flip() +
  ggtitle("Infants observed at all time points") +
  geom_point(aes(shape = Bottle_Rejector)) +
  scale_shape_manual(values = c(1, 4))

```

## Individual cues, only for infants that express the cue at least once at multiple ages


```{r}
# This cell is giving an error and im not sure why


# for (selected_cue in cues) {
#   
#   selected_cue_individual <-
#     inner_join(data_dyad_total_zeros %>%
#                  filter(Behavior == selected_cue),
#                data_map, by = "id") %>%
#     filter(time_points > 1) %>%
#     filter(quarter == 4) %>%
#     ungroup() %>%
#     group_by(id) %>%
#     mutate(max_value = max(num_per_length),
#            min_value = min(num_per_length)) %>%
#     filter(min_value > 0) %>%
#     mutate(range = max_value - min_value,
#            ratio = max_value / min_value) %>%
#     filter(row_number() == 1)
#   
#   
#   p1 <- ggplot(selected_cue_individual, 
#                aes(x = ratio)) +
#     geom_histogram(aes(y=..density..), binwidth = 0.25, na.rm = TRUE) +
#     geom_rug() + 
#     xlab("Ratio of largest to smallest cue rate")  +
#     ggtitle(selected_cue)
#   
#   p2 <- ggplot(selected_cue_individual,
#                aes(x = min_value,
#                    y = max_value,
#                    color = ratio,
#                    shape = Bottle_Rejector)) +
#     geom_point() +
#     scale_color_gradient(low="blue", high="orange") +
#     xlim(0, NA) +
#     ylim(0, NA) +
#     xlab("Smallest cue rate") +
#     ylab("Largest cue rate") +
#     geom_abline(intercept = 0, slope = ratio_lines, linetype = 2, color = ratio_lines)  +
#     scale_shape_manual(values = c(1, 4))  +
#     ggtitle(selected_cue)
#   
#   
#   grid.arrange(p1, p2, ncol = 2)
#   
#   t <- selected_cue_individual %>% 
#     ungroup() %>%
#     summarize_at(vars(ratio),
#                  list(size = ~length(.),
#                       ~mean(.),
#                       ~sd(.),
#                       ~min(.),
#                       Q1 = ~quantile(., 0.25),
#                       ~median(.), Q3 = ~quantile(., 0.75),
#                       ~max(.)))
#   print(kable(t, digits = 2))
#   cat('\n')
#   
# }

```


