---
title: "Repeated Measures ANOVA"
author: "Jake Esprabens"
date: "7/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r echo = T, results = 'hide', message=FALSE}
library(tidyverse)
library(effectsize)
```

## Reading in Data
```{r}
# currently using data duration dataset and data time event dataset.
# However, I still had to do some summarising

data_duration <- read.csv("data_duration.csv") %>%
  rename(ID_Number = id)

data_time_event <- read.csv("data_time_event.csv") %>%
  rename(ID_Number = id)
```

# Repeated measures analysis to test effects of time on:

## meal duration

```{r}
# data clean
meal_duration_data <- data_duration %>%
  group_by(ID_Number, dyad_set)%>%
  summarize(meal_duration = sum(duration))

# anova
meal_duration_model <- aov(data = meal_duration_data, meal_duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 
# meal duration as response
# dyad set as explanatory
# ratio between subject and time
# -> splits error between subject error and interaction error

summary(meal_duration_model)

effectsize::eta_squared(meal_duration_model, partial = TRUE)
```

## number and duration of bottle states (proportion of time spent in each)

```{r}
# Summarising
bottle_state_count_data <- data_time_event %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(bim_count = sum(Bottle_in_mouth),
            bnim_count = sum(Bottle_not_in_mouth))


bottle_state_data <- data_duration %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(bim_duration = sum(duration[Behavior == "Bottle in mouth"]),
            bnim_duration = sum(duration[Behavior == "Bottle not in mouth"]),
            bim_prop = sum(duration_fraction[Behavior == "Bottle in mouth"]),
            bnim_prop = sum(duration_fraction[Behavior == "Bottle not in mouth"])
  )
```


#### Count
```{r}
# bottle in mouth (BIM)
bim_count_model <- aov(data = bottle_state_count_data, bim_count ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bim_count_model)

effectsize::eta_squared(bim_count_model, partial = TRUE)


# bottle not in mouth (BNIM)
bnim_count_model <- aov(data = bottle_state_count_data, bnim_count ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bnim_count_model)

effectsize::eta_squared(bnim_count_model, partial = TRUE)
```


#### Duration
```{r}
# Bottle in mouth
bim_dur_model <- aov(data = bottle_state_data, bim_duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bim_dur_model)

effectsize::eta_squared(bim_dur_model, partial = TRUE)

# Bottle not in mouth
bnim_dur_model <- aov(data = bottle_state_data, bnim_duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bnim_dur_model)

effectsize::eta_squared(bnim_dur_model, partial = TRUE)
```


#### Proportion
```{r}
# Bottle in mouth
bim_prop_model <- aov(data = bottle_state_data, bim_prop ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bim_prop_model)

effectsize::eta_squared(bim_prop_model, partial = TRUE)

# Bottle not in mouth
bnim_prop_model <- aov(data = bottle_state_data, bnim_prop ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(bnim_prop_model)

effectsize::eta_squared(bnim_prop_model, partial = TRUE)
```


## number of cues

```{r}
num_cues_data <- data_time_event %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(num_cues = sum(num_cues_at_time))

num_cues_model <- aov(data = num_cues_data,num_cues ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(num_cues_model)

effectsize::eta_squared(num_cues_model, partial = TRUE)
```

## number of types of cues 

```{r}
types_cues_data <- data_duration %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(num_types_cues = n_distinct(Behavior))

types_cues_model <- aov(data = types_cues_data, num_types_cues ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(types_cues_model)

effectsize::eta_squared(types_cues_model, partial = TRUE)
```


## number and duration of sleeping bouts (proportion of time spent sleeping)
```{r}
# Using "Eyes Closed" as sleeping
sleeping_count_data <- data_time_event %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(sleeping_count = sum(Eyes.Closed))

sleeping_data <- data_duration %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(sleeping_duration = sum(duration[Behavior == "Eyes Closed"]),
            sleeping_prop = sum(duration_fraction[Behavior == "Eyes Closed"]))
```

#### count
```{r}
sleeping_count_model <- aov(data = sleeping_count_data, sleeping_count ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(sleeping_count_model)

effectsize::eta_squared(sleeping_count_model, partial = TRUE)
```

#### duration
```{r}
sleeping_dur_model <- aov(data = sleeping_data, sleeping_duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(sleeping_dur_model)

effectsize::eta_squared(sleeping_dur_model, partial = TRUE)
```

#### proportion
```{r}
sleeping_prop_model <- aov(data = sleeping_data, sleeping_prop ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(sleeping_prop_model)

effectsize::eta_squared(sleeping_prop_model, partial = TRUE)
```




## number and duration of crying bouts (proportion of time spent crying)
```{r}
crying_count_data <- data_time_event %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(crying_count = sum(Crying))
  
crying_data <- data_duration %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(crying_duration = sum(duration[Behavior == "Crying"]),
            crying_prop = sum(duration_fraction[Behavior == "Crying"]))
```

##### count
```{r}
crying_count_model <- aov(data = crying_count_data, crying_count ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(crying_count_model)

effectsize::eta_squared(crying_count_model, partial = TRUE)
```


#### duration
```{r}
crying_dur_model <- aov(data = crying_data, crying_duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(crying_dur_model)

effectsize::eta_squared(crying_dur_model, partial = TRUE)
```


#### proportion
```{r}
crying_prop_model <- aov(data = crying_data, crying_prop ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(crying_prop_model)

effectsize::eta_squared(crying_prop_model, partial = TRUE)
```


## number of mom behaviors (excluding indicates feed over)
```{r}
mom_behavior_data <- data_duration %>%
  filter(Behavior != "Indicates feeding is over") %>%
  filter(dyad_unit == "Mom") %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(num_mom_behaviors = n())

mom_behavior_model <- aov(data = mom_behavior_data, num_mom_behaviors ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(mom_behavior_model)

effectsize::eta_squared(mom_behavior_model, partial = TRUE)

```

## number and duration of burping, bottle propping, infant bottle holding, and  tech use bouts

### Uninvolved Mother Behaviors (Tech Use, Propped Bottle)
```{r}
uninvolved_data <- data_duration %>%
  filter(Behavior == "Propped bottle" |
         Behavior == "Looks at phone or device") %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(num_behaviors = n(),
            duration = sum(duration))
```

#### count
```{r}
# count of these behaviors
uninvolved_model_count <- aov(data = uninvolved_data, num_behaviors ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(uninvolved_model_count)

effectsize::eta_squared(uninvolved_model_count, partial = TRUE)
```


#### duration
```{r}
# duration of these behaviors
uninvolved_model_duration <- aov(data = uninvolved_data, duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(uninvolved_model_duration)

effectsize::eta_squared(uninvolved_model_duration, partial = TRUE)
```


### Burping and Infant Bottle Holding (Responsve Behaviors)

```{r}
# I ran these too just in case. The oned above are the uninvolved behaviors

responsive_data <- data_duration %>%
  filter(Behavior == "Burping" |
         Behavior == "Allows infant to hold bottle") %>%
  group_by(ID_Number, dyad_set) %>%
  summarize(num_behaviors = n(),
            duration = sum(duration))
```

#### count
```{r}
# count of these behaviors
resp_model_count <- aov(data = responsive_data, num_behaviors ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(resp_model_count)

effectsize::eta_squared(resp_model_count, partial = TRUE)
```


#### duration
```{r}
# duration of these behaviors
resp_model_duration <- aov(data = responsive_data, duration ~ factor(dyad_set) + Error(factor(ID_Number)/factor(dyad_set))) 

summary(resp_model_duration)

effectsize::eta_squared(resp_model_duration, partial = TRUE)
```
