---
title: "6 Month Data Processing"
author: "Jake Esprabens"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r, include = FALSE}

library(readxl)
library(tidyverse)
```


```{r}

behavior_codebook <- read_csv("behavior_codebook.csv") # took out ../ from before because I have this file in my current WD - Jake
behaviors <- as.character(behavior_codebook$Behavior)
names(behaviors) <- behavior_codebook$Behavior_group

state_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State start") %>%
  select(Behavior) %>%
  pull()

point_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State point") %>%
  select(Behavior) %>%
  pull()

# face blocked already taken care of in video coding
# face_blocked_removal <- 0.5 # exclude if face blocked > 50% of video

state_point_duration <- 0.00001 # for easier coding, treat state points as start/stop

```

# Read raw data

1. Combine all the 2 Excel files ()
1. Separate "Observation" column into:
  a. id = five-digit ID, e.g. 70138
  a. dyad_set, e.g. 4moB
  a. coder_id, e.g. CJ
  a. dyad_unit = Mom, Baby
1. Main time variable is Time_Relative_sf
1. Sort by dyad_id then by time
1. Remove rows for the "redundant" state behaviors (Crying, Eyes Closed).  Can just have one binary variable for each state behavior (e.g. Crying: 1=Crying, 0=Not Crying)
1. Change duration from 0 to 0.00001 for state points (makes a few coding items easier).
1. Add time zero state start for Mom Bottle not in mouth, and a corresponding state stop.  (Mom files start with Bottle in mouth, but not exactly at time 0, so this fixes that.)
1. Replace spaces with underscores in variable names
1. Add column for regrouped behaviors

```{r}
# Read in the two Excel files, one for 4moB Baby and one for 4moB Mom
baby_6mo <- read_excel("6-month Bottle-Feeding Coding_FINALbaby - Baby Coding - Event Logs.xlsx") %>%
  mutate(dyad_unit = "Baby",
         Modifier_1 = NA)
mom_6mo <- read_excel("6-month Bottle-Feeding Coding_FINALmom - Mom Coding Profile - Event Logs.xlsx") %>%
  mutate(dyad_unit = "Mom",
         Comment = NA)

# Combine the Data
# - remove first 7 columns as they are not needed
# - create dyad_set variable (not sure if needed thought since its all 4moB)
# create time and duration
# arrange by ID and time
# replace spaces with underscores in variable names

data <- rbind(baby_6mo, mom_6mo) %>%
  select(-(1:7))%>%
  mutate(dyad_set = "6moB") %>%
  mutate(time = Time_Relative_sf) %>%
  mutate(duration = ifelse(Event_Type == "State point",
                           state_point_duration,
                           Duration_sf)) %>%
  arrange("ID Number", "time") %>%
  rename_all(~ gsub(" ", "_", .)) # replace spaces with underscores in names

add_time_zero_start <- data %>%
  filter(dyad_unit == "Mom") %>%
  group_by(ID_Number) %>%
  filter(min(time) > 0) %>%
  filter(time == min(time)) %>% # first Mom event
  mutate(Behavior = "Bottle not in mouth",
         Duration_sf = time,
         duration = time,
         Time_Relative_sf = 0,
         time = 0,
         Event_Type = "State start",
         Coder = "KJR")

add_time_zero_end <- add_time_zero_start %>%
  mutate(Time_Relative_sf = duration,
         time = duration,
         Duration_sf = 0,
         duration = 0,
         Event_Type = "State stop")

data <- data %>%
  bind_rows(add_time_zero_start) %>%
  bind_rows(add_time_zero_end) %>%
  arrange(ID_Number, time)

data <- data %>%
  mutate(Recoded_Behavior = case_when(
    Behavior == "Blocks mouth with hands or feet" ~ "Blocks mouth",
    Behavior == "Blocks mouth with hands" ~ "Blocks mouth",
    Behavior == "Displays negative facial expression when not crying" ~ "Displays negative facial expression",
    Behavior == "Leans away from bottle or arches back" ~ "Leans away or arches back",
    Behavior == "Lip compression/does not open mouth for nipple" ~ "Lip compression/does not open mouth",
    Behavior == "Shakes head or turns head/body away from nipple/bottle" ~ "Shakes head or turns head/body away",
    Behavior == "Verbal question or acknowledgement of hunger" ~ "Verbal acknowledgement of hunger",
    Behavior == "Verbal question or acknowledgement of fullness" ~ "Verbal acknowledgement of fullness",
    TRUE ~ Behavior
  )) %>%
  mutate(Software_Behavior = Behavior,
         Behavior = Recoded_Behavior) %>%
  select(-Recoded_Behavior)

rm(baby_6mo, mom_6mo, add_time_zero_start, add_time_zero_end) 
```

```{r}
# adding the bottle rejectors
bottle_rej_6mo <- read_excel("Bottle Rejectors.xlsx",sheet = 4) %>%
  filter(`Rejected? (1=yes, 0=no, 99=not coded)` == 1)

data <- data %>%
  mutate(Bottle_Rejector = ifelse(ID_Number %in% bottle_rej_6mo$id, 1,0))


# COMMENT OUT THIS CODE BELOW WHEN THE REJECTORS ARE READY
# data <- data %>%
#   mutate(Bottle_Rejector = NA)
```



# A few checks to make sure data is valid


## Check that each  starts with "Bottle not in Mouth" (Code should return 0 rows)
```{r}
data %>%
  filter(dyad_unit == "Mom") %>%
  group_by(ID_Number)%>%
  slice(1) %>%
  select(Behavior) %>%
  filter(!(Behavior == "Bottle not in mouth"))
```


## Check that each state start has a state stop (code should return 0 rows)

```{r}
data %>%
  filter(Event_Type != "State point") %>% 
  group_by(ID_Number, Behavior) %>%
  summarize(start_count = sum(Event_Type == "State start"),
            stop_count = sum(Event_Type == "State stop")) %>%
  filter(start_count != stop_count) %>%
  nrow()
```

## Check that behaviors are recorded correctly as Mom/Baby

```{r}
data %>% ungroup() %>%
  group_by(Behavior, dyad_unit) %>%
  summarize(n = n())

data %>% ungroup() %>% 
  filter(dyad_unit == "Mom") %>%
  filter(Behavior %in% c("Not Crying", "Eyes Open"))
```

# Export the data as a csv
```{r}
# exporting data, saves a csv of data to current directory
write.csv(data, "./data-6moB.csv", row.names = FALSE)
```