---
title: "creating-quarterly-data"
author: "Jake Esprabens"
date: "5/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
library(tidyr) # need devtools version ?
library(tibble)
library(ggplot2)
library(GGally)
library(stringr)
library(purrr)
library(forcats)
library(knitr)
library(purrr)
library(ggpubr)
library(cowplot)
library(gridExtra)

library(gifski)
library(gganimate)
# devtools::install_github('haleyjeppson/ggmosaic')
library(ggmosaic)


knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Vectorized sequence function
# seq_vec(x, y) = c(x[1]:y[1], x[2]:y[2], ...)
seq_vec <- Vectorize(seq.default, vectorize.args = c("from", "to"))



```


```{r, include = FALSE}

behavior_codebook <- read_csv("behavior_codebook.csv")
behaviors <- as.character(behavior_codebook$Behavior)
names(behaviors) <- behavior_codebook$Behavior_group

state_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State start") %>%
  select(Behavior) %>%
  pull()

point_behaviors <- behavior_codebook %>%
  filter(Event_Type == "State point") %>%
  select(Behavior) %>%
  pull()

cues <- behavior_codebook %>%
  filter(Behavior_group == "Infant Satiation Cues") %>%
  select(Behavior) %>%
  pull()

state_point_duration <- 0.000000001 # for easier coding, treat state points as start/stop

# Reorder dyad_set: 2wk, 2mo, 4mo
dyad_set_levels <- c("2wkB", "2moB", "4moB", "6moB")

n_time_points = length(dyad_set_levels)

```


Read raw data.
Excel files have already been cleaned and combined into one file.

```{r, read-data, include = FALSE}

data <- read_csv("all_data.csv") %>%
  mutate(Grouped_behavior = fct_recode(Behavior, !!!behaviors)) %>%
  rename("id" = "ID_Number",
         "coder_id" = "Coder") %>%
  mutate(
    Time_Relative_sf = as.double(Time_Relative_sf),
    Duration_sf = as.double(Duration_sf),
    Comment = as.logical(Comment),
    id = factor(id),
    Position_of_Infant = as.integer(Position_of_Infant),
    time = as.double(time),
    duration = as.double(duration),
    dyad_set = factor(dyad_set, levels = dyad_set_levels),
    Bottle_Rejector = factor(Bottle_Rejector)
  )

```


Total number of dyads at each age


```{r}

n_dyads <- data %>%
  group_by(dyad_set, Bottle_Rejector) %>%
  summarize(n = n_distinct(id))

n_dyads %>% kable()

# two-way table?

```

List of dyads observed

```{r}

data_ids <- data %>%
  group_by(dyad_set, id) %>%
  summarize(id = first(id),
            Bottle_Rejector = first(Bottle_Rejector))

```


Summarize which dyads are observed at which ages

- 0.0 = not observed
- 0.5 = observed, Bottle rejector
- 1.0 = observed, not bottle rejector


```{r}
# Create data map - which dyads are in which set

count_ones <- function(x){
  length(x[x == 1])
}

count_positives <- function(x){
  length(x[x > 0])
}

data_map <- data %>%
  group_by(id, dyad_set) %>%
  filter(row_number() == 1) %>% 
  mutate(indicator = 1 - 0.5 * as.numeric(as.character(Bottle_Rejector))) %>%
  select(id, dyad_set, indicator) %>% 
  pivot_wider(names_from = dyad_set, values_from = indicator, values_fill = 0) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(Time_points_with_rejectors = count_positives(c_across(!id))) %>%
  mutate(Time_points = count_ones(c_across(!c(id, Time_points_with_rejectors))))

# write.csv(data_map,
#           "data-map.csv",
#           row.names = FALSE)

```

Summarize total number of dyads observed at each combination of ages


```{r}

data_age_summary <- data_map %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~round(.x + 0.1))) %>%
  filter(!(id == "Total")) %>%
  group_by(`2wkB`, `2moB`, `4moB`) %>%
  summarize(count = n_distinct(id)) %>%
  arrange(desc(`2wkB` + `2moB` + `4moB`), 
          desc(`2wkB`), 
          desc(`2moB`), 
          desc(`4moB`))

```

```{r}

data_age_summary_acceptors <- data_map %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~trunc(.x + 0.1))) %>%
  filter(!(id == "Total")) %>%
  group_by(`2wkB`, `2moB`, `4moB`) %>%
  summarize(count = n_distinct(id)) %>%
  arrange(desc(`2wkB` + `2moB` + `4moB`), 
          desc(`2wkB`), 
          desc(`2moB`), 
          desc(`4moB`))

```


Add columns for end time of each behavior, video length, and start/end/duration as fraction of video length.


```{r duration-data}
# individual instances of each behavior
# For each behavior, compute start time, end time, and duration
# as fraction of feeding length

data_duration <- data %>%
  mutate(end_time = time + duration) %>%
  group_by(dyad_set, id) %>%
  mutate(duration_fraction = duration / max(end_time),
         start_fraction = time / max(end_time),
         end_fraction = end_time / max(end_time),
         video_length = max(end_time)) %>%
  filter(Event_Type %in% c("State start", "State point"))

```

Jake adds in chunk to make quarterly data

```{r}
# this adds in a quarter and half variable to easily mark which part of the video the behavior falls in
data_duration <- data_duration %>% 
  group_by(dyad_set, id) %>%
  mutate(quarter = case_when(time < (video_length / 4) ~ 1,
                             time < 2*(video_length / 4) & time >= (video_length / 4) ~ 2,
                             time < 3*(video_length / 4) & time >= 2*(video_length / 4) ~ 3,
                             time >= 3*(video_length / 4) ~ 4)) %>%
  mutate(half = case_when(time < (video_length / 2) ~ 1,
                          time >= 2*(video_length / 4) ~ 2
                          ))
```

For each dyad, count number of instances and total time of each behavior, both absolute and relative to length of video.

```{r dyad-totals}
# Total count and time of each Behavior per dyad

data_dyad_total <- data_duration %>%
  group_by(dyad_set, id, Behavior) %>%
  summarize(Bottle_Rejector = first(Bottle_Rejector),
            Event_Type = first(Event_Type),
            dyad_unit = first(dyad_unit),
            Grouped_behavior = first(Grouped_behavior),
            total_fraction = sum(duration_fraction), 
            total_duration = sum(duration),
            num_occurrences = n(),
            video_length = max(video_length),
            quarter = quarter) %>%
  mutate(num_per_length = num_occurrences / video_length)


```

Add zeros for unobserved behaviors.
One row for each possible behavior for each dyad at each age.


```{r}
quarterly_data_dyad_total_zeros <-
  left_join(expand_grid(data_ids, behavior_codebook) %>%
              rename(Grouped_behavior = Behavior_group),
            data_dyad_total %>%
              select_if(names(.) %in% c("dyad_set", "id", "Behavior") |
                          sapply(., is.numeric)),
            by = c("dyad_set", "id", "Behavior")) %>%
  mutate(
    across(where(is.numeric), ~replace_na(.x, 0))
  ) %>%
  group_by(dyad_set, id) %>%
  mutate(video_length = max(video_length))

write.csv(quarterly_data_dyad_total_zeros,
          "quarterly-data-dyad-total-zeros.csv",
          row.names = FALSE)
```






